### 2020-11-06 article/article.tex
[ article ] Added barebones template.

\documentclass[conference]{IEEEtran}
\usepackage[english]{babel}
\input{commands.tex}

%%%%%%%% MARGIN
\geometry{verbose, letterpaper, tmargin=3cm,
  bmargin=3cm,lmargin=2.5cm,rmargin=2.5cm}

%%%%%%%% PARAGRAPH SETTINGS
% https://bit.ly/36WrtN4
\setlength\parindent{0pt}

% https://bit.ly/371dvto
\setlength{\parskip}{5pt}

%%%%%%%% HYPERREF PACKAGE
\usepackage{hyperref}
\hypersetup{linkcolor=blue}
\hypersetup{citecolor=blue}
\hypersetup{urlcolor=blue}
\hypersetup{colorlinks=true}

%%%%%%%% BIB-LATEX STUFF
\usepackage[style=ieee,
            bibstyle=ieee,
            citestyle=ieee,
            hyperref=true,
            backend=biber]{biblatex}
\addbibresource{ref.bib} %Put relative path to ref

%%%%%%%% DEFINITION AND THEOREM DEFINITIONS
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\theoremstyle{remark}
\newtheorem{question}{Question}

\newtheorem{theorem}{Theorem}[section]

%%%%%%%% CODE RENDERING !!! UNCOMMENT IF NEEDED !!!
% Compile with flag -shell-escape
%\usepackage{minted}

%%%%%%%% START DOCUMENT

\title{}
\author{Juan Sebasti\'an C\'ardenas-Rodríguez \\
  \scalebox{0.7}{Mathematical Engineering, Universidad EAFIT}}
\date{\today}

\begin{document}
\maketitle

\textit{Note}: All the code and the latex file can be found in
\href{https://github.com/juanscr/ai-works}{the github repository}.

\printbibliography
\end{document}

### 2020-11-06 src/DataGeneration.jl
[ src ] Added data generation.

@@ -1,0 +1,100 @@
+using Clustering
+using CSV
+using Plots
+using Random
+using Tables
+using TSne
+
+# Fixed seed
+Random.seed!(1234)
+
+# ============ Transform data ============ #
+function get_es(es_string)
+    r = Random.rand(Float64)
+    if es_string == "No decirle a nadie."
+        return -255 + r*55
+    elseif es_string == "Pido consejo a alguien cercano sobre cómo solucionarlo."
+        return 100 + r*100
+    elseif es_string == "Hablo lo que siento con la persona que tengo rabia."
+        return 200 + r*55
+    else
+        return -200 + r*100
+    end
+end;
+
+function get_output(output)
+    r = Random.rand(Float64)
+    if output == "Mucho."
+        return 75 + r*25
+    elseif output == "Muy poco."
+        return r*25
+    else
+        return 40 + r*20
+    end
+end;
+
+# ============ Read data ============ #
+rows = CSV.Rows("data/results.csv")
+data = []
+for row in rows
+    row_data = zeros(6)
+    row_data[1] = parse(Float64, row[2])
+    row_data[2] = parse(Float64, row[3])
+    row_data[3] = get_es(row[4])
+    row_data[4] = get_output(row[5])
+    row_data[5] = get_output(row[6])
+    row_data[6] = get_output(row[7])
+    push!(data, row_data)
+end;
+data = collect(transpose(hcat(data...)))
+
+# ============ Embedded Data ============ #
+function normalize(A)
+    return A ./ maximum(abs.(A), dims = 1)
+end
+
+function plot_data(data)
+    scatter(data[:, 1], data[:, 2],
+            markersize = 5,
+            markerstrokewidth = 0,
+            label = false,
+            color = "black",
+            grid = false)
+end;
+
+data_emb = tsne(normalize(data))
+plot_data(data_emb)
+savefig("figs/embedded-data.pdf")
+
+# ============ Write new data ============ #
+function find_membership(data, dist, prototypes, args)
+    k = size(prototypes)[1]
+    u = zeros(Float64, k, size(data)[1])
+    distances = zeros(Float64, k, size(data)[1])
+    for j in 1:k
+        distances[j, :] = dist(data, prototypes[j, :], args...)
+    end
+    indexes_min = argmin(distances, dims = 1)
+    u[indexes_min] .= 1
+
+    return u, distances
+end
+
[…]

### 2020-11-08 src/NN.jl
[ src ] Added first test for NN.

@@ -1,0 +1,54 @@
+# ====== Global Behavior ====== #
+using CSV
+using Flux
+using Plots
+
+# ====== Transform data ====== #
+function get_training_data(train_datax :: Matrix{Float64},
+                           train_datay :: Matrix{Float64})
+    data = []
+    for i in 1:size(train_datax, 1)
+        push!(data, (train_datax[i, :], train_datay[i, :]))
+    end
+    return data
+end
+
+# ====== NN ====== #
+function nn(ls :: Vector{Int64}, η :: Float64, train_data, ϕs)
+    # Layers Construction
+    layers = [Dense(length(train_data[1][1]), ls[1], ϕs[1])]
+    for i in 2:(length(ls) - 1)
+        push!(layers, Dense(ls[i - 1], ls[i], ϕs[i]))
+    end
+    push!(layers, Dense(ls[end], length(train_data[1][2]), ϕs[end]))
+
+    # NN construction
+    chain = Chain(layers...)
+
+    # Initialization for training
+    params = Flux.params(chain)
+    opt = Flux.Optimise.Descent(η)
+    loss(x, y) = Flux.Losses.mse(chain(x), y)
+    # Training
+    for i in 1:50
+        Flux.train!(loss, params, train_data, opt)
+    end
+end
+
+# ====== Main ====== #
+# Data reading
+data_csv = CSV.File("data/num-data.csv")
+data = zeros(length(data_csv), 7)
+i = 1
+for row in data_csv
+    data[i, 1] = row.Column1
+    data[i, 2] = row.Column2
+    data[i, 3] = row.Column3
+    data[i, 4] = row.Column4
+    data[i, 5] = row.Column5
+    data[i, 6] = row.Column6
+    data[i, 7] = row.Column7
+end
+
+# Testing
+nn([1], 0.2, get_training_data(data[1:6, :], data[7:end, :]), [σ])

### 2020-11-10 src/NN.jl
[ src ] Added gradient plotting and corrections.

@@ -29,26 +29,55 @@ function nn(ls :: Vector{Int64}, η :: Float64, train_data, ϕs)
     params = Flux.params(chain)
     opt = Flux.Optimise.Descent(η)
     loss(x, y) = Flux.Losses.mse(chain(x), y)
+
+    Δs = zeros(50, trunc(Int, length(params) / 2))
+
     # Training
-    for i in 1:50
+    for i in 1:100
         Flux.train!(loss, params, train_data, opt)
+
+        # Gradients
+        gs = gradient(params) do
+            loss(train_data[end]...)
+        end
+
+        for j in 1:2:length(params)
+            Δs[i, trunc(Int, (j + 1)/2)] = sum(gs[params[j]])
+        end
+        break
     end
+
+    # Gradients
+    return chain, Δs
 end
 
 # ====== Main ====== #
 # Data reading
 data_csv = CSV.File("data/num-data.csv")
 data = zeros(length(data_csv), 7)
-i = 1
+k = 1
 for row in data_csv
-    data[i, 1] = row.Column1
-    data[i, 2] = row.Column2
-    data[i, 3] = row.Column3
-    data[i, 4] = row.Column4
-    data[i, 5] = row.Column5
-    data[i, 6] = row.Column6
-    data[i, 7] = row.Column7
+    data[k, 1] = row.Column1
+    data[k, 2] = row.Column2
+    data[k, 3] = row.Column3
+    data[k, 4] = row.Column4
+    data[k, 5] = row.Column5
+    data[k, 6] = row.Column6
+    data[k, 7] = row.Column7
+    global k += 1
 end
 
+# Data testing
+dat0 = [([0, 0], [0]),
+        ([1, 0], [1]),
+        ([0, 1], [1]),
+        ([1, 1], [1])]
+
 # Testing
-nn([1], 0.2, get_training_data(data[1:6, :], data[7:end, :]), [σ])
+chain, Δs = nn([2], 0.5, dat0, [σ, σ])
+plot(Δs)
+savefig("testing.pdf")
+
+for dat1 in dat0
+    println(chain(dat1[1]), " == ", dat1[2])
+end

### 2020-11-11 src/NN.jl
[ src ] Updated directory structure.

@@ -1,7 +1,11 @@
 # ====== Global Behavior ====== #
+include("modules/ActFunctions.jl")
 using CSV
-using Flux
+include("modules/Brain.jl")
 using Plots
+using Random
+
+Random.seed!(1234)
 
 # ====== Transform data ====== #
 function get_training_data(train_datax :: Matrix{Float64},
@@ -11,44 +15,6 @@ function get_training_data(train_datax :: Matrix{Float64},
         push!(data, (train_datax[i, :], train_datay[i, :]))
     end
     return data
-end
-
-# ====== NN ====== #
-function nn(ls :: Vector{Int64}, η :: Float64, train_data, ϕs)
-    # Layers Construction
-    layers = [Dense(length(train_data[1][1]), ls[1], ϕs[1])]
-    for i in 2:(length(ls) - 1)
-        push!(layers, Dense(ls[i - 1], ls[i], ϕs[i]))
-    end
-    push!(layers, Dense(ls[end], length(train_data[1][2]), ϕs[end]))
-
-    # NN construction
-    chain = Chain(layers...)
-
-    # Initialization for training
-    params = Flux.params(chain)
-    opt = Flux.Optimise.Descent(η)
-    loss(x, y) = Flux.Losses.mse(chain(x), y)
-
-    Δs = zeros(50, trunc(Int, length(params) / 2))
-
-    # Training
-    for i in 1:100
-        Flux.train!(loss, params, train_data, opt)
-
-        # Gradients
-        gs = gradient(params) do
-            loss(train_data[end]...)
-        end
-
-        for j in 1:2:length(params)
-            Δs[i, trunc(Int, (j + 1)/2)] = sum(gs[params[j]])
-        end
-        break
-    end
-
-    # Gradients
-    return chain, Δs
 end
 
 # ====== Main ====== #
@@ -66,18 +32,19 @@ for row in data_csv
     data[k, 7] = row.Column7
     global k += 1
 end
+data = data ./ maximum(data, dims = 1)
 
-# Data testing
-dat0 = [([0, 0], [0]),
-        ([1, 0], [1]),
-        ([0, 1], [1]),
-        ([1, 1], [1])]
+# Activation Functions
+sig = Sigmoid()
+relu = ReLu()
+tant = Tanh()
+h = Heaviside()
 
-# Testing
-chain, Δs = nn([2], 0.5, dat0, [σ, σ])
-plot(Δs)
+# Brain
[…]

### 2020-11-11 src/modules/ActFunctions.jl
[ src ] Added modules for NN.

@@ -1,0 +1,98 @@
+# Continuous function with first derivatives type
+abstract type C1Function end
+
+# ========== Activation Functions ========== #
+# Sigmoid Activation Function
+mutable struct Sigmoid<:C1Function
+    eval::Function
+    eval_diff::Function
+
+    function Sigmoid()
+        this = new()
+        this.eval = function eval(x)
+            return 1 / (1 + exp(-x))
+        end
+
+        this.eval_diff = function eval_diff(x)
+            return eval(x) * (1 - eval(x))
+        end
+
+        return this
+    end
+end
+
+# Hyperbolic tangent
+mutable struct Tanh<:C1Function
+    eval::Function
+    eval_diff::Function
+
+    function Tanh()
+        this = new()
+        this.eval = function eval(x)
+            return tanh(x)
+        end
+
+        this.eval_diff = function eval_diff(x)
+            return 1 - eval(x) ^ 2
+        end
+
+        return this
+    end
+end
+
+# Linear
+mutable struct Linear<:C1Function
+    eval::Function
+    eval_diff::Function
+
+    function Linear()
+        this = new()
+        this.eval = function eval(x)
+            return x
+        end
+
+        this.eval_diff = function eval_diff(x)
+            return 1
+        end
+
+        return this
+    end
+end
+
+# ReLu
+mutable struct ReLu<:C1Function
+    eval::Function
+    eval_diff::Function
+
+    function ReLu()
+        this = new()
+        this.eval = function eval(x)
+            return maximum([x, 0])
+        end
+
+        this.eval_diff = function eval_diff(x)
+            return x < 0 ? 0 : 1
+        end
+
+        return this
+    end
+end
+
+# Heaviside
+mutable struct Heaviside<:C1Function
+    eval::Function
+    eval_diff::Function
+
+    function Heaviside()
+        this = new()
+        this.eval = function eval(x)
+            return x >= 0 ? 1 : 0
+        end
+
+        this.eval_diff = function eval_diff(x)
+            return 0
+        end
+
+        return this
+    end
+end

### 2020-11-11 src/modules/Brain.jl

@@ -1,0 +1,111 @@
+# ========== Global Beahvior ========== #
+include("ActFunctions.jl")
+using Distributions
+using LinearAlgebra
+using Plots
+using Random
+using Statistics
+
+# ========== Neural Network ========== #
+mutable struct Brain
+    ϕ::Vector{C1Function}
+    ω::Vector{Matrix{Float64}}
+    init_ω::Function
+    propagate::Function
+    learn_data::Function
+    bias::Bool
+
+    function Brain(m::Int64, n::Int64, l::Vector{Int64},
+                   ϕ::Vector{<:C1Function}; bias = true)
+        this = new()
+        this.ϕ = ϕ
+        this.bias = bias
+
+        # Function to initialize weights
+        this.init_ω = function init_ω(m, n, l)
+            gen_weight = function(x, y, bias)
+                dim_left = x
+                if bias
+                    dim_left += 1
+                end
+                return rand(Uniform(-1, 1), (dim_left, y))
+            end
+
+            # Initialize weights
+            this.ω = [gen_weight(m, l[1], this.bias)]
+            for i in 2:length(l)
+                push!(this.ω, gen_weight(l[i - 1], l[i], this.bias))
+            end
+            push!(this.ω, gen_weight(l[end], n, this.bias))
+        end
+        this.init_ω(m, n, l)
+
+        # Forward propagation
+        this.propagate = function propagate(x; give_all = false)
+            xᵣ = reshape(x, length(x), 1)
+            if this.bias
+                xᵣ = [xᵣ; 1]
+            end
+
+            # Forward propagation
+            z = Vector{Matrix{Float64}}([])
+            a = Vector{Matrix{Float64}}([xᵣ])
+            i = 1
+            for l in 1:length(this.ω)
+                push!(z, this.ω[l]' * a[l])
+                push!(a, this.ϕ[l].eval.(z[end]))
+                a[end] = this.bias && l != length(this.ω) ? [a[end]; 1] : a[end]
+            end
+
+            if give_all
+                return a, z
+            else
+                return a[end]
+            end
+        end
+
+        this.learn_data = function learn_data(x, y; η=0.1, α=0.1, epocs=10)
+            grads = zeros(epocs, length(this.ω))
+            ΔWs = [zeros(size(this.ω[i])) for i in 1:length(this.ω)]
+            instant_error = zeros(size(y))
+            average_error = zeros(epocs, size(y, 1))
+            for epoc in 1:epocs
[…]

### 2020-11-11 article/article.tex
[ article ] Added authors and abstract.
[ article ] Added sections.
[ article ] added introduction

@@
 %%%%%%%% START DOCUMENT
+\title{Supervised Learning for Psychological Attention to High School Students}
 
-\title{}
-\author{Juan Sebasti\'an C\'ardenas-Rodríguez \\
-  \scalebox{0.7}{Mathematical Engineering, Universidad EAFIT}}
-\date{\today}
+\author{\IEEEauthorblockN{Juan S. Cárdenas-Rodríguez}
+  \IEEEauthorblockA{\textit{Department of Mathematical Sciences} \\
+    \textit{EAFIT University}\\
+    Medellín, Colombia \\
+    jscardenar@eafit.edu.co} \and \IEEEauthorblockN{David Plazas}
+  \IEEEauthorblockA{\textit{Department of Mathematical Sciences} \\
+    \textit{EAFIT University}\\
+    Medellín, Colombia \\
+    dplazas@eafit.edu.co} }
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{abstract}
+  Hello.
+\end{abstract}
+
+\begin{IEEEkeywords}
+  Nice.
+\end{IEEEkeywords}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \textit{Note}: All the code and the latex file can be found in
-\href{https://github.com/juanscr/ai-works}{the github repository}.
+\href{https://github.com/juanscr/ai-works}{the GitHub repository}.
+
+\section{Introduction}
+
+Mental health is crucially important for every human being and has become one of
+the most important issues surrounding human health. According to the World
+Health Organization (WHO)\footnote{WHO's \href{https://bit.ly/34l2v94}{2001 report.}}
+report of 2001, mental disorders can affect 25\% of the population, therefore,
+suggesting the ongoing trend of people suffering from lack of mental health.
+Additionally, with the recent events caused by the COVID-19 pandemic, mental issues
+have risen as consequence of lockdowns all around the globe, as have been proved by 
+recent studies \parencite{rossi2020,xiong2020}.
+
+Furthermore, mental health is more important to monitor in adolescents and kids
+as this group is in the process of developing their mental structure and
+character. In this manner, as they continue creating their view about the world
+they must be surrounded by a healthy environment that promotes healthy habits
+and relationships with their surroundings.
+
+As a result, schools and parents have an important responsibility to the
+students of creating this environment and wisely handling mental health issues.
+However, high schools do not always know how to handle or detect cases of mental
+health issues. Additionally, technology has led to targeted harassing becoming
+more popular over time, therefore, difficulting the probability of detecting
+these cases.
+
+Some of the most common and important mental health issues are anxiety,
+depression, and hyperkinetic disorder. According to \textcite{schulte2016}, around
+10\% to 20\% of children suffer from hyperkinetic disorder. Additionally, school
+teachers just assume this disorder is a cause of undisciplined students and can
+take the hyperkinetic student to a depressive state. These three mental
+disorders can leave severe damage to a kid and can lead them to suicide.
+
+Hence, it is of the utmost importance to quickly and efficiently detect students
+that might be having a mental health issue to immediately start a process with
+him/her. Furthermore, this detection has to be done with measurable variables
+that can be easily obtained from questionnaires or school data.
+
+The present work is oriented to the application of supervised learning techniques
+(decision trees, support vector machines and neural networks) for classifying the
+data from the survey, aiming for the construction of a model to detect 
+individuals with mental health issues. This document is organized as follows: 
+Section \ref{sec:start} gives a short review of the current literature of 
+supervised techniques in this application area, Section \ref{sec:meth} shows 
+the general methodology used in this work, moreover Section \ref{sec:res} shows 
+the obtained results over the data and slight modifications, finally Section 
+\ref{sec:conc} concludes this work and sets pillars for future works.
+
+\section{State of the Art}\label{sec:start}
+
+\section{Methodology}\label{sec:meth}
+
+\section{Results}\label{sec:res}
+
+\section{Conclusions}\label{sec:conc}
 

### 2020-11-11 article/article.tex
[ article ] crs fitting.

@@
 the most important issues surrounding human health. According to the World
-Health Organization (WHO)\footnote{WHO's \href{https://bit.ly/34l2v94}{2001 report.}}
-report of 2001, mental disorders can affect 25\% of the population, therefore,
-suggesting the ongoing trend of people suffering from lack of mental health.
-Additionally, with the recent events caused by the COVID-19 pandemic, mental issues
-have risen as consequence of lockdowns all around the globe, as have been proved by 
-recent studies \parencite{rossi2020,xiong2020}.
+Health Organization (WHO)\footnote{WHO's \href{https://bit.ly/34l2v94}{2001
+    report.}} report of 2001, mental disorders can affect 25\% of the
+population, therefore, suggesting the ongoing trend of people suffering from
+lack of mental health. Additionally, with the recent events caused by the
+COVID-19 pandemic, mental issues have risen as consequence of lockdowns all
+around the globe, as have been proved by recent studies
+\parencite{rossi2020,xiong2020}.
 
@@
 Some of the most common and important mental health issues are anxiety,
-depression, and hyperkinetic disorder. According to \textcite{schulte2016}, around
-10\% to 20\% of children suffer from hyperkinetic disorder. Additionally, school
-teachers just assume this disorder is a cause of undisciplined students and can
-take the hyperkinetic student to a depressive state. These three mental
+depression, and hyperkinetic disorder. According to \textcite{schulte2016},
+around 10\% to 20\% of children suffer from hyperkinetic disorder. Additionally,
+school teachers just assume this disorder is a cause of undisciplined students
+and can take the hyperkinetic student to a depressive state. These three mental
 disorders can leave severe damage to a kid and can lead them to suicide.
@@
 
-The present work is oriented to the application of supervised learning techniques
-(decision trees, support vector machines and neural networks) for classifying the
-data from the survey, aiming for the construction of a model to detect 
-individuals with mental health issues. This document is organized as follows: 
-Section \ref{sec:start} gives a short review of the current literature of 
-supervised techniques in this application area, Section \ref{sec:meth} shows 
+The present work is oriented to the application of supervised learning
+techniques (decision trees, support vector machines and neural networks) for
+classifying the data from the survey, aiming for the construction of a model to
+detect individuals with mental health issues. This document is organized as
+follows: Section \ref{sec:start} gives a short review of the current literature
+of supervised techniques in this application area, Section \ref{sec:meth} shows
 the general methodology used in this work, moreover Section \ref{sec:res} shows

### 2020-11-11 src/modules/Tools.jl
[ modules ] Added basic tools usage.

@@ -1,0 +1,3 @@
+function normalize(data)
+    return data ./ maximum(data, dims = 1)
+end

### 2020-11-11 src/DataGeneration.jl
[ src ] Added indexes generation.

@@ -3,6 +3,7 @@ using CSV
 using Plots
 using Random
 using Tables
+include("modules/Tools.jl")
 using TSne
 
 # Fixed seed
@@ -49,10 +50,6 @@ end;
 data = collect(transpose(hcat(data...)))
 
 # ============ Embedded Data ============ #
-function normalize(A)
-    return A ./ maximum(abs.(A), dims = 1)
-end
-
 function plot_data(data)
     scatter(data[:, 1], data[:, 2],
             markersize = 5,
@@ -98,3 +95,38 @@ u, _ = find_membership(data, euclidean, protos, [])
 # CSV creation
 final_data = [data reshape(u[1, :], size(data, 1), 1)]
 CSV.write("data/num-data.csv", Tables.table(final_data))
+
+
+# ============ Separate data ============ #
+indexes = 1:size(data, 1)
+
+# Training
+n_training = trunc(Int, 0.6 * size(data)[1])
+indexes_tr = sort(sample(collect(indexes), n_training, replace = false))
+
+# Testing
+n_testing = trunc(Int, 0.2 * size(data)[1])
+indexes_avail = []
+for i in indexes
+    if i ∉ indexes_tr
+        push!(indexes_avail, i)
+    end
+end
+indexes_te = sort(sample(indexes_avail, n_testing, replace = false))
+
+# Validation
+indexes_val = []
+for i in indexes
+    if i ∉ indexes_tr && i ∉ indexes_te
+        push!(indexes_val, i)
+    end
+end
+indexes_val = sort(indexes_val)
+
+# Fill holes
+indexes_te = vcat(indexes_te, -ones(n_training - n_testing))
+indexes_val = vcat(indexes_val, -ones(n_training - length(indexes_val)))
+indexes_mat = [indexes_tr indexes_te indexes_val]
+
+# File of indexes
+CSV.write("data/indexes.csv", Tables.table(indexes_mat))

### 2020-11-11 src/modules/Tools.jl
[ src ] Added method to clean indexes.

@@ -1,3 +1,10 @@
+# Normalize data
 function normalize(data)
     return data ./ maximum(data, dims = 1)
+end
+
+# Clean indexes
+function purge(indexes :: Vector{Int64})
+    index_neg = findfirst(x -> x < 0, indexes)
+    return indexes[1:(index_neg - 1)]
 end

### 2020-11-11 src/NN.jl
[ src ] Added code to run all combinations.

@@ -2,19 +2,63 @@
 include("modules/ActFunctions.jl")
 using CSV
 include("modules/Brain.jl")
-using Plots
 using Random
+using StatsBase
 
+# Random seed
 Random.seed!(1234)
 
-# ====== Transform data ====== #
-function get_training_data(train_datax :: Matrix{Float64},
-                           train_datay :: Matrix{Float64})
-    data = []
-    for i in 1:size(train_datax, 1)
-        push!(data, (train_datax[i, :], train_datay[i, :]))
+# ====== Functions ====== #
+function get_neuron_combinations(L :: Int64, ls :: Vector{Int64})
+    prod = Iterators.product([ls for i in 1:L]...)
+
+    # Transformation to matrix
+    grid = reshape(collect(prod), 1, :)
+    array = vcat(map(x -> transpose(collect(x)), grid)...)
+
+    return array
+end
+
+function write_info_run(grads :: Matrix{Float64}, avg_err :: Vector{Float64},
+                        name_file :: String, η :: Float64, ls :: Vector{Int64})
+    open(name_file, "a") do io
+        # Write run information
+        write(io, string("eta,", η, "\n"))
+        write(io, "ls,")
+        for l in ls
+            write(io, string(l, ","))
+        end
+        write(io, "\n")
+
+        # Write run results
+        write(io, "Gradients\n")
+        for i in 1:size(grads, 1)
+            for j in 1:size(grads, 2)
+                write(io, string(grads[i, j], ","))
+            end
+            write(io, "\n")
+        end
+
+        write(io, "Average Error\n")
+        for i in 1:length(avg_err)
+            write(io, string(avg_err[i], "\n"))
+        end
     end
-    return data
+end
+
+function run_brain(η :: Float64, ls :: Vector{Int64}, tr_datax :: Matrix{Float64},
+                   tr_datay :: Matrix{Float64}, name_file :: String)
+    # Activation function
+    sig = Sigmoid()
+
+    # Brain
+    brain = Brain(size(tr_datax, 2), size(tr_datay, 2), ls,
+                  [sig for i in 1:(length(ls) + 1)])
+    grads, avg_err = brain.learn_data(tr_datax, tr_datay, η=η, α=0.1, epocs=50)
+    avg_err = reshape(sum(avg_err, dims = 2), :)
+
+    # File writing
[…]

### 2020-11-11 src/modules/Brain.jl
[ src ] Removed useless module.

@@ -2,7 +2,6 @@
 include("ActFunctions.jl")
 using Distributions
 using LinearAlgebra
-using Plots
 using Random
 using Statistics
 

### 2020-11-11 src/NN.jl
[ src ] Removed useless module.

@@ -3,7 +3,6 @@ include("modules/ActFunctions.jl")
 using CSV
 include("modules/Brain.jl")
 using Random
-using StatsBase
 
 # Random seed
 Random.seed!(1234)

### 2020-11-11 src/modules/Brain.jl
[ src ] Removed useless module.

@@ -3,7 +3,6 @@ include("ActFunctions.jl")
 using Distributions
 using LinearAlgebra
 using Random
-using Statistics
 
 # ========== Neural Network ========== #
 mutable struct Brain

### 2020-11-13 src/NN.jl
[ src ] Added data method to tools.

@@ -1,8 +1,8 @@
 # ====== Global Behavior ====== #
 include("modules/ActFunctions.jl")
-using CSV
 include("modules/Brain.jl")
 using Random
+include("modules/Tools.jl")
 
 # Random seed
 Random.seed!(1234)
@@ -61,28 +61,9 @@ function run_brain(η :: Float64, ls :: Vector{Int64}, tr_datax :: Matrix{Float6
 end
 
 # ====== Main ====== #
-# Data reading
-data_csv = CSV.File("data/num-data.csv")
-data = zeros(length(data_csv), 7)
-k = 1
-for row in data_csv
-    data[k, 1] = row.Column1
-    data[k, 2] = row.Column2
-    data[k, 3] = row.Column3
-    data[k, 4] = row.Column4
-    data[k, 5] = row.Column5
-    data[k, 6] = row.Column6
-    data[k, 7] = row.Column7
-    global k += 1
-end
-data = normalize(data)
-
-# Training data
-indexes_csv = CSV.File("data/indexes.csv")
-indexes_tr = indexes_csv.columns[1]
-
-train_datax = data[indexes_tr, 1:6]
-train_datay = data[indexes_tr, 7:end]
+train_data, _, _ = create_data("data/num-data.csv")
+train_datax = train_data[1]
+train_datay = train_data[2]
 
 # Parameters for running
 ηs = [0.2, 0.5, 0.9]

### 2020-11-13 src/modules/Tools.jl

@@ -1,3 +1,5 @@
+using CSV
+
 # Normalize data
 function normalize(data)
     return data ./ maximum(data, dims = 1)
@@ -7,4 +9,46 @@ end
 function purge(indexes :: Vector{Int64})
     index_neg = findfirst(x -> x < 0, indexes)
     return indexes[1:(index_neg - 1)]
+end
+
+# Get data
+function create_data(name_file :: String, sep = true)
+    # Data reading
+    data_csv = CSV.File("data/num-data.csv")
+    data = zeros(length(data_csv), 7)
+    k = 1
+    for row in data_csv
+        data[k, 1] = row.Column1
+        data[k, 2] = row.Column2
+        data[k, 3] = row.Column3
+        data[k, 4] = row.Column4
+        data[k, 5] = row.Column5
+        data[k, 6] = row.Column6
+        data[k, 7] = row.Column7
+        k += 1
+    end
+    data = normalize(data)
+
+    if !sep
+        return data
+    end
+
+    # Separate data
+    indexes_csv = CSV.File("data/indexes.csv")
+    indexes_tr = trunc.(Int, indexes_csv.columns[1])
+    indexes_te = purge(trunc.(Int, indexes_csv.columns[2]))
+    indexes_val = purge(trunc.(Int, indexes_csv.columns[3]))
+
+    # Create data
+    train_datax = data[indexes_tr, 1:6]
+    train_datay = data[indexes_tr, 7:end]
+
+    test_datax = data[indexes_te, 1:6]
+    test_datay = data[indexes_te, 7:end]
+
+    val_datax = data[indexes_val, 1:6]
+    val_datay = data[indexes_val, 7:end]
+
+    return (train_datax, train_datay), (test_datax, test_datay),
+           (val_datax, val_datay)
 end

### 2020-11-13 src/modules/Tools.jl
[ src ] Added meshgrid method.

@@ -12,7 +12,7 @@ function purge(indexes :: Vector{Int64})
 end
 
 # Get data
-function create_data(name_file :: String, sep = true)
+function create_data(name_file :: String; sep = true)
     # Data reading
     data_csv = CSV.File("data/num-data.csv")
     data = zeros(length(data_csv), 7)
@@ -30,7 +30,7 @@ function create_data(name_file :: String, sep = true)
     data = normalize(data)
 
     if !sep
-        return data
+        return data[:, 1:6], data[:, 7:end]
     end
 
     # Separate data
@@ -52,3 +52,18 @@ function create_data(name_file :: String, sep = true)
     return (train_datax, train_datay), (test_datax, test_datay),
            (val_datax, val_datay)
 end
+
+# Meshgrid
+function meshgrid(data, n)
+    mins = minimum(data, dims = 1)
+    maxs = maximum(data, dims = 1)
+    ranges = [mins[j]:(maxs[j] - mins[j])/n:maxs[j] for j in 1:length(mins)]
+
+    # Grid generation
+    grid = reshape(collect(Iterators.product(ranges...)), 1, :)
+
+    # Array creation
+    array = vcat(map(x -> transpose(collect(x)), grid)...)
+
+    return array
+end;

### 2020-11-13 src/SVM.jl
[ src ] Added initial SVM test.

@@ -1,0 +1,40 @@
+# ==== Global behavior ==== #
+using ScikitLearn
+include("modules/Tools.jl")
+
+@sk_import svm: SVC
+
+# ==== Functions ==== #
+function generate_results(svm, name_file :: String, data_name :: String,
+                          kernel :: String, n = 10)
+    datax, _ = create_data(data_name, sep = false)
+    class = svm.predict(datax)
+
+    # File
+    open(name_file, "a") do io
+        write(io, string("Kernel,", kernel, "\n"))
+
+        # Classification
+        write(io, "Classification\n")
+        for num in class
+            write(io, string(num, "\n"))
+        end
+
+        # Meshgrid
+        mesh = meshgrid(datax, n)
+        Z = decision_function(svm, mesh)
+    end
+end
+
+# ==== Main ==== #
+# Data
+train_data, _, _ = create_data("data/num-data.csv")
+
+train_datax = train_data[1]
+train_datay = train_data[2]
+
+# SVM
+svm = SVC(kernel = "linear")
+fit!(svm, train_datax, reshape(train_datay, :))
+generate_results(svm, "../results/svm-results.csv", "data/num-data.csv",
+                 "Linear")

### 2020-11-15 article/article.tex
[ article ] finished introduction

@@
 classifying the data from the survey, aiming for the construction of a model to
-detect individuals with mental health issues. This document is organized as
-follows: Section \ref{sec:start} gives a short review of the current literature
-of supervised techniques in this application area, Section \ref{sec:meth} shows
-the general methodology used in this work, moreover Section \ref{sec:res} shows
-the obtained results over the data and slight modifications, finally Section
-\ref{sec:conc} concludes this work and sets pillars for future works.
+detect individuals with mental health issues. Recent developments and the
+increasing popularity of supervised techniques has contributed to their
+application in different areas, among them, mental health.
 
-\section{State of the Art}\label{sec:start}
+The novel work by \textcite{thieme2020} makes and excellent literature review of
+Machine Learning (ML) in mental health, including the current state-of-the-art
+and formulates new strategies for integrating human-oriented research with
+multi-disciplinary. They also conclude that ML applied in mental health is
+``still in its infancy'' given the complexity and difficulties of constructing
+robust models for clinically reliable outputs.
+
+Additionally, the work presented by \textcite{shatte2019} is also a complete
+compendium of recent ML applications in mental health, including the usage
+of Support Vector Machines (SVMs), Decision Trees (DTs), Neural Networks (NN)
+and beyond. This paper includes a systematic review of over three hundred papers
+and it concludes that these techniques have brought benefits 
+across the areas of diagnosis, treatment, research and clinical administration.
+
+Finally, another overview of applications of Artificial Intelligence (AI) for Mental 
+Illnesses is the research published by \textcite{graham2019}, where the authors
+reviewed 28 research papers which include modern methodologies (and 
+technologies) for predicting or classifying psychological illnesses such as 
+depression, schizophrenia or suicidal behavior. The study discusses how the
+application of AI techniques supports the clinical practice while considering its
+limitations, it also presents some ethical implications and states which areas need
+further development.
+
+This document is organized as
+follows: Section \ref{sec:meth} shows the general methodology used in this work,
+moreover Section \ref{sec:res} shows the obtained results over the data and
+slight modifications, finally Section \ref{sec:conc} concludes this work and
+sets pillars for future works.
 

### 2020-11-15 src/SVM.jl
[ src ] Completed SVM result generation:

@@ -5,8 +5,23 @@ include("modules/Tools.jl")
 @sk_import svm: SVC
 
 # ==== Functions ==== #
+function generate_meshgrid(data_name :: String, name_file :: String; n = 10)
+    datax, _ = create_data(data_name, sep = false)
+    mesh = meshgrid(datax, n)
+    open(name_file, "w") do io
+        write(io, "Meshgrid\n")
+        for i in 1:size(mesh, 1)
+            for j in 1:size(mesh, 2)
+                write(io, string(mesh[i, j], ","))
+            end
+            write(io, "\n")
+        end
+    end
+    return mesh
+end
+
 function generate_results(svm, name_file :: String, data_name :: String,
-                          kernel :: String, n = 10)
+                          kernel :: String, mesh :: Matrix{Float64}; n = 5)
     datax, _ = create_data(data_name, sep = false)
     class = svm.predict(datax)
 
@@ -21,8 +36,11 @@ function generate_results(svm, name_file :: String, data_name :: String,
         end
 
         # Meshgrid
-        mesh = meshgrid(datax, n)
         Z = decision_function(svm, mesh)
+        write(io, "Meshgrid\n")
+        for i in 1:length(Z)
+            write(io, string(Z[i], "\n"))
+        end
     end
 end
 
@@ -34,7 +52,17 @@ train_datax = train_data[1]
 train_datay = train_data[2]
 
 # SVM
-svm = SVC(kernel = "linear")
-fit!(svm, train_datax, reshape(train_datay, :))
-generate_results(svm, "../results/svm-results.csv", "data/num-data.csv",
-                 "Linear")
+kernels = ["linear", "rbf", "poly"]
+
+# Files
+data_name = "data/num-dats.csv"
+meshgrid_file = "../results/meshgrid.csv"
+svm_results = "../results/svm-results.csv"
+
+# Output
+mesh = generate_meshgrid(data_name, meshgrid_file, n = 5)
+for kernel in kernels
+    svm = SVC(kernel = kernel)
+    fit!(svm, train_datax, reshape(train_datay, :))
+    generate_results(svm, svm_results, data_name, kernel, mesh)
+end

### 2020-11-15 src/modules/Tools.jl
[ src ] Corrected data normalization.

@@ -2,7 +2,7 @@ using CSV
 
 # Normalize data
 function normalize(data)
-    return data ./ maximum(data, dims = 1)
+    return data ./ maximum(abs.(data), dims = 1)
 end
 
 # Clean indexes

### 2020-11-15 src/SVM.jl
[ src ] Moved function to tools.

@@ -20,29 +20,6 @@ function generate_meshgrid(data_name :: String, name_file :: String; n = 10)
     return mesh
 end
 
-function generate_results(svm, name_file :: String, data_name :: String,
-                          kernel :: String, mesh :: Matrix{Float64}; n = 5)
-    datax, _ = create_data(data_name, sep = false)
-    class = svm.predict(datax)
-
-    # File
-    open(name_file, "a") do io
-        write(io, string("Kernel,", kernel, "\n"))
-
-        # Classification
-        write(io, "Classification\n")
-        for num in class
-            write(io, string(num, "\n"))
-        end
-
-        # Meshgrid
-        Z = decision_function(svm, mesh)
-        write(io, "Meshgrid\n")
-        for i in 1:length(Z)
-            write(io, string(Z[i], "\n"))
-        end
-    end
-end
 
 # ==== Main ==== #
 # Data
@@ -64,5 +41,7 @@ mesh = generate_meshgrid(data_name, meshgrid_file, n = 5)
 for kernel in kernels
     svm = SVC(kernel = kernel)
     fit!(svm, train_datax, reshape(train_datay, :))
-    generate_results(svm, svm_results, data_name, kernel, mesh)
+    extra_info = string("Kernel,", kernel)
+    generate_results(svm, svm_results, data_name, kernel, mesh,
+                     extra_info=extra_info)
 end

### 2020-11-15 src/modules/Tools.jl

@@ -67,3 +67,31 @@ function meshgrid(data, n)
 
     return array
 end;
+
+# Generate results for classifier
+function generate_results(clf, name_file :: String, data_name :: String,
+                          kernel :: String, mesh :: Matrix{Float64};
+                          extra_info = "")
+    datax, _ = create_data(data_name, sep = false)
+    class = clf.predict(datax)
+
+    # File
+    open(name_file, "a") do io
+        if length(extra_info) != 0
+            write(io, string(extra_info, "\n"))
+        end
+
+        # Classification
+        write(io, "Classification\n")
+        for num in class
+            write(io, string(num, "\n"))
+        end
+
+        # Meshgrid
+        Z = decision_function(clf, mesh)
+        write(io, "Meshgrid\n")
+        for i in 1:length(Z)
+            write(io, string(Z[i], "\n"))
+        end
+    end
+end

### 2020-11-15 src/SVM.jl
[ src ] Printed header in meshgrid file.

@@ -9,7 +9,7 @@ function generate_meshgrid(data_name :: String, name_file :: String; n = 10)
     datax, _ = create_data(data_name, sep = false)
     mesh = meshgrid(datax, n)
     open(name_file, "w") do io
-        write(io, "Meshgrid\n")
+        write(io, "X1,X2,X3,X4,X5,X6\n")
         for i in 1:size(mesh, 1)
             for j in 1:size(mesh, 2)
                 write(io, string(mesh[i, j], ","))

### 2020-11-15 src/SVM.jl
[ src ] Corrected CSV formatting.

@@ -12,9 +12,12 @@ function generate_meshgrid(data_name :: String, name_file :: String; n = 10)
         write(io, "X1,X2,X3,X4,X5,X6\n")
         for i in 1:size(mesh, 1)
             for j in 1:size(mesh, 2)
-                write(io, string(mesh[i, j], ","))
+                if j == size(mesh, 2)
+                    write(io, string(mesh[i, j], "\n"))
+                else
+                    write(io, string(mesh[i, j], ","))
+                end
             end
-            write(io, "\n")
         end
     end
     return mesh

### 2020-11-15 src/SVM.jl
[ src ] Remove redundant parameter.

@@ -45,6 +45,5 @@ for kernel in kernels
     svm = SVC(kernel = kernel)
     fit!(svm, train_datax, reshape(train_datay, :))
     extra_info = string("Kernel,", kernel)
-    generate_results(svm, svm_results, data_name, kernel, mesh,
-                     extra_info=extra_info)
+    generate_results(svm, svm_results, data_name, mesh, extra_info=extra_info)
 end

### 2020-11-15 src/modules/Tools.jl

@@ -70,8 +70,7 @@ end;
 
 # Generate results for classifier
 function generate_results(clf, name_file :: String, data_name :: String,
-                          kernel :: String, mesh :: Matrix{Float64};
-                          extra_info = "")
+                          mesh :: Matrix{Float64}; extra_info = "")
     datax, _ = create_data(data_name, sep = false)
     class = clf.predict(datax)
 

### 2020-11-15 src/modules/Tools.jl
[ src ] Added compliance with other classifiers.

@@ -87,7 +87,12 @@ function generate_results(clf, name_file :: String, data_name :: String,
         end
 
         # Meshgrid
-        Z = decision_function(clf, mesh)
+        Z = nothing
+        try
+            Z = decision_function(clf, datax)
+        catch
+            Z = predict_proba(clf, datax)[:, 2]
+        end
         write(io, "Meshgrid\n")
         for i in 1:length(Z)
             write(io, string(Z[i], "\n"))

### 2020-11-15 src/modules/Tools.jl
[ src ] Corrected mesh:

@@ -89,9 +89,9 @@ function generate_results(clf, name_file :: String, data_name :: String,
         # Meshgrid
         Z = nothing
         try
-            Z = decision_function(clf, datax)
+            Z = decision_function(clf, mesh)
         catch
-            Z = predict_proba(clf, datax)[:, 2]
+            Z = predict_proba(clf, mesh)[:, 2]
         end
         write(io, "Meshgrid\n")
         for i in 1:length(Z)

### 2020-11-16 src/NN.jl
[ src ] Change output to best and worst ones NN.

@@ -19,7 +19,8 @@ function get_neuron_combinations(L :: Int64, ls :: Vector{Int64})
 end
 
 function write_info_run(grads :: Matrix{Float64}, avg_err :: Vector{Float64},
-                        name_file :: String, η :: Float64, ls :: Vector{Int64})
+                        name_file :: String, η :: Float64, ls :: Vector{Int64},
+                        Z :: Vector{Float64})
     open(name_file, "a") do io
         # Write run information
         write(io, string("eta,", η, "\n"))
@@ -42,41 +43,94 @@ function write_info_run(grads :: Matrix{Float64}, avg_err :: Vector{Float64},
         for i in 1:length(avg_err)
             write(io, string(avg_err[i], "\n"))
         end
+
+        write(io, "Output\n")
+        for i in 1:length(Z)
+            write(io, string(Z[i], "\n"))
+        end
     end
 end
 
-function run_brain(η :: Float64, ls :: Vector{Int64}, tr_datax :: Matrix{Float64},
-                   tr_datay :: Matrix{Float64}, name_file :: String)
-    # Activation function
-    sig = Sigmoid()
+function write_brain(brain :: Brain, grads :: Matrix{Float64},
+                     avg_err :: Matrix{Float64}, η :: Float64,
+                     name_file :: String)
+    # Number of neurons
+    ls = Vector{Int64}([])
+    for ω in brain.ω[1:(end-1)]
+        push!(ls, size(ω, 2))
+    end
 
-    # Brain
-    brain = Brain(size(tr_datax, 2), size(tr_datay, 2), ls,
-                  [sig for i in 1:(length(ls) + 1)])
-    grads, avg_err = brain.learn_data(tr_datax, tr_datay, η=η, α=0.1, epocs=50)
-    avg_err = reshape(sum(avg_err, dims = 2), :)
+    # Output of NN
+    datax, _ = create_data("data/num-data.csv", sep = false)
+    Z = zeros(size(datax, 1))
+    for i in 1:size(datax, 1)
+        Z[i] = brain.propagate(datax[i, :])[1, 1]
+    end
 
-    # File writing
-    write_info_run(grads, avg_err, name_file, η, ls)
+    # Write data
+    write_info_run(grads, reshape(avg_err, :), name_file, η, ls, Z)
 end
 
 # ====== Main ====== #
 train_data, _, _ = create_data("data/num-data.csv")
[…]

### 2020-11-16 article/article.tex

@@
 \section{Methodology}\label{sec:meth}
+All the code developed for this work was implemented in Julia 1.5.3. and 
+can be found in the authors'
+\href{https://github.com/juanscr/ai-works}{GitHub repository}.
+
+\subsection{Survey}
+The used survey for extracting data was initially designed for developing
+a Fuzzy inference expert system, but the data was labeled according to
+unsupervised clustering techniques, obtaining 2 clusters through the subtractive
+algorithm \parencite{chiu1994} and then sharpened using Fuzzy-C-Means 
+\parencite{dunn1973}. The data has 6 variables and 113 observations.
+
+\subsection{Support Vector Machines}
+We refer to \textcite{burges1998} for the theoretical background on Support
+Vector Machines (SVMs).
+
+\subsection{Decision Trees}
+We refer to
+
+\subsection{Neural Networks}
+We refer to \textcite{aggarwal2018} for the formulation of the Neural Netwok 
+(NN) learning machine and the details of its implementation, such as the 
+backpropagation algorithm for training and the bias correction. The NN was
+implemented by the authors, including the bias correction and the
 

### 2020-11-16 src/plotting/Brain.py
[ src ] Added plotters for brain and data creation.

@@ -1,0 +1,109 @@
+#!/usr/bin/env python3
+
+# ==== Global behavior ==== #
+from GetData import create_data
+import matplotlib.pyplot as plt
+import numpy as np
+
+from matplotlib import rc
+from sklearn.metrics import roc_curve, auc
+
+rc('text', usetex=True)
+save = lambda x: plt.savefig("../../results/figs/" + x, bbox_inches='tight')
+
+# ==== Brain ==== #
+class Brain:
+    def __init__(self, brain_data):
+        self.eta = 0
+        self.ls = []
+        self.grads = []
+        self.err = []
+        self.out = []
+        self.get_brain_from_string(brain_data)
+
+    def get_brain_from_string(self, brain_data):
+        # Eta
+        self.eta = float(brain_data[0][1:])
+
+        # Number of neurons
+        self.ls = list(map(int, brain_data[1].split(",")[1:-1]))
+
+        # Gradients
+        for i in range(3, 53):
+            self.grads.append(brain_data[i].split(",")[:-1])
+        self.grads = np.array(self.grads, dtype=float)
+
+        # Error
+        for i in range(54, 104):
+            self.err.append(brain_data[i][:-1])
+        self.err = np.array(self.err, dtype=float)
+
+        # Output
+        for i in range(105, len(brain_data) - 1):
+            self.out.append(brain_data[i][:-1])
+        self.out = np.array(self.out, dtype=float)
+
+    @staticmethod
+    def read_brains(name_file):
+        brain_csv = open(name_file).read().split("eta")
+        brain_csv = list(map(lambda x: x.split("\n"), brain_csv))[1:]
+
+        # Create each brain
+        brains = []
+        for brain_data in brain_csv:
+            brains.append(Brain(brain_data))
+
+        return brains
+
+    def plotmemaybe(self):
+        prefix = ""
+        for l in self.ls:
+            prefix += str(l) + "-"
+        prefix += str(self.eta) + "-"
+
+        # Plot information
+        self.plot_grads(prefix + "gradients.pdf")
+        self.plot_err(prefix + "error.pdf")
+        self.plot_roc(prefix + "roc.pdf")
+
+    def plot_grads(self, name_file):
+        epocs = range(1, 51)
+        for i in range(self.grads.shape[1]):
+            plt.plot(epocs, self.grads[:, i], label="$l={}$".format(i + 1))
[…]

### 2020-11-16 src/plotting/GetData.py

@@ -1,0 +1,50 @@
+#!/usr/bin/env python3
+
+import numpy as np
+
+def normalize(data):
+    return data / np.max(np.abs(data), axis=0)
+
+def purge(column):
+    index = np.where(column == -2)[0][0]
+    return column[:index]
+
+def create_data(name_file, index_file, sep=True):
+    data_csv = open(name_file).readlines()[1:]
+    data = np.zeros((len(data_csv), 7))
+    k = 0
+    for row in data_csv:
+        data[k, :] = list(map(float, row.split(",")))
+        k += 1
+
+    data = normalize(data)
+
+    if not sep:
+        return data[:, :6], data[:, 6:]
+
+    # Separate data
+    indexes_csv = open(index_file).readlines()[1:]
+    indexes = np.zeros((len(indexes_csv), 3), dtype=int)
+    k = 0
+    for row in indexes_csv:
+        indexes[k, :] = list(map(lambda x: int(float(x)), row.split(",")))
+        k += 1
+    indexes = indexes - 1
+
+    # Indexes
+    indexes_tr = indexes[:, 0]
+    indexes_te = purge(indexes[:, 1])
+    indexes_val = purge(indexes[:, 2])
+
+    # Data creation
+    train_datax = data[indexes_tr, :6]
+    train_datay = data[indexes_tr, 6:]
+
+    test_datax = data[indexes_te, :6]
+    test_datay = data[indexes_te, 6:]
+
+    val_datax = data[indexes_val, :6]
+    val_datay = data[indexes_val, 6:]
+
+    return (train_datax, train_datay), (test_datax, test_datay),\
+           (val_datax, val_datay)

### 2020-11-16 src/plotting/Brain.py
[ src ] Change direction of plots.

@@ -9,7 +9,7 @@ from matplotlib import rc
 from sklearn.metrics import roc_curve, auc
 
 rc('text', usetex=True)
-save = lambda x: plt.savefig("../../results/figs/" + x, bbox_inches='tight')
+save = lambda x: plt.savefig("../../article/figs/" + x, bbox_inches='tight')
 
 # ==== Brain ==== #
 class Brain:

### 2020-11-16 src/Tree.jl
[ src ] Saved tree classifier.

@@ -1,8 +1,10 @@
 # ==== Global behavior ==== #
 using CSV
+using PyCall
 using ScikitLearn
 include("modules/Tools.jl")
 
+@pyimport joblib
 @sk_import tree: DecisionTreeClassifier
 
 # ==== Function ==== #
@@ -37,3 +39,7 @@ dt = DecisionTreeClassifier(criterion = "entropy")
 mesh = read_meshgrid("../results/meshgrid.csv")
 fit!(dt, train_datax, reshape(train_datay, :))
 generate_results(dt, dt_results, data_name, mesh)
+
+# Save tree
+save_model = "../results/tree.joblib"
+joblib.dump(dt, save_model)

### 2020-11-16 src/Tree.jl
[ src ] Unnormalized data.

@@ -29,7 +29,7 @@ data_name = "data/num-dats.csv"
 dt_results = "../results/dt-results.csv"
 
 # Data
-train_data, _, _ = create_data("data/num-data.csv")
+train_data, _, _ = create_data("data/num-data.csv", norm = false)
 
 train_datax = train_data[1]
 train_datay = train_data[2]

### 2020-11-16 src/modules/Tools.jl
[ src ] Added option to normalize data.

@@ -12,7 +12,7 @@ function purge(indexes :: Vector{Int64})
 end
 
 # Get data
-function create_data(name_file :: String; sep = true)
+function create_data(name_file :: String; sep = true, norm = true)
     # Data reading
     data_csv = CSV.File("data/num-data.csv")
     data = zeros(length(data_csv), 7)
@@ -27,7 +27,9 @@ function create_data(name_file :: String; sep = true)
         data[k, 7] = row.Column7
         k += 1
     end
-    data = normalize(data)
+    if norm
+        data = normalize(data)
+    end
 
     if !sep
         return data[:, 1:6], data[:, 7:end]

### 2020-11-16 src/plotting/Tree.py
[ src ] Added initial code for tree plotting.

@@ -1,0 +1,44 @@
+#!/usr/bin/env python3
+
+# ==== Global behavior ==== #
+import graphviz
+import matplotlib.pyplot as plt
+import numpy as np
+import sklearn.tree as tree
+
+from GetData import create_data
+from joblib import load
+from matplotlib import rc
+
+rc('text', usetex=True)
+save = lambda x: plt.savefig("../../article/figs/" + x, bbox_inches='tight')
+
+# ==== Tree ==== #
+class Tree:
+    def __init__(self, clas, output, tree_joblib, feature_names, clas_names):
+        self.clas = clas
+        self.output = output
+        self.tree = load(tree_joblib)
+        self.feature_names = feature_names
+        self.clas_names = clas_names
+
+    @staticmethod
+    def read_tree(name_file):
+        print("holi")
+
+    def plotmemaybe(self):
+        prefix = "tree-"
+
+        # Plot information
+        self.plot_tree(prefix + "graph.pdf")
+
+
+    def plot_tree(self, name_file):
+        dot_data = tree.export_graphviz(self.tree,
+                                        out_file=None,
+                                        feature_names=self.feature_names,
+                                        class_names=self.clas_names,
+                                        filled=True, rounded=True,
+                                        special_characters=True)
+        graph = graphviz.Source(dot_data)
+        graph.render(name_file)

### 2020-11-16 src/Tree.jl
[ src ] Normalize data.

@@ -29,7 +29,7 @@ data_name = "data/num-dats.csv"
 dt_results = "../results/dt-results.csv"
 
 # Data
-train_data, _, _ = create_data("data/num-data.csv", norm = false)
+train_data, _, _ = create_data("data/num-data.csv")
 
 train_datax = train_data[1]
 train_datay = train_data[2]

### 2020-11-16 src/plotting/GetData.py
[ src ] Added meshgrid creation.

@@ -2,13 +2,16 @@
 
 import numpy as np
 
+# Normalize data
 def normalize(data):
     return data / np.max(np.abs(data), axis=0)
 
+# Purge columns
 def purge(column):
     index = np.where(column == -2)[0][0]
     return column[:index]
 
+# Create data set
 def create_data(name_file, index_file, sep=True):
     data_csv = open(name_file).readlines()[1:]
     data = np.zeros((len(data_csv), 7))
@@ -48,3 +51,13 @@ def create_data(name_file, index_file, sep=True):
 
     return (train_datax, train_datay), (test_datax, test_datay),\
            (val_datax, val_datay)
+
+# Create meshgrid
+def create_meshgrid(name_file):
+    mesh_csv = open(name_file).readlines()[1:]
+    mesh = np.zeros((len(mesh_csv), 6))
+    k = 0
+    for row in mesh_csv:
+        mesh[k, :] = list(map(float, row.split(",")))
+        k += 1
+    return mesh

### 2020-11-16 src/Tree.jl
[ src ] Removed useless export.

@@ -38,7 +38,6 @@ train_datay = train_data[2]
 dt = DecisionTreeClassifier(criterion = "entropy")
 mesh = read_meshgrid("../results/meshgrid.csv")
 fit!(dt, train_datax, reshape(train_datay, :))
-generate_results(dt, dt_results, data_name, mesh)
 
 # Save tree
 save_model = "../results/tree.joblib"

### 2020-11-16 src/plotting/Tree.py
[ src ] Finished exporting tree.

@@ -6,31 +6,27 @@ import matplotlib.pyplot as plt
 import numpy as np
 import sklearn.tree as tree
 
-from GetData import create_data
+from GetData import create_data, create_meshgrid
 from joblib import load
 from matplotlib import rc
 
 rc('text', usetex=True)
-save = lambda x: plt.savefig("../../article/figs/" + x, bbox_inches='tight')
+dir_of_file = lambda x: "../../article/figs/" + x
+save = lambda x: plt.savefig(dir_of_file(x), bbox_inches='tight')
 
 # ==== Tree ==== #
 class Tree:
-    def __init__(self, clas, output, tree_joblib, feature_names, clas_names):
-        self.clas = clas
-        self.output = output
+    def __init__(self, tree_joblib, feature_names, clas_names):
         self.tree = load(tree_joblib)
         self.feature_names = feature_names
         self.clas_names = clas_names
 
-    @staticmethod
-    def read_tree(name_file):
-        print("holi")
-
-    def plotmemaybe(self):
+    def plotmemaybe(self, n=10):
         prefix = "tree-"
 
         # Plot information
-        self.plot_tree(prefix + "graph.pdf")
+        self.plot_tree(prefix + "graph")
+        self.plot_contour(prefix + "contour-", n)
 
 
     def plot_tree(self, name_file):
@@ -41,4 +37,66 @@ class Tree:
                                         filled=True, rounded=True,
                                         special_characters=True)
         graph = graphviz.Source(dot_data)
-        graph.render(name_file)
+        graph.render(dir_of_file(name_file))
+
+    def plot_contour(self, name_file, n):
+        datax, datay = create_data("../data/num-data.csv", "../data/indexes.csv",
+                                   sep=False)
+        datay = np.resize(datay, datay.shape[0])
+
+        # Meshgrid
+        ranges = []
+        for i in range(datax.shape[1]):
+            ranges.append(np.linspace(datax[:, i].min(), datax[:, i].max(), n))
+        mesh = np.meshgrid(*ranges)
+
+        # Evaluate tree
+        mesh_fl = list(map(lambda x : x.flatten(), mesh))
+        mesh_col = list(map(lambda x : np.reshape(x, (x.size, 1)), mesh_fl))
+        mesh_h = np.hstack(mesh_col)
+        output = tree.DecisionTreeClassifier.predict(self.tree, mesh_h)
+
+        # Plot each contour
+        for i in range(3):
[…]

### 2020-11-17 article/article.tex
[ article ] added plots
[ article ] added NN methodology

--- 2020-11-15 article/article.tex
@@
 \section{Methodology}\label{sec:meth}
+All the code developed for this work was implemented in Julia 1.5.3. and
+can be found in the authors'
+\href{https://github.com/juanscr/ai-works}{GitHub repository}.
+
+\subsection{Survey}
+The used survey for extracting data was initially designed for developing
+a Fuzzy Inference System, but the data was labeled according to
+unsupervised clustering techniques, obtaining 2 clusters through the subtractive
+algorithm \parencite{chiu1994} and then sharpened using Fuzzy-C-Means
+\parencite{dunn1973}. The data has 6 variables and 113 observations. This
+dataset was divided with the standard $60-20-20$ rule, creating a training
+dataset with $60\%$ of the complete data, a validation set with $20\%$ and a
+test set with $20\%$ as well. All data was normalized by dividing each dimension
+by its maximum (in absolute value), casting the data into the [-1,1] hypercube.
+
+\subsection{Support Vector Machines}
+\textcite{burges1998} published an excellent reference for the theoretical
+background on SVMs with different kernels and explains the formulation of the
+optimization problem. The SVMs were used directly from Scikit-Learn
+\parencite{scikit-learn, sklearn_api} using
+\href{https://bit.ly/3lDHADX}{Julia's API}. The SVMs were trained using three
+different kernels: linear, polynomial and RBF (radial base function).
+
+\subsection{Decision Trees}
+We refer to \textcite{bramer2007} for the general ideas behind the decision tree
+classifier.
+
+\subsection{Neural Networks}
+The book of \textcite{aggarwal2018} was used as primary reference for the
+formulation of the NN learning machine and the details of its implementation,
+such as the backpropagation algorithm and the bias correction.
+The NN was implemented by the authors, including the bias correction and the
+momentum acceleration term.
+
+The NNs trained used a fully-connected Multi-Layer Perceptron (MLP) using
+different number of neurons and different learning rates. The detailed process
+will be now described: let $L$ be the number of hidden layers in the MLP and let
+$\mathcal{L}\in\mathbb{R}^{L}$ be a vector containing the number of neurons on
+each hidden layer. The number of hidden layers was varied as $L=1,2,3$ and let
+$l_i$ be the number of neurons in the $i$-th layer of the MLP, hence, each
+$l_i\in\mathcal{L}$ was varied in $1,2,3$ as well. This gives a total of
+$3^1+3^2+3^3=39$ different permutations just for the architecture of the MLP,
+and this was repeated for learning rates as $\eta=0.2,0.5,0.9$, yielding a total
+of $117$ NNs to be trained.
+
+All $117$ MLPs were trained sequentially, fixing a maximum of 50 epochs,
+and only the main results for the two bests and for the worst MLP configurations
+will be presented, in order to keep this paper concrete. The order relation
+between the trained NNs was established by evaluating the cost function at the
+end of the final epoch. All MLPs used the sigmoid activation function.
+
+The results are presented using three learning curves: the sum of local
+gradients per layer at the end of each epoch, the average error energy and a
+Receiver Operating Characteristic (ROC) curve, comparing the obtained results
+with the real labels.
+\begin{itemize}
+  \item The sum of gradients per layer at the end of each epoch is an approach
+  visualizing if the training algorithm is solving the optimization problem,
+  since the sum of local gradients must converge to zero as each gradient
+  converges to zero. It is well-known that the vanish of gradients is a
+  necessary condition for optimality and the training algorithm is just an
+  optimization problem minimizing the output error (cost function).
+  \item The average error energy is the cost function of the optimization
+  problem. Let $y_i\in\mathbb{R}^n$ be the real output of a given input pattern
+  $x_i\in\mathbb{R}^m$ and let $\hat{y}_i\in\mathbb{R}^n$ be the output of the
+  NN for the same input pattern. Denoting each component by superscripts, the
+  average error energy $\xi_{av}$ on each epoch is then computed as
+  \begin{equation}
+    \xi_{av}=\dfrac{1}{2}\sum_{i=1}^{N}\sum_{k=1}^n\left(y^k_i-\hat{y}^k_i\right)^2,
+  \end{equation}
+  where $N$ is the training sample size. Thus, it is clear that
+  $\xi_{av}\rightarrow0$ as the training algorithm solves the learning problem
+  well.
+  \item The ROC curve is a tool that helps visualize the correct clasifications
+  of the learning machine by plotting the true positive rate on the vertical
+  axis, and false positive rate on the horizontal axis. The Area Under the Curve
+  (AUC) is an indicator of how good the data is being classified by the model,
+  with higher values being better usually better.
+\end{itemize}
 
 \section{Results}\label{sec:res}
+\subsection{Support Vector Machines}
+
+\subsection{Decision Trees}
+\begin{figure}
+    \includegraphics[width=\columnwidth]{figs/tree-graph.pdf}
+    \caption{Decision tree.}
+    \label{fig:dt}
+\end{figure}
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/tree-contour-0-3.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/tree-contour-0-4.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/tree-contour-0-5.pdf}
+        \caption{}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/tree-contour-1-3.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/tree-contour-1-4.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/tree-contour-1-5.pdf}
+        \caption{}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/tree-contour-2-3.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/tree-contour-2-4.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/tree-contour-2-5.pdf}
+        \caption{}
+    \end{subfigure}
+    \caption{Decision Tree contour with real labels.}
+    \label{fig:dts}
+\end{figure*}
+
+\subsection{Neural Networks}
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/1-2-3-0.9-gradients.pdf}
+        \caption{Gradients for each layer.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/1-2-3-0.9-error.pdf}
+        \caption{Average error energy per epoch.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/1-2-3-0.9-roc.pdf}
+        \caption{ROC curve.}
+    \end{subfigure}
+    \caption{Learning curves for $\mathcal{L}=[1,2,3]$ network (worst).}
+    \label{fig:NN-worst}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/2-0.9-gradients.pdf}
+        \caption{Gradients for each layer.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/2-0.9-error.pdf}
+        \caption{Average error energy per epoch.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/2-0.9-roc.pdf}
+        \caption{ROC curve.}
+    \end{subfigure}
+    \caption{Learning curves for $\mathcal{L}=[2]$ network (2nd best).}
+    \label{fig:NN-2best}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/3-0.9-gradients.pdf}
+        \caption{Gradients for each layer.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/3-0.9-error.pdf}
+        \caption{Average error energy per epoch.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/3-0.9-roc.pdf}
+        \caption{ROC curve.}
+    \end{subfigure}
+    \caption{Learning curves for $\mathcal{L}=[3]$ network (best).}
+    \label{fig:NN-best}
+\end{figure*}
 
@@
 \printbibliography
+
 \end{document}

### 2020-11-17 src/SVM.jl
[ src ] Exported joblib file.

@@ -1,28 +1,10 @@
 # ==== Global behavior ==== #
+using PyCall
 using ScikitLearn
 include("modules/Tools.jl")
 
+@pyimport joblib
 @sk_import svm: SVC
-
-# ==== Functions ==== #
-function generate_meshgrid(data_name :: String, name_file :: String; n = 10)
-    datax, _ = create_data(data_name, sep = false)
-    mesh = meshgrid(datax, n)
-    open(name_file, "w") do io
-        write(io, "X1,X2,X3,X4,X5,X6\n")
-        for i in 1:size(mesh, 1)
-            for j in 1:size(mesh, 2)
-                if j == size(mesh, 2)
-                    write(io, string(mesh[i, j], "\n"))
-                else
-                    write(io, string(mesh[i, j], ","))
-                end
-            end
-        end
-    end
-    return mesh
-end
-
 
 # ==== Main ==== #
 # Data
@@ -40,10 +22,10 @@ meshgrid_file = "../results/meshgrid.csv"
 svm_results = "../results/svm-results.csv"
 
 # Output
-mesh = generate_meshgrid(data_name, meshgrid_file, n = 5)
+prefix = "../results/svm-"
 for kernel in kernels
     svm = SVC(kernel = kernel)
     fit!(svm, train_datax, reshape(train_datay, :))
-    extra_info = string("Kernel,", kernel)
-    generate_results(svm, svm_results, data_name, mesh, extra_info=extra_info)
+    joblib.dump(svm, string(prefix, kernel, ".joblib"))
+
 end

### 2020-11-17 src/Tree.jl
[ src ] Removed unused function.

@@ -7,22 +7,6 @@ include("modules/Tools.jl")
 @pyimport joblib
 @sk_import tree: DecisionTreeClassifier
 
-# ==== Function ==== #
-function read_meshgrid(name_file :: String)
-    rows = CSV.Rows(name_file)
-
-    # Mesh
-    mesh = []
-    for row in rows
-        row_data = zeros(6)
-        for i in 1:6
-            row_data[i] = parse(Float64, row[i])
-        end
-        push!(mesh, row_data)
-    end
-    return collect(transpose(hcat(mesh...)))
-end
-
 # ==== Main ==== #
 # Files
 data_name = "data/num-dats.csv"
@@ -36,7 +20,6 @@ train_datay = train_data[2]
 
 # Decision tree
 dt = DecisionTreeClassifier(criterion = "entropy")
-mesh = read_meshgrid("../results/meshgrid.csv")
 fit!(dt, train_datax, reshape(train_datay, :))
 
 # Save tree

### 2020-11-17 src/modules/Tools.jl
[ src ] Removed data generation.

@@ -54,50 +54,3 @@ function create_data(name_file :: String; sep = true, norm = true)
     return (train_datax, train_datay), (test_datax, test_datay),
            (val_datax, val_datay)
 end
-
-# Meshgrid
-function meshgrid(data, n)
-    mins = minimum(data, dims = 1)
-    maxs = maximum(data, dims = 1)
-    ranges = [mins[j]:(maxs[j] - mins[j])/n:maxs[j] for j in 1:length(mins)]
-
-    # Grid generation
-    grid = reshape(collect(Iterators.product(ranges...)), 1, :)
-
-    # Array creation
-    array = vcat(map(x -> transpose(collect(x)), grid)...)
-
-    return array
-end;
-
-# Generate results for classifier
-function generate_results(clf, name_file :: String, data_name :: String,
-                          mesh :: Matrix{Float64}; extra_info = "")
-    datax, _ = create_data(data_name, sep = false)
-    class = clf.predict(datax)
-
-    # File
-    open(name_file, "a") do io
-        if length(extra_info) != 0
-            write(io, string(extra_info, "\n"))
-        end
-
-        # Classification
-        write(io, "Classification\n")
-        for num in class
-            write(io, string(num, "\n"))
-        end
-
-        # Meshgrid
-        Z = nothing
-        try
-            Z = decision_function(clf, mesh)
-        catch
-            Z = predict_proba(clf, mesh)[:, 2]
-        end
-        write(io, "Meshgrid\n")
-        for i in 1:length(Z)
-            write(io, string(Z[i], "\n"))
-        end
-    end
-end

### 2020-11-17 src/DataGeneration.jl
[ src ] Printed embedded data.

@@ -50,18 +50,8 @@ end;
 data = collect(transpose(hcat(data...)))
 
 # ============ Embedded Data ============ #
-function plot_data(data)
-    scatter(data[:, 1], data[:, 2],
-            markersize = 5,
-            markerstrokewidth = 0,
-            label = false,
-            color = "black",
-            grid = false)
-end;
-
-data_emb = tsne(normalize(data))
-plot_data(data_emb)
-savefig("figs/embedded-data.pdf")
+data_emb = normalize(tsne(normalize(data)))
+CSV.write("data/embedded-data.csv", Tables.table(data_emb))
 
 # ============ Write new data ============ #
 function find_membership(data, dist, prototypes, args)

### 2020-11-17 src/DataGeneration.jl
[ src ] Exported embedded data.

@@ -51,7 +51,6 @@ data = collect(transpose(hcat(data...)))
 
 # ============ Embedded Data ============ #
 data_emb = normalize(tsne(normalize(data)))
-CSV.write("data/embedded-data.csv", Tables.table(data_emb))
 
 # ============ Write new data ============ #
 function find_membership(data, dist, prototypes, args)
@@ -86,6 +85,8 @@ u, _ = find_membership(data, euclidean, protos, [])
 final_data = [data reshape(u[1, :], size(data, 1), 1)]
 CSV.write("data/num-data.csv", Tables.table(final_data))
 
+final_data_emb = [data_emb reshape(u[1, :], size(data, 1), 1)]
+CSV.write("data/embedded-data.csv", Tables.table(final_data_emb))
 
 # ============ Separate data ============ #
 indexes = 1:size(data, 1)

### 2020-11-17 src/modules/Tools.jl
[ src ] Added other dimension compliance.

@@ -14,25 +14,17 @@ end
 # Get data
 function create_data(name_file :: String; sep = true, norm = true)
     # Data reading
-    data_csv = CSV.File("data/num-data.csv")
-    data = zeros(length(data_csv), 7)
-    k = 1
-    for row in data_csv
-        data[k, 1] = row.Column1
-        data[k, 2] = row.Column2
-        data[k, 3] = row.Column3
-        data[k, 4] = row.Column4
-        data[k, 5] = row.Column5
-        data[k, 6] = row.Column6
-        data[k, 7] = row.Column7
-        k += 1
+    data_col = CSV.File(name_file).columns
+    data = zeros(length(data_csv), length(columns))
+    for i in 1:length(columns)
+        data[:, i] = data_col[i]
     end
     if norm
         data = normalize(data)
     end
 
     if !sep
-        return data[:, 1:6], data[:, 7:end]
+        return data[:, 1:(end - 1)], data[:, end:end]
     end
 
     # Separate data
@@ -42,14 +34,14 @@ function create_data(name_file :: String; sep = true, norm = true)
     indexes_val = purge(trunc.(Int, indexes_csv.columns[3]))
 
     # Create data
-    train_datax = data[indexes_tr, 1:6]
-    train_datay = data[indexes_tr, 7:end]
+    train_datax = data[indexes_tr, 1:(end - 1)]
+    train_datay = data[indexes_tr, end:end]
 
-    test_datax = data[indexes_te, 1:6]
-    test_datay = data[indexes_te, 7:end]
+    test_datax = data[indexes_te, 1:(end - 1)]
+    test_datay = data[indexes_te, end:end]
 
-    val_datax = data[indexes_val, 1:6]
-    val_datay = data[indexes_val, 7:end]
+    val_datax = data[indexes_val, 1:(end - 1)]
+    val_datay = data[indexes_val, end:end]
 
     return (train_datax, train_datay), (test_datax, test_datay),
            (val_datax, val_datay)

### 2020-11-17 src/NN.jl
[ src ] Added embedded data.

@@ -71,10 +71,64 @@ function write_brain(brain :: Brain, grads :: Matrix{Float64},
     write_info_run(grads, reshape(avg_err, :), name_file, η, ls, Z)
 end
 
+function run_combinations(ηs :: Vector{Float64}, ls :: Vector{Int64},
+                          neurons :: Vector{Int64}, tr_datax :: Matrix{Float64},
+                          tr_datay :: Matrix{Float64}, selection_criterion,
+                          number_of_brains :: Int64)
+    # Activation functions
+    sig = Sigmoid()
+
+    # Run all combinations
+    for η in ηs
+        for l in ls
+            possible_neurons = get_neuron_combinations(l, neurons)
+            for i in 1:size(possible_neurons, 1)
+                ls_aux = possible_neurons[i, :]
+
+                # Run brain
+                brain = Brain(size(tr_datax, 2), size(tr_datay, 2), ls_aux,
+                            [sig for i in 1:(length(ls_aux) + 1)])
+                grads, avg_err = brain.learn_data(tr_datax, tr_datay, η=η,
+                                                α=0.1, epocs=50)
+                avg_err = sum(avg_err / size(avg_err, 2), dims = 2)
+
+                # Fill list
+                if length(selected_brains) < number_of_brains
+                    push!(selected_brains, (brain, grads, avg_err, η))
+                    sort!(selected_brains, by = selection_criterion)
+                    continue
+                end
+
+                # Replace list
+                err = selection_criterion((brain, grads, avg_err, η))
+
+                # Best ones
+                for i in 1:(number_of_brains - 1)
+                    if selection_criterion(selected_brains[i]) > err
+                        selected_brains[(i+1):(end - 1)] = selected_brains[i:(end - 2)]
+                        selected_brains[i] = (brain, grads, avg_err, η)
+                        break
+                    end
+                end
+
+                # Worst one
+                if selection_criterion(selected_brains[end]) < err
+                    selected_brains[end] = (brain, grads, avg_err, η)
+                end
+            end
+        end
+    end
+    return selected_brains
+end
+
 # ====== Main ====== #
 train_data, _, _ = create_data("data/num-data.csv")
 tr_datax = train_data[1]
 tr_datay = train_data[2]
+
+train_data_emb, _, _ = create_data("data/embedded-data.csv")
+tr_dataxe = train_data_emb[1]
+tr_dataye = train_data_emb[2]
 
[…]

### 2020-11-17 src/modules/Tools.jl
[ src ] Corrected columns errors.

@@ -15,8 +15,8 @@ end
 function create_data(name_file :: String; sep = true, norm = true)
     # Data reading
     data_col = CSV.File(name_file).columns
-    data = zeros(length(data_csv), length(columns))
-    for i in 1:length(columns)
+    data = zeros(length(data_col[1]), length(data_col))
+    for i in 1:length(data_col)
         data[:, i] = data_col[i]
     end
     if norm

### 2020-11-17 article/article.tex
[ article ] Corrected typo.

@@
 health issues. Additionally, technology has led to targeted harassing becoming
-more popular over time, therefore, difficulting the probability of detecting
+more popular over time, therefore, complicating the probability of detecting
 these cases.
@@
   well.
-  \item The ROC curve is a tool that helps visualize the correct clasifications
+  \item The ROC curve is a tool that helps visualize the correct classifications
   of the learning machine by plotting the true positive rate on the vertical

### 2020-11-17 src/NN.jl
[ src ] Corrected embedded data.

@@ -53,7 +53,7 @@ end
 
 function write_brain(brain :: Brain, grads :: Matrix{Float64},
                      avg_err :: Matrix{Float64}, η :: Float64,
-                     name_file :: String)
+                     name_file :: String, file_data :: String)
     # Number of neurons
     ls = Vector{Int64}([])
     for ω in brain.ω[1:(end-1)]
@@ -61,7 +61,7 @@ function write_brain(brain :: Brain, grads :: Matrix{Float64},
     end
 
     # Output of NN
-    datax, _ = create_data("data/num-data.csv", sep = false)
+    datax, _ = create_data(file_data, sep = false)
     Z = zeros(size(datax, 1))
     for i in 1:size(datax, 1)
         Z[i] = brain.propagate(datax[i, :])[1, 1]
@@ -79,6 +79,7 @@ function run_combinations(ηs :: Vector{Float64}, ls :: Vector{Int64},
     sig = Sigmoid()
 
     # Run all combinations
+    selected_brains = []
     for η in ηs
         for l in ls
             possible_neurons = get_neuron_combinations(l, neurons)
@@ -123,12 +124,12 @@ end
 
 # ====== Main ====== #
 train_data, _, _ = create_data("data/num-data.csv")
-tr_datax = train_data[1]
-tr_datay = train_data[2]
+train_datax = train_data[1]
+train_datay = train_data[2]
 
 train_data_emb, _, _ = create_data("data/embedded-data.csv")
-tr_dataxe = train_data_emb[1]
-tr_dataye = train_data_emb[2]
+train_dataxe = train_data_emb[1]
+train_dataye = train_data_emb[2]
 
 # Parameters for running
 ηs = [0.2, 0.5, 0.9]
@@ -136,21 +137,22 @@ ls = [1, 2, 3]
 neurons = [1, 2, 3]
 
 # Selection
-selected_brains = []
 number_of_brains = 3
 selection_criterion = x -> x[3][end]
 
 # Run
-selected_brains = run_combinations(ηs, ls, neurons, tr_datax, tr_datay,
+selected_brains = run_combinations(ηs, ls, neurons, train_datax, train_datay,
                                    selection_criterion, number_of_brains)
-selected_brainse = run_combinations(ηs, ls, neurons, tr_dataxe, tr_dataye,
+selected_brainse = run_combinations(ηs, ls, neurons, train_dataxe, train_dataye,
                                     selection_criterion, number_of_brains)
 
 # Write files
 for selected_brain in selected_brains
[…]

### 2020-11-17 src/plotting/Brain.py
[ src ] Added plot for embedded data.

@@ -55,11 +55,13 @@ class Brain:
 
         return brains
 
-    def plotmemaybe(self):
+    def plotmemaybe(self, aux_prefix=""):
         prefix = ""
         for l in self.ls:
             prefix += str(l) + "-"
         prefix += str(self.eta) + "-"
+        if len(aux_prefix) != 0:
+            prefix += aux_prefix + "-"
 
         # Plot information
         self.plot_grads(prefix + "gradients.pdf")
@@ -107,3 +109,8 @@ class Brain:
 brains = Brain.read_brains("../../results/nn-results.csv")
 for brain in brains:
     brain.plotmemaybe()
+
+# Data creation embedded
+brains = Brain.read_brains("../../results/nn-results-emb.csv")
+for brain in brains:
+    brain.plotmemaybe("emb")

### 2020-11-17 src/Tree.jl
[ src ] Exported embedded data.

@@ -14,14 +14,23 @@ dt_results = "../results/dt-results.csv"
 
 # Data
 train_data, _, _ = create_data("data/num-data.csv")
-
 train_datax = train_data[1]
 train_datay = train_data[2]
+
+train_datae, _, _ = create_data("data/embedded-data.csv")
+train_dataxe = train_datae[1]
+train_dataye = train_datae[2]
 
 # Decision tree
 dt = DecisionTreeClassifier(criterion = "entropy")
 fit!(dt, train_datax, reshape(train_datay, :))
 
+dte = DecisionTreeClassifier(criterion = "entropy")
+fit!(dte, train_dataxe, reshape(train_dataye, :))
+
 # Save tree
 save_model = "../results/tree.joblib"
 joblib.dump(dt, save_model)
+
+save_model = "../results/tree-emb.joblib"
+joblib.dump(dte, save_model)

### 2020-11-17 src/plotting/GetData.py
[ src ] Added higher dimension compliance.

@@ -14,16 +14,14 @@ def purge(column):
 # Create data set
 def create_data(name_file, index_file, sep=True):
     data_csv = open(name_file).readlines()[1:]
-    data = np.zeros((len(data_csv), 7))
-    k = 0
+    data = []
     for row in data_csv:
-        data[k, :] = list(map(float, row.split(",")))
-        k += 1
+        data.append(row.split(","))
 
-    data = normalize(data)
+    data = normalize(np.array(data, dtype=float))
 
     if not sep:
-        return data[:, :6], data[:, 6:]
+        return data[:, :-1], data[:, -1:]
 
     # Separate data
     indexes_csv = open(index_file).readlines()[1:]
@@ -40,14 +38,14 @@ def create_data(name_file, index_file, sep=True):
     indexes_val = purge(indexes[:, 2])
 
     # Data creation
-    train_datax = data[indexes_tr, :6]
-    train_datay = data[indexes_tr, 6:]
+    train_datax = data[indexes_tr, :-1]
+    train_datay = data[indexes_tr, -1:]
 
-    test_datax = data[indexes_te, :6]
-    test_datay = data[indexes_te, 6:]
+    test_datax = data[indexes_te, :-1]
+    test_datay = data[indexes_te, -1:]
 
-    val_datax = data[indexes_val, :6]
-    val_datay = data[indexes_val, 6:]
+    val_datax = data[indexes_val, :-1]
+    val_datay = data[indexes_val, -1:]
 
     return (train_datax, train_datay), (test_datax, test_datay),\
            (val_datax, val_datay)

### 2020-11-17 src/plotting/Tree.py
[ src ] Created embedded data graphs.

@@ -21,12 +21,14 @@ class Tree:
         self.feature_names = feature_names
         self.clas_names = clas_names
 
-    def plotmemaybe(self, n=10):
+    def plotmemaybe(self, data_file, aux_prefix="", n=10):
         prefix = "tree-"
+        if len(aux_prefix) != 0:
+            prefix += aux_prefix + "-"
 
         # Plot information
         self.plot_tree(prefix + "graph")
-        self.plot_contour(prefix + "contour-", n)
+        self.plot_contour(prefix + "contour-", data_file, n)
 
 
     def plot_tree(self, name_file):
@@ -39,11 +41,34 @@ class Tree:
         graph = graphviz.Source(dot_data)
         graph.render(dir_of_file(name_file))
 
-    def plot_contour(self, name_file, n):
-        datax, datay = create_data("../data/num-data.csv", "../data/indexes.csv",
+    def plot_contour(self, name_file, data_file, n):
+        datax, datay = create_data(data_file, "../data/indexes.csv",
                                    sep=False)
         datay = np.resize(datay, datay.shape[0])
 
+        if datax.shape[1] > 2:
+            self.contour_hd(datax, datay, name_file, n)
+        else:
+            self.contour_2d(datax, datay, name_file, n)
+
+    def contour_2d(self, datax, datay, name_file, n):
+        x_range = np.linspace(datax[:, 0].min(), datax[:, 0].max(), n)
+        y_range = np.linspace(datax[:, 1].min(), datax[:, 1].max(), n)
+
+        # Mesh
+        xx, yy = np.meshgrid(x_range, y_range)
+
+        # Evaluate tree
+        x_r = np.reshape(xx.flatten(), (xx.size, 1))
+        y_r = np.reshape(yy.flatten(), (yy.size, 1))
+        mesh_mat = np.hstack((x_r, y_r))
+        output = tree.DecisionTreeClassifier.predict(self.tree, mesh_mat)
+        zz = np.reshape(output, xx.shape)
+
+        # Contour
+        self.plot_contour_formatted(xx, yy, zz, datax, datay, 0, 1, name_file)
+
+    def contour_hd(self, datax, datay, name_file, n):
         # Meshgrid
         ranges = []
         for i in range(datax.shape[1]):
@@ -60,20 +85,25 @@ class Tree:
         for i in range(3):
             for j in range(3, len(self.feature_names)):
                 xx, yy, zz = Tree.project_mesh(mesh_h, output, i, j, datax, n)
[…]

### 2020-11-17 src/SVM.jl
[ src ] Exported embedded data.

@@ -17,9 +17,7 @@ train_datay = train_data[2]
 kernels = ["linear", "rbf", "poly"]
 
 # Files
-data_name = "data/num-dats.csv"
-meshgrid_file = "../results/meshgrid.csv"
-svm_results = "../results/svm-results.csv"
+data_name = "data/num-data.csv"
 
 # Output
 prefix = "../results/svm-"
@@ -27,5 +25,15 @@ for kernel in kernels
     svm = SVC(kernel = kernel)
     fit!(svm, train_datax, reshape(train_datay, :))
     joblib.dump(svm, string(prefix, kernel, ".joblib"))
+end
 
+# Files embedded data
+data_name = "data/embedded-data.csv"
+
+# Output
+prefix = "../results/svm-emb-"
+for kernel in kernels
+    svm = SVC(kernel = kernel)
+    fit!(svm, train_datax, reshape(train_datay, :))
+    joblib.dump(svm, string(prefix, kernel, ".joblib"))
 end

### 2020-11-17 src/plotting/GetData.py
[ src ] Added plot embedded data.

@@ -1,5 +1,6 @@
 #!/usr/bin/env python3
 
+import matplotlib.pyplot as plt
 import numpy as np
 
 # Normalize data
@@ -59,3 +60,8 @@ def create_meshgrid(name_file):
         mesh[k, :] = list(map(float, row.split(",")))
         k += 1
     return mesh
+
+def plot_embedded_data(embedded_data_file):
+    datax, _ = create_data(embedded_data_file, "../data/indexes.csv", sep=False)
+    plt.scatter(datax[:, 0], datax[:, 1], color='k')
+    plt.savefig("../../article/figs/embedded-data.pdf")

### 2020-11-17 article/article.tex
[ article ] working
[ article ] started appendix plots

@@
 \section{Results}\label{sec:res}
+For giving an idea of the dataset treated in this work (visualization), the data
+was embedded into a 2-dimensional space using the T-student Stochastic
+Neighborhood Embedding (TSNE) \href{https://github.com/lejon/TSne.jl}{in Julia}
+\parencite{maaten2008}. In Fig. \ref{fig:emb_dat}, the embedded dataset is
+presented.
+\begin{figure}
+  \includegraphics[width=\columnwidth]{figs/embedded-data.pdf}
+  \caption{Embedded dataset.}
+  \label{fig:emb_dat}
+\end{figure}
+
 \subsection{Support Vector Machines}
@@
     \end{subfigure}
-    \caption{Learning curves for $\mathcal{L}=[1,2,3]$ network (worst).}
+    \caption{Learning curves for $\mathcal{L}=[1,2,3]$ network $\eta=0.9$
+    (worst).}
     \label{fig:NN-worst}
@@
     \end{subfigure}
-    \caption{Learning curves for $\mathcal{L}=[2]$ network (2nd best).}
+    \caption{Learning curves for $\mathcal{L}=[2]$ network with $\eta=0.9$
+     (2nd best).}
     \label{fig:NN-2best}
@@
     \end{subfigure}
-    \caption{Learning curves for $\mathcal{L}=[3]$ network (best).}
+    \caption{Learning curves for $\mathcal{L}=[3]$ network with $\eta=0.9$
+    (best).}
     \label{fig:NN-best}
@@
 
+\appendices
+
+\section{Results for Embedded Data}
+This section presents the same results above presented but for the data
+embedded with the TSNE algorithm prior to training.
+\subsection{Support Vector Machines}
+
+\subsection{Decision Tree}
+\begin{figure}
+    \includegraphics[width=\columnwidth]{figs/tree-emb-graph.pdf}
+    \caption{Decision tree.}
+    \label{fig:dte}
+\end{figure}
+
+\begin{figure}
+    \includegraphics[width=\columnwidth]{figs/tree-contour-0-1.pdf}
+    \caption{Decision Tree contour with real labels (embedded data).}
+    \label{fig:dte_cont}
+\end{figure}
+
+\subsection{Neural Networks}
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-gradients.pdf}
+        \caption{Gradients for each layer.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-error.pdf}
+        \caption{Average error energy per epoch.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-roc.pdf}
+        \caption{ROC curve.}
+    \end{subfigure}
+    \caption{Learning curves for $\mathcal{L}=[2,3,3]$ network with $\eta=0.9$
+    (worst).}
+    \label{fig:NN-emb-worst}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/3-0.5-emb-gradients.pdf}
+        \caption{Gradients for each layer.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/3-0.5-emb-error.pdf}
+        \caption{Average error energy per epoch.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/3-0.5-emb-roc.pdf}
+        \caption{ROC curve.}
+    \end{subfigure}
+    \caption{Learning curves for $\mathcal{L}=[3]$ with $\eta=0.5$ network
+    (2nd best).}
+    \label{fig:NN-emb-2best}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/2-0.2-emb-gradients.pdf}
+        \caption{Gradients for each layer.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/2-0.2-emb-error.pdf}
+        \caption{Average error energy per epoch.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/2-0.2-emb-roc.pdf}
+        \caption{ROC curve.}
+    \end{subfigure}
+    \caption{Learning curves for $\mathcal{L}=[2]$ with $\eta=0.2$ network
+    (best).}
+    \label{fig:NN-emb-best}
+\end{figure*}
+
 \end{document}

### 2020-11-17 src/SVM.jl
[ src ] Exported embedded svms.

@@ -8,16 +8,13 @@ include("modules/Tools.jl")
 
 # ==== Main ==== #
 # Data
-train_data, _, _ = create_data("data/num-data.csv")
-
+data_name = "data/num-data.csv"
+train_data, _, _ = create_data(data_name)
 train_datax = train_data[1]
 train_datay = train_data[2]
 
 # SVM
 kernels = ["linear", "rbf", "poly"]
-
-# Files
-data_name = "data/num-data.csv"
 
 # Output
 prefix = "../results/svm-"
@@ -29,11 +26,14 @@ end
 
 # Files embedded data
 data_name = "data/embedded-data.csv"
+train_datae, _, _ = create_data(data_name)
+train_dataxe = train_datae[1]
+train_dataye = train_datae[2]
 
 # Output
 prefix = "../results/svm-emb-"
 for kernel in kernels
     svm = SVC(kernel = kernel)
-    fit!(svm, train_datax, reshape(train_datay, :))
+    fit!(svm, train_dataxe, reshape(train_dataye, :))
     joblib.dump(svm, string(prefix, kernel, ".joblib"))
 end

### 2020-11-17 src/plotting/SVM.py
[ src ] Added plotter of SVMs.

@@ -1,0 +1,133 @@
+#!/usr/bin/env python3
+
+# ==== Global behavior ==== #
+import matplotlib.pyplot as plt
+import numpy as np
+
+from GetData import create_data, create_meshgrid
+from joblib import load
+from matplotlib import rc
+from sklearn.svm import SVC
+
+rc('text', usetex=True)
+dir_of_file = lambda x: "../../article/figs/" + x
+save = lambda x: plt.savefig(dir_of_file(x), bbox_inches='tight')
+
+# ==== SVM ==== #
+class SVM:
+    def __init__(self, svm_joblib, feature_names):
+        self.svm = load(svm_joblib)
+        self.feature_names = feature_names
+
+    def plotmemaybe(self, data_file, aux_prefix="", n=10):
+        prefix = "svm-"
+        if len(aux_prefix) != 0:
+            prefix += aux_prefix + "-"
+
+        # Plot information
+        self.plot_contour(prefix + "contour-", data_file, n)
+
+
+    def plot_contour(self, name_file, data_file, n):
+        datax, datay = create_data(data_file, "../data/indexes.csv",
+                                   sep=False)
+        datay = np.resize(datay, datay.shape[0])
+
+        if datax.shape[1] > 2:
+            self.contour_hd(datax, datay, name_file, n)
+        else:
+            self.contour_2d(datax, datay, name_file, n)
+
+    def contour_2d(self, datax, datay, name_file, n):
+        x_range = np.linspace(datax[:, 0].min(), datax[:, 0].max(), n)
+        y_range = np.linspace(datax[:, 1].min(), datax[:, 1].max(), n)
+
+        # Mesh
+        xx, yy = np.meshgrid(x_range, y_range)
+
+        # Evaluate tree
+        x_r = np.reshape(xx.flatten(), (xx.size, 1))
+        y_r = np.reshape(yy.flatten(), (yy.size, 1))
+        mesh_mat = np.hstack((x_r, y_r))
+        output = SVC.decision_function(self.svm, mesh_mat)
+        zz = np.reshape(output, xx.shape)
+
+        # Contour
+        self.plot_contour_formatted(xx, yy, zz, datax, datay, 0, 1, name_file)
+
+    def contour_hd(self, datax, datay, name_file, n):
+        # Meshgrid
+        ranges = []
+        for i in range(datax.shape[1]):
+            ranges.append(np.linspace(datax[:, i].min(), datax[:, i].max(), n))
+        mesh = np.meshgrid(*ranges)
+
+        # Evaluate tree
[…]

### 2020-11-17 src/plotting/SVM.py
[ src ] Corrected replacement.

@@ -122,7 +122,7 @@ for kernel in kernels:
     svm = SVM(svm_name(kernel), ["Level of Attention", "Academic Perfomance",
                                  "Emotional Socialization", "Depression",
                                  "Anxiety", "Hyperactivity"])
-    svm.plotmemaybe("../data/num-data.csv", n=4)
+    svm.plotmemaybe("../data/num-data.csv", n=4, aux_prefix=kernel)
 
 # Embedded dataset
 svm_name = lambda x: "../../results/svm-emb-" + x + ".joblib"
@@ -130,4 +130,5 @@ for kernel in kernels:
     svm = SVM(svm_name(kernel), ["Level of Attention", "Academic Perfomance",
                                 "Emotional Socialization", "Depression",
                                 "Anxiety", "Hyperactivity"])
-    svm.plotmemaybe("../data/embedded-data.csv", n=4, aux_prefix="emb")
+    svm.plotmemaybe("../data/embedded-data.csv", n=4,
+                    aux_prefix="emb-" + kernel)

### 2020-11-17 article/article.tex
[ article ] added plots

@@
 \subsection{Support Vector Machines}
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-linear-contour-0-3.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-linear-contour-0-4.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-linear-contour-0-5.pdf}
+        \caption{}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-linear-contour-1-3.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-linear-contour-1-4.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-linear-contour-1-5.pdf}
+        \caption{}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-linear-contour-2-3.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-linear-contour-2-4.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-linear-contour-2-5.pdf}
+        \caption{}
+    \end{subfigure}
+    \caption{Linear kernel SVM contour with real labels.}
+    \label{fig:SVM-linear}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-poly-contour-0-3.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-poly-contour-0-4.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-poly-contour-0-5.pdf}
+        \caption{}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-poly-contour-1-3.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-poly-contour-1-4.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-poly-contour-1-5.pdf}
+        \caption{}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-poly-contour-2-3.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-poly-contour-2-4.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-poly-contour-2-5.pdf}
+        \caption{}
+    \end{subfigure}
+    \caption{Polynomial kernel SVM contour with real labels.}
+    \label{fig:SVM-poly}
+\end{figure*}
+
+\begin{figure*}
+    \centering
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-0-3.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-0-4.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-0-5.pdf}
+        \caption{}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-1-3.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-1-4.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-1-5.pdf}
+        \caption{}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-2-3.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-2-4.pdf}
+        \caption{}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.32\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-2-5.pdf}
+        \caption{}
+    \end{subfigure}
+    \caption{RBF kernel SVM contour with real labels.}
+    \label{fig:SVM-rbf}
+\end{figure*}
 
@@
 \subsection{Support Vector Machines}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{figs/svm-emb-linear-contour-0-1.pdf}
+  \caption{Linear kernel SVM contour with real labels.}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{figs/svm-emb-poly-contour-0-1.pdf}
+  \caption{Polynomial kernel SVM contour with real labels.}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{figs/svm-emb-rbf-contour-0-1.pdf}
+  \caption{RBF kernel SVM contour with real labels.}
+\end{figure}
 
@@
     \caption{Decision tree.}
-    \label{fig:dte}
 \end{figure}
@@
     \includegraphics[width=\columnwidth]{figs/tree-contour-0-1.pdf}
-    \caption{Decision Tree contour with real labels (embedded data).}
-    \label{fig:dte_cont}
+    \caption{Decision Tree contour with real labels.}
 \end{figure}
@@
     (worst).}
-    \label{fig:NN-emb-worst}
 \end{figure*}
@@
     (2nd best).}
-    \label{fig:NN-emb-2best}
 \end{figure*}
@@
     (best).}
-    \label{fig:NN-emb-best}
 \end{figure*}

### 2020-11-17 src/SVM.jl
[ src ] Exported error aproximation results and ordered file.

@@ -1,39 +1,69 @@
 # ==== Global behavior ==== #
+using CSV
 using PyCall
 using ScikitLearn
+using Tables
 include("modules/Tools.jl")
 
 @pyimport joblib
 @sk_import svm: SVC
 
+# ==== Functions ==== #
+function export_error(ms :: Vector{Int64}, δ :: Float64, VC :: Float64,
+                      name_file :: String)
+    aux_func(m) = calculate_min_error(m, δ, VC)
+    εs = map(aux_func, ms)
+
+    # Output
+    out = [εs ms]
+    CSV.write(name_file, Tables.table(out))
+end
+
+function run_data(prefix :: String, train_datax :: Matrix{Float64},
+                  train_datay :: Vector{Float64}, ms :: Vector{Int64},
+                  δ :: Float64)
+    # Possible kernles
+    kernels = ["linear", "rbf", "poly"]
+    n = size(train_datax, 2)
+    VCs = [n + 1, nothing, (n + 3) * (n + 2) * (n + 1) / 6]
+
+    for i in 1:length(kernels)
+        svm = SVC(kernel = kernels[i])
+        fit!(svm, train_datax, reshape(train_datay, :))
+        joblib.dump(svm, string(prefix, kernels[i], ".joblib"))
+
+        if !isnothing(VCs[i])
+            export_error(ms, δ, VCs[i], string("../results/", prefix,
+                                               kernels[i], "-eps.csv"))
+        end
+    end
+end
+
 # ==== Main ==== #
-# Data
+### High dimensional Data
 data_name = "data/num-data.csv"
 train_data, _, _ = create_data(data_name)
 train_datax = train_data[1]
-train_datay = train_data[2]
-
-# SVM
-kernels = ["linear", "rbf", "poly"]
+train_datay = reshape(train_data[2], :)
 
 # Output
 prefix = "../results/svm-"
-for kernel in kernels
-    svm = SVC(kernel = kernel)
-    fit!(svm, train_datax, reshape(train_datay, :))
-    joblib.dump(svm, string(prefix, kernel, ".joblib"))
-end
 
-# Files embedded data
+# Error aproximation data
+m = size(train_datax, 1)
+ms = trunc.(Int, floor(0.8*m):1:floor(8*m))
+δ = 0.3
+
+run_data(prefix, train_datax, train_datay, ms, δ)
+
+
+### Embedded data
 data_name = "data/embedded-data.csv"
[…]

### 2020-11-17 src/modules/Tools.jl
[ src ] Added module to calculate aproximate error.

@@ -1,4 +1,6 @@
 using CSV
+using Ipopt
+using JuMP
 
 # Normalize data
 function normalize(data)
@@ -45,4 +47,23 @@ function create_data(name_file :: String; sep = true, norm = true)
 
     return (train_datax, train_datay), (test_datax, test_datay),
            (val_datax, val_datay)
+end
+
+# Calculate ε-dimension
+function calculate_min_error(m :: Int64, δ :: Float64, VC :: Float64)
+    model = Model(with_optimizer(Ipopt.Optimizer, print_level = 0))
+
+    # Variables
+    @variable(model, 0 <= ε)
+
+    # Constraints
+    @constraint(model, 4 * log(2 / δ) / m <= ε)
+    @NLconstraint(model, 8 * VC * log(13 / ε) / ε <= m)
+
+    # Objective function
+    @objective(model, Min, ε^2)
+
+    # Optimization
+    JuMP.optimize!(model)
+    return JuMP.value(ε)
 end

### 2020-11-17 src/plotting/SVM.py
[ src ] Added plots for error.

@@ -15,9 +15,20 @@ save = lambda x: plt.savefig(dir_of_file(x), bbox_inches='tight')
 
 # ==== SVM ==== #
 class SVM:
-    def __init__(self, svm_joblib, feature_names):
+    def __init__(self, svm_joblib, feature_names, error_mat_name=""):
         self.svm = load(svm_joblib)
         self.feature_names = feature_names
+        self.error_mat = None
+        if error_mat_name:
+            self.read_error(error_mat_name)
+
+    def read_error(self, error_mat_name):
+        file0 = open(error_mat_name).readlines()[1:]
+
+        # Get matrix
+        str_mat = list(map(lambda x: x.split(","), file0))
+        self.error_mat = np.array(str_mat, dtype=float)
+        self.error_mat[:, [0, 1]] = self.error_mat[:, [1, 0]]
 
     def plotmemaybe(self, data_file, aux_prefix="", n=10):
         prefix = "svm-"
@@ -26,6 +37,22 @@ class SVM:
 
         # Plot information
         self.plot_contour(prefix + "contour-", data_file, n)
+        if self.error_mat is not None:
+            self.plot_error(prefix + "error.pdf", data_file)
+
+    def plot_error(self, name_file, data_file):
+        # Data
+        (train_datax, _), _, _ = create_data(data_file, "../data/indexes.csv")
+        m = train_datax.shape[0]
+
+        # Plotting
+        plt.plot(self.error_mat[:, 0], self.error_mat[:, 1], 'k')
+        plt.plot([m, m], [self.error_mat[:, 1].min()*0.5, self.error_mat[:, 1].max()*2], 'b--',
+                 lw=0.5)
+        plt.xlabel("$m$")
+        plt.ylabel("$\epsilon$")
+        save(name_file)
+        plt.clf()
 
 
     def plot_contour(self, name_file, data_file, n):
@@ -115,20 +142,27 @@ class SVM:
 
 # ==== SVM plotters ==== #
 kernels = ["linear", "poly", "rbf"]
+errors = {"linear": "../../results/svm-linear-eps.csv",
+          "poly": "../../results/svm-poly-eps.csv",
+          "rbf": ""}
 
 # High dimensional dataset
 svm_name = lambda x: "../../results/svm-" + x + ".joblib"
+features = ["Level of Attention", "Academic Perfomance",
+            "Emotional Socialization", "Depression", "Anxiety",
+            "Hyperactivity"]
+
 for kernel in kernels:
[…]

### 2020-11-18 article/article.tex
[ article ] working on methodology

@@
 
-Finally, another overview of applications of Artificial Intelligence (AI) for Mental
-Illnesses is the research published by \textcite{graham2019}, where the authors
-reviewed 28 research papers which include modern methodologies (and
+Finally, another overview of applications of Artificial Intelligence (AI) for
+Mental Illnesses is the research published by \textcite{graham2019}, where the
+authors reviewed 28 research papers which include modern methodologies (and
 technologies) for predicting or classifying psychological illnesses such as
 depression, schizophrenia or suicidal behavior. The study discusses how the
-application of AI techniques supports the clinical practice while considering its
-limitations, it also presents some ethical implications and states which areas need
-further development.
+application of AI techniques supports the clinical practice while considering
+its limitations, it also presents some ethical implications and states which
+areas need further development.
 
@@
 \subsection{Survey}
-The used survey for extracting data was initially designed for developing
+The used survey for extracting data was initially designed in the developing
 a Fuzzy Inference System, but the data was labeled according to
@@
 
+Remark: the dataset includes both inputs (first three variables) and outputs
+(last three variables) of the Fuzzy Inference System. This will be later
+useful to organize relationships in the variables for more intuitive plots.
+
 \subsection{Support Vector Machines}
@@
 
+Given that the sample size is fixed, the analysis for the ``Probably
+Approximately Correct'' (PAC) learning was not straight-forward, as the
+classifier's maximum permited error $\epsilon$ was estimated from the classic
+formulae, rather than calculating the adequate sample size for a given $\delta$.
+
+The PAC learning here applied is based on the ideas presented in
+\parencite{kubat2017}. Let $N$ be number of samples in the training set,
+$\epsilon$ is the classifier maximum permited error rate, $\delta$ is the
+probability that a classifier with error rate greater than $\epsilon$ is
+\text{error-free} on the training set, $m$ be the dimension of each training
+patttern, and let $VC$ be the Vapnik-Chervonenkis dimension of the given
+classifier. Hence, for learning in continuous domains, the lower bound for
+$N$ is
+
+\begin{equation}
+N\geq \max\left\{ \dfrac{4}{\epsilon}\ln\left(\dfrac{2}{\delta}\right),
+\dfrac{8\mathrm{VC}}{\epsilon}\ln\left(\dfrac{13}{\epsilon}\right) \right\}.
+\end{equation}
+
+It is clear that solving for $\epsilon$ is non-trivial for given values of
+$\delta$, $N$ and $\mathrm{VC}$; thus, an optimization approach was used to
+estimate $\epsilon$ for the input values, solving the nonlinear optimization
+problem
+
+\begin{equation}
+\begin{split}
+\min_{\epsilon\in\mathbb{R}_+}\ &J=\,\epsilon^2\\
+\mathrm{s.t.}\ &\dfrac{4}{\epsilon}\ln\left(\dfrac{2}{\delta} \right)\leq N\\
+\quad&\dfrac{8\mathrm{VC}}{\epsilon}\ln\left(\dfrac{13}{\epsilon}\right)\leq N.
+\end{split}
+\end{equation}
+
+The problem was initially constrained to $\epsilon\in[0,1]$, but it had not
+feasible solution for the size of the training set, yielding values of
+$\epsilon$ greater than 1. Instead, the constrained was removed and a
+sensitivity analysis was made for the training set size, varying the latter to
+find a suitable value for $\epsilon$. The size of training set was varied in
+$(0.8N, 10N)$ for each kernel SVM and the estimated $\epsilon$ are presented
+in Fig. \ref{fig:error-SVM}, with a fixed $\delta$. Note that $\mathrm{VC}=7$
+for the linear SVM, since
+$m=6$, and $\mathrm{VC}=84$ for the polynomial SVM, since cubic polynomials were
+selected; furthermore, the VC dimension for the RBF SVM is infinite and this
+case was not included (see \parencite{burges1998}).
+
+Note that $\epsilon$ in the linear SVM enters the feasible value for training
+sets above 150 samples and stabilizing around $\epsilon=0.3$ for large training
+set samples value. In contrast, $\epsilon$ for the polynomial SVM never reaches
+a suitable value below 1, indicating that this classifier requires more than 600
+samples in the training set to satisfy the PAC learning.
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-linear-error.pdf}
+        \caption{Linear SVM.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-poly-error.pdf}
+        \caption{Polynomial SVM}
+    \end{subfigure}
+    \caption{Estimated $\epsilon$ for different training set sizes.}
+    \label{fig:error-SVM}
+\end{figure}
+
 \subsection{Decision Trees}
 We refer to \textcite{bramer2007} for the general ideas behind the decision tree
-classifier.
+classifier. The DTs were used directly from Scikit-Learn
+\parencite{scikit-learn, sklearn_api} using
+\href{https://bit.ly/3lDHADX}{Julia's API}. The DT were trained using all
+default parameters in the suite, but using the ``entropy'' (information gain)
+criterion for measuring the quality of splits.
+
+The same idea from the SVM classifiers for plotting the countour of the decision
+boundaries of the fitted model was used, plotting the training dataset with the
+real labels and the contour for the decision function.
+
+Additionally, it is well-known that the bound for the training dataset size is
+given by
+\begin{equation}
+  N\geq \dfrac{\ln(2)}{2\epsilon^2}\left[(2^k-1)(1+\log_2 m) + 1 + \ln\left(
+  \dfrac{1}{\delta}\right)\right],
+\end{equation}
+but again, the size of the dataset is fixed,
 
@@
   where $N$ is the training sample size. Thus, it is clear that
-  $\xi_{av}\rightarrow0$ as the training algorithm solves the learning problem
-  well.
+  $\xi_{av}\rightarrow0$ is a good initial approach for evaluating the
+  learning performance.
   \item The ROC curve is a tool that helps visualize the correct classifications

### 2020-11-18 src/plotting/GetData.py
[ src ] Added specs calculation and indexes method.

@@ -3,6 +3,11 @@
 import matplotlib.pyplot as plt
 import numpy as np
 
+from matplotlib import rc
+
+rc('text', usetex=True)
+save = lambda x: plt.savefig("../../article/figs/" + x, bbox_inches='tight')
+
 # Normalize data
 def normalize(data):
     return data / np.max(np.abs(data), axis=0)
@@ -12,18 +17,67 @@ def purge(column):
     index = np.where(column == -2)[0][0]
     return column[:index]
 
-# Create data set
-def create_data(name_file, index_file, sep=True):
-    data_csv = open(name_file).readlines()[1:]
-    data = []
-    for row in data_csv:
-        data.append(row.split(","))
+# Calculate sensitivity and specificity
+def get_sensitivity_specifity(out_clas, real_clas, threshold=0.2):
+    # Sensitivity
+    tp = 0
+    fn = 0
 
-    data = normalize(np.array(data, dtype=float))
+    # Specificity
+    tn = 0
+    fp = 0
 
-    if not sep:
-        return data[:, :-1], data[:, -1:]
+    # Calculate each one
+    for i in range(out_clas.size):
+        if 0.5 - threshold <= out_clas[i] <= 0.5 + threshold:
+            continue
 
+        if out_clas[i] < 0.5 - threshold:
+            cond = int(real_clas[i] == 0)
+            tn += cond
+            fn += 1 - cond
+        elif out_clas[i] > 0.5 + threshold:
+            cond = int(real_clas[i] == 1)
+            tp += cond
+            fp += 1 - cond
+    try:
+        sens = tp / (tp + fn)
+    except ZeroDivisionError:
+        sens = "Error"
+
+    try:
+        spec = tn / (tn + fp)
+    except ZeroDivisionError:
+        spec = "Error"
+
+    return sens, spec
+
+# Create file for classifiers
+def create_sens_spec(outs, name_file, sep_info, data_file, index_file):
+    file0 = open(name_file, "w")
+
+    indexes_tr, indexes_te, indexes_val = get_index(index_file)
+    _, datay = create_data(data_file, index_file, sep=False)
+
+    for i in range(len(outs)):
+        out = outs[i]
+        for key in sep_info[i]:
+            file0.write(str(key) + "," + str(sep_info[i][key]) + "\n")
+
+        sens_tr, spec_tr = get_sensitivity_specifity(out[indexes_tr],
+                                                     datay[indexes_tr, 0])
[…]

### 2020-11-18 src/plotting/Brain.py
[ src ] Exported files.

@@ -1,7 +1,7 @@
 #!/usr/bin/env python3
 
 # ==== Global behavior ==== #
-from GetData import create_data
+from GetData import create_data, create_sens_spec
 import matplotlib.pyplot as plt
 import numpy as np
 
@@ -110,7 +110,19 @@ brains = Brain.read_brains("../../results/nn-results.csv")
 for brain in brains:
     brain.plotmemaybe()
 
+# Sensitivity and specificity
+outs = list(map(lambda x: x.out, brains))
+sep_info = list(map(lambda x: {"eta": x.eta, "ls": x.ls}, brains))
+create_sens_spec(outs, "../../results/nn-specs.csv", sep_info,
+                 "../data/num-data.csv", "../data/indexes.csv")
+
 # Data creation embedded
 brains = Brain.read_brains("../../results/nn-results-emb.csv")
 for brain in brains:
     brain.plotmemaybe("emb")
+
+# Sensitivity and specificity
+outs = list(map(lambda x: x.out, brains))
+sep_info = list(map(lambda x: {"eta": x.eta, "ls": x.ls}, brains))
+create_sens_spec(outs, "../../results/nn-emb-specs.csv", sep_info,
+                 "../data/num-data.csv", "../data/indexes.csv")

### 2020-11-18 src/plotting/SVM.py
[ src ] Exported specs.

@@ -4,7 +4,7 @@
 import matplotlib.pyplot as plt
 import numpy as np
 
-from GetData import create_data, create_meshgrid
+from GetData import create_data, create_meshgrid, create_sens_spec
 from joblib import load
 from matplotlib import rc
 from sklearn.svm import SVC
@@ -47,8 +47,9 @@ class SVM:
 
         # Plotting
         plt.plot(self.error_mat[:, 0], self.error_mat[:, 1], 'k')
-        plt.plot([m, m], [self.error_mat[:, 1].min()*0.5, self.error_mat[:, 1].max()*2], 'b--',
-                 lw=0.5)
+        plt.plot([m, m], [self.error_mat[:, 1].min()*0.5,
+                          self.error_mat[:, 1].max()*2],
+                 'b--', lw=0.5)
         plt.xlabel("$m$")
         plt.ylabel("$\epsilon$")
         save(name_file)
@@ -145,24 +146,44 @@ kernels = ["linear", "poly", "rbf"]
 errors = {"linear": "../../results/svm-linear-eps.csv",
           "poly": "../../results/svm-poly-eps.csv",
           "rbf": ""}
+datax, _ = create_data("../data/num-data.csv", "../data/indexes.csv",
+                       sep=False)
 
-# High dimensional dataset
+### High dimensional dataset
 svm_name = lambda x: "../../results/svm-" + x + ".joblib"
 features = ["Level of Attention", "Academic Perfomance",
             "Emotional Socialization", "Depression", "Anxiety",
             "Hyperactivity"]
 
+svms = []
 for kernel in kernels:
     svm = SVM(svm_name(kernel), features, error_mat_name=errors[kernel])
     svm.plotmemaybe("../data/num-data.csv", n=4, aux_prefix=kernel)
+    svms.append(svm)
 
-# Embedded dataset
+# Specs
+outs = list(map(lambda x: SVC.decision_function(x.svm, datax), svms))
+sep_info = list(map(lambda x: {"Kernel": x}, kernels))
+create_sens_spec(outs, "../../results/svm-specs.csv", sep_info,
+                 "../data/num-data.csv", "../data/indexes.csv")
+
+### Embedded dataset
 svm_name = lambda x: "../../results/svm-emb-" + x + ".joblib"
 errors = {"linear": "../../results/svm-emb-linear-eps.csv",
           "poly": "../../results/svm-emb-poly-eps.csv",
           "rbf": ""}
 
[…]

### 2020-11-18 src/plotting/Tree.py
[ src ] Exported specs.

@@ -6,7 +6,7 @@ import matplotlib.pyplot as plt
 import numpy as np
 import sklearn.tree as tree
 
-from GetData import create_data, create_meshgrid
+from GetData import create_data, create_meshgrid, create_sens_spec
 from joblib import load
 from matplotlib import rc
 
@@ -133,6 +133,22 @@ dt = Tree("../../results/tree.joblib", ["Level of Attention", "Academic Perfoman
                                         "Anxiety", "Hyperactivity"], ["0", "1"])
 dt.plotmemaybe("../data/num-data.csv", n=4)
 
+# Print specs
+datax, _ = create_data("../data/num-data.csv", "../data/indexes.csv",
+                       sep=False)
+outs = [tree.DecisionTreeClassifier.predict_proba(dt.tree, datax)[:, 1]]
+sep_info = [{}]
+create_sens_spec(outs, "../../results/tree-specs.csv", sep_info,
+                 "../data/num-data.csv", "../data/indexes.csv")
+
 # Embedded dataset
 dte = Tree("../../results/tree-emb.joblib", ["X0", "X1"], ["0", "1"])
 dte.plotmemaybe("../data/embedded-data.csv", n=4, aux_prefix="emb")
+
+# Print specs
+datax, _ = create_data("../data/embedded-data.csv", "../data/indexes.csv",
+                       sep=False)
+outs = [tree.DecisionTreeClassifier.predict_proba(dte.tree, datax)[:, 1]]
+sep_info = [{}]
+create_sens_spec(outs, "../../results/tree-emb-specs.csv", sep_info,
+                 "../data/embedded-data.csv", "../data/indexes.csv")

### 2020-11-18 article/article.tex
[ article ] added performance tables.

@@
 \end{equation}
-but again, the size of the dataset is fixed,
+but again, the size of the dataset is fixed. Thus, $\epsilon$ was calculated by
+fixing the tree depth $k$ and setting $\delta=0.7$.............
 
@@
 
+\begin{table}
+\centering
+\caption{Performance scores for linear SVM.}
+\label{tab:linear_SVM}
+\begin{tabular}{ccc}
+\hline
+\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
+Training & 0 & 1 \\
+Testing & 0 & 1 \\
+Validation & 0 & 1 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Performance scores for polynomial SVM.}
+\label{tab:poly_SVM}
+\begin{tabular}{cll}
+\hline
+\textbf{Set} & \multicolumn{1}{c}{\textbf{Sensitivity}} & \multicolumn{1}{c}{\textbf{Specificity}} \\ \hline
+Training & 0.89 & 1 \\
+Testing & 0 & 1 \\
+Validation & 0.57 & 1 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Performance scores for RBF SVM.}
+\label{tab:rbf_SVM}
+\begin{tabular}{cll}
+\hline
+\textbf{Set} & \multicolumn{1}{c}{\textbf{Sensitivity}} & \multicolumn{1}{c}{\textbf{Specificity}} \\ \hline
+Training & 0.13 & 1 \\
+Testing & 0 & 1 \\
+Validation & 0.25 & 1 \\ \hline
+\end{tabular}
+\end{table}
+
 \subsection{Decision Trees}
@@
 \end{figure*}
+
+\begin{table}
+\centering
+\caption{Performance scores for DT.}
+\label{tab:DT}
+\begin{tabular}{ccc}
+\hline
+\textbf{Set} & \multicolumn{1}{c}{\textbf{Sensitivity}} & \multicolumn{1}{c}{\textbf{Specificity}} \\ \hline
+Training & 1 & 1 \\
+Testing & 0.5 & 1 \\
+Validation & 0.75 & 1 \\ \hline
+\end{tabular}
+\end{table}
 
@@
 
+\begin{table}
+\centering
+\caption{Performance scores for $\mathcal{L}=[3]$ and $\eta=0.9$.}
+\label{tab:L3}
+\begin{tabular}{ccc}
+\hline
+\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
+Training & 0.5 & 1 \\
+Testing & $\times$ & 1 \\
+Validation & 1 & 1 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Performance scores for $\mathcal{L}=[2]$ and $\eta=0.9$.}
+\label{tab:L2}
+\begin{tabular}{ccc}
+\hline
+\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
+Training & $\times$ & 1 \\
+Testing & $\times$ & 1 \\
+Validation & $\times$ & 1 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Performance scores for $\mathcal{L}=[1,2,3]$ and $\eta=0.9$.}
+\label{tab:L123}
+\begin{tabular}{ccc}
+\hline
+\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
+Training & 0 & 1 \\
+Testing & 0 & 1 \\
+Validation & 0 & 1 \\ \hline
+\end{tabular}
+\end{table}
+
 \section{Conclusions}\label{sec:conc}
@@
 
+\begin{table}
+\centering
+\caption{Performance scores for linear SVM.}
+\label{tab:linear_SVM_emb}
+\begin{tabular}{ccc}
+\hline
+\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
+Training & 0 & 1 \\
+Testing & 0 & 1 \\
+Validation & 0 & 1 \\ \hline
+\end{tabular}
+\end{table}
+
 \begin{figure}
@@
 
+\begin{table}
+\centering
+\caption{Performance scores for polynomial SVM.}
+\label{tab:poly_SVM_emb}
+\begin{tabular}{ccc}
+\hline
+\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
+Training & 0 & 1 \\
+Testing & 0 & 1 \\
+Validation & 0 & 1 \\ \hline
+\end{tabular}
+\end{table}
+
 \begin{figure}
@@
 \end{figure}
+
+\begin{table}
+\centering
+\caption{Performance scores for polynomial RBF.}
+\label{tab:rbf_SVM_emb}
+\begin{tabular}{ccc}
+\hline
+\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
+Training & 0 & 1 \\
+Testing & 0 & 1 \\
+Validation & 0 & 1 \\ \hline
+\end{tabular}
+\end{table}
 
@@
 \end{figure}
+
+\begin{table}
+\centering
+\caption{Performance scores for DT.}
+\label{tab:DT_emb}
+\begin{tabular}{cll}
+\hline
+\textbf{Set} & \multicolumn{1}{c}{\textbf{Sensitivity}} & \multicolumn{1}{c}{\textbf{Specificity}} \\ \hline
+Training & 1 & 1 \\
+Testing & 0 & 1 \\
+Validation & 0.63 & 0.94 \\ \hline
+\end{tabular}
+\end{table}
 
@@
 
+\begin{table}
+\centering
+\caption{Performance scores for $\mathcal{L}=[2]$ and $\eta=0.2$.}
+\label{tab:L2_emb}
+\begin{tabular}{ccc}
+\hline
+\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
+Training & $\times$ & 1 \\
+Testing & $\times$ & 1 \\
+Validation & $\times$ & 1 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Performance scores for $\mathcal{L}=[3]$ and $\eta=0.5$.}
+\label{tab:L3_emb}
+\begin{tabular}{ccc}
+\hline
+\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
+Training & $\times$ & 1 \\
+Testing & $\times$ & 1 \\
+Validation & $\times$ & 1 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+\centering
+\caption{Performance scores for $\mathcal{L}=[2,3,3]$ and $\eta=0.9$.}
+\label{tab:L233_emb}
+\begin{tabular}{ccc}
+\hline
+\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
+Training & 0 & 1 \\
+Testing & 0 & 1 \\
+Validation & 0 & 1 \\ \hline
+\end{tabular}
+\end{table}
+
 \end{document}

### 2020-11-18 article/inputs/svm.tex
[ article ] added input files

--- 2020-11-17 article/article.tex
@@
-\documentclass[conference]{IEEEtran}
-\usepackage[english]{babel}
-\input{commands.tex}
-
-%%%%%%%% MARGIN
-\geometry{verbose, letterpaper, tmargin=3cm,
-  bmargin=3cm,lmargin=2.5cm,rmargin=2.5cm}
-
-%%%%%%%% PARAGRAPH SETTINGS
-% https://bit.ly/36WrtN4
-\setlength\parindent{0pt}
-
-% https://bit.ly/371dvto
-\setlength{\parskip}{5pt}
-
-%%%%%%%% HYPERREF PACKAGE
-\usepackage{hyperref}
-\hypersetup{linkcolor=blue}
-\hypersetup{citecolor=blue}
-\hypersetup{urlcolor=blue}
-\hypersetup{colorlinks=true}
-
-%%%%%%%% BIB-LATEX STUFF
-\usepackage[style=ieee,
-            bibstyle=ieee,
-            citestyle=ieee,
-            hyperref=true,
-            backend=biber]{biblatex}
-\addbibresource{ref.bib} %Put relative path to ref
-
-%%%%%%%% DEFINITION AND THEOREM DEFINITIONS
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-
-\theoremstyle{remark}
-\newtheorem{remark}{Remark}
-
-\theoremstyle{remark}
-\newtheorem{question}{Question}
-
-\newtheorem{theorem}{Theorem}[section]
-
-%%%%%%%% CODE RENDERING !!! UNCOMMENT IF NEEDED !!!
-% Compile with flag -shell-escape
-%\usepackage{minted}
-
-%%%%%%%% START DOCUMENT
-\title{Supervised Learning for Psychological Attention to High School Students}
-
-\author{\IEEEauthorblockN{Juan S. Cárdenas-Rodríguez}
-  \IEEEauthorblockA{\textit{Department of Mathematical Sciences} \\
-    \textit{EAFIT University}\\
-    Medellín, Colombia \\
-    jscardenar@eafit.edu.co} \and \IEEEauthorblockN{David Plazas}
-  \IEEEauthorblockA{\textit{Department of Mathematical Sciences} \\
-    \textit{EAFIT University}\\
-    Medellín, Colombia \\
-    dplazas@eafit.edu.co} }
-
-\begin{document}
-\maketitle
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-  Hello.
-\end{abstract}
-
-\begin{IEEEkeywords}
-  Nice.
-\end{IEEEkeywords}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\textit{Note}: All the code and the latex file can be found in
-\href{https://github.com/juanscr/ai-works}{the GitHub repository}.
-
-\section{Introduction}
-
-Mental health is crucially important for every human being and has become one of
-the most important issues surrounding human health. According to the World
-Health Organization (WHO)\footnote{WHO's \href{https://bit.ly/34l2v94}{2001
-    report.}} report of 2001, mental disorders can affect 25\% of the
-population, therefore, suggesting the ongoing trend of people suffering from
-lack of mental health. Additionally, with the recent events caused by the
-COVID-19 pandemic, mental issues have risen as consequence of lockdowns all
-around the globe, as have been proved by recent studies
-\parencite{rossi2020,xiong2020}.
-
-Furthermore, mental health is more important to monitor in adolescents and kids
-as this group is in the process of developing their mental structure and
-character. In this manner, as they continue creating their view about the world
-they must be surrounded by a healthy environment that promotes healthy habits
-and relationships with their surroundings.
-
-As a result, schools and parents have an important responsibility to the
-students of creating this environment and wisely handling mental health issues.
-However, high schools do not always know how to handle or detect cases of mental
-health issues. Additionally, technology has led to targeted harassing becoming
-more popular over time, therefore, complicating the probability of detecting
-these cases.
-
-Some of the most common and important mental health issues are anxiety,
-depression, and hyperkinetic disorder. According to \textcite{schulte2016},
-around 10\% to 20\% of children suffer from hyperkinetic disorder. Additionally,
-school teachers just assume this disorder is a cause of undisciplined students
-and can take the hyperkinetic student to a depressive state. These three mental
-disorders can leave severe damage to a kid and can lead them to suicide.
-
-Hence, it is of the utmost importance to quickly and efficiently detect students
-that might be having a mental health issue to immediately start a process with
-him/her. Furthermore, this detection has to be done with measurable variables
-that can be easily obtained from questionnaires or school data.
-
-The present work is oriented to the application of supervised learning
-techniques (decision trees, support vector machines and neural networks) for
-classifying the data from the survey, aiming for the construction of a model to
-detect individuals with mental health issues. Recent developments and the
-increasing popularity of supervised techniques has contributed to their
-application in different areas, among them, mental health.
-
-The novel work by \textcite{thieme2020} makes and excellent literature review of
-Machine Learning (ML) in mental health, including the current state-of-the-art
-and formulates new strategies for integrating human-oriented research with
-multi-disciplinary. They also conclude that ML applied in mental health is
-``still in its infancy'' given the complexity and difficulties of constructing
-robust models for clinically reliable outputs.
-
-Additionally, the work presented by \textcite{shatte2019} is also a complete
-compendium of recent ML applications in mental health, including the usage
-of Support Vector Machines (SVMs), Decision Trees (DTs), Neural Networks (NN)
-and beyond. This paper includes a systematic review of over three hundred papers
-and it concludes that these techniques have brought benefits
-across the areas of diagnosis, treatment, research and clinical administration.
-
-Finally, another overview of applications of Artificial Intelligence (AI) for Mental
-Illnesses is the research published by \textcite{graham2019}, where the authors
-reviewed 28 research papers which include modern methodologies (and
-technologies) for predicting or classifying psychological illnesses such as
-depression, schizophrenia or suicidal behavior. The study discusses how the
-application of AI techniques supports the clinical practice while considering its
-limitations, it also presents some ethical implications and states which areas need
-further development.
-
-This document is organized as
-follows: Section \ref{sec:meth} shows the general methodology used in this work,
-moreover Section \ref{sec:res} shows the obtained results over the data and
-slight modifications, finally Section \ref{sec:conc} concludes this work and
-sets pillars for future works.
-
-\section{Methodology}\label{sec:meth}
-All the code developed for this work was implemented in Julia 1.5.3. and
-can be found in the authors'
-\href{https://github.com/juanscr/ai-works}{GitHub repository}.
-
-\subsection{Survey}
-The used survey for extracting data was initially designed for developing
-a Fuzzy Inference System, but the data was labeled according to
-unsupervised clustering techniques, obtaining 2 clusters through the subtractive
-algorithm \parencite{chiu1994} and then sharpened using Fuzzy-C-Means
-\parencite{dunn1973}. The data has 6 variables and 113 observations. This
-dataset was divided with the standard $60-20-20$ rule, creating a training
-dataset with $60\%$ of the complete data, a validation set with $20\%$ and a
-test set with $20\%$ as well. All data was normalized by dividing each dimension
-by its maximum (in absolute value), casting the data into the [-1,1] hypercube.
-
-\subsection{Support Vector Machines}
-\textcite{burges1998} published an excellent reference for the theoretical
-background on SVMs with different kernels and explains the formulation of the
-optimization problem. The SVMs were used directly from Scikit-Learn
-\parencite{scikit-learn, sklearn_api} using
-\href{https://bit.ly/3lDHADX}{Julia's API}. The SVMs were trained using three
-different kernels: linear, polynomial and RBF (radial base function).
-
-\subsection{Decision Trees}
-We refer to \textcite{bramer2007} for the general ideas behind the decision tree
-classifier.
-
-\subsection{Neural Networks}
-The book of \textcite{aggarwal2018} was used as primary reference for the
-formulation of the NN learning machine and the details of its implementation,
-such as the backpropagation algorithm and the bias correction.
-The NN was implemented by the authors, including the bias correction and the
-momentum acceleration term.
-
-The NNs trained used a fully-connected Multi-Layer Perceptron (MLP) using
-different number of neurons and different learning rates. The detailed process
-will be now described: let $L$ be the number of hidden layers in the MLP and let
-$\mathcal{L}\in\mathbb{R}^{L}$ be a vector containing the number of neurons on
-each hidden layer. The number of hidden layers was varied as $L=1,2,3$ and let
-$l_i$ be the number of neurons in the $i$-th layer of the MLP, hence, each
-$l_i\in\mathcal{L}$ was varied in $1,2,3$ as well. This gives a total of
-$3^1+3^2+3^3=39$ different permutations just for the architecture of the MLP,
-and this was repeated for learning rates as $\eta=0.2,0.5,0.9$, yielding a total
-of $117$ NNs to be trained.
-
-All $117$ MLPs were trained sequentially, fixing a maximum of 50 epochs,
-and only the main results for the two bests and for the worst MLP configurations
-will be presented, in order to keep this paper concrete. The order relation
-between the trained NNs was established by evaluating the cost function at the
-end of the final epoch. All MLPs used the sigmoid activation function.
-
-The results are presented using three learning curves: the sum of local
-gradients per layer at the end of each epoch, the average error energy and a
-Receiver Operating Characteristic (ROC) curve, comparing the obtained results
-with the real labels.
-\begin{itemize}
-  \item The sum of gradients per layer at the end of each epoch is an approach
-  visualizing if the training algorithm is solving the optimization problem,
-  since the sum of local gradients must converge to zero as each gradient
-  converges to zero. It is well-known that the vanish of gradients is a
-  necessary condition for optimality and the training algorithm is just an
-  optimization problem minimizing the output error (cost function).
-  \item The average error energy is the cost function of the optimization
-  problem. Let $y_i\in\mathbb{R}^n$ be the real output of a given input pattern
-  $x_i\in\mathbb{R}^m$ and let $\hat{y}_i\in\mathbb{R}^n$ be the output of the
-  NN for the same input pattern. Denoting each component by superscripts, the
-  average error energy $\xi_{av}$ on each epoch is then computed as
-  \begin{equation}
-    \xi_{av}=\dfrac{1}{2}\sum_{i=1}^{N}\sum_{k=1}^n\left(y^k_i-\hat{y}^k_i\right)^2,
-  \end{equation}
-  where $N$ is the training sample size. Thus, it is clear that
-  $\xi_{av}\rightarrow0$ as the training algorithm solves the learning problem
-  well.
-  \item The ROC curve is a tool that helps visualize the correct classifications
-  of the learning machine by plotting the true positive rate on the vertical
-  axis, and false positive rate on the horizontal axis. The Area Under the Curve
-  (AUC) is an indicator of how good the data is being classified by the model,
-  with higher values being better usually better.
-\end{itemize}
-
-\section{Results}\label{sec:res}
-For giving an idea of the dataset treated in this work (visualization), the data
-was embedded into a 2-dimensional space using the T-student Stochastic
-Neighborhood Embedding (TSNE) \href{https://github.com/lejon/TSne.jl}{in Julia}
-\parencite{maaten2008}. In Fig. \ref{fig:emb_dat}, the embedded dataset is
-presented.
-\begin{figure}
-  \includegraphics[width=\columnwidth]{figs/embedded-data.pdf}
-  \caption{Embedded dataset.}
-  \label{fig:emb_dat}
-\end{figure}
-
-\subsection{Support Vector Machines}
 \begin{figure*}
@@
 
-\subsection{Decision Trees}
-\begin{figure}
-    \includegraphics[width=\columnwidth]{figs/tree-graph.pdf}
-    \caption{Decision tree.}
-    \label{fig:dt}
-\end{figure}
+\begin{table}
+\centering
+\caption{Performance scores for linear SVM.}
+\label{tab:linear_SVM}
+\begin{tabular}{ccc}
+\hline
+\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
+Training & 0 & 1 \\
+Testing & 0 & 1 \\
+Validation & 0 & 1 \\ \hline
+\end{tabular}
+\end{table}
 
-\begin{figure*}
+\begin{table}
 \centering
-    \begin{subfigure}[b]{0.32\textwidth}
+\caption{Performance scores for polynomial SVM.}
+\label{tab:poly_SVM}
+\begin{tabular}{cll}
+\hline
+\textbf{Set} & \multicolumn{1}{c}{\textbf{Sensitivity}} & \multicolumn{1}{c}{\textbf{Specificity}} \\ \hline
+Training & 0.89 & 1 \\
+Testing & 0 & 1 \\
+Validation & 0.57 & 1 \\ \hline
+\end{tabular}
+\end{table}
+
+\begin{table}
 \centering
-        \includegraphics[width=\textwidth]{figs/tree-contour-0-3.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/tree-contour-0-4.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/tree-contour-0-5.pdf}
-        \caption{}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/tree-contour-1-3.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/tree-contour-1-4.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/tree-contour-1-5.pdf}
-        \caption{}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/tree-contour-2-3.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/tree-contour-2-4.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/tree-contour-2-5.pdf}
-        \caption{}
-    \end{subfigure}
-    \caption{Decision Tree contour with real labels.}
-    \label{fig:dts}
-\end{figure*}
-
-\subsection{Neural Networks}
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/1-2-3-0.9-gradients.pdf}
-        \caption{Gradients for each layer.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/1-2-3-0.9-error.pdf}
-        \caption{Average error energy per epoch.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/1-2-3-0.9-roc.pdf}
-        \caption{ROC curve.}
-    \end{subfigure}
-    \caption{Learning curves for $\mathcal{L}=[1,2,3]$ network $\eta=0.9$
-    (worst).}
-    \label{fig:NN-worst}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-0.9-gradients.pdf}
-        \caption{Gradients for each layer.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-0.9-error.pdf}
-        \caption{Average error energy per epoch.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-0.9-roc.pdf}
-        \caption{ROC curve.}
-    \end{subfigure}
-    \caption{Learning curves for $\mathcal{L}=[2]$ network with $\eta=0.9$
-     (2nd best).}
-    \label{fig:NN-2best}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/3-0.9-gradients.pdf}
-        \caption{Gradients for each layer.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/3-0.9-error.pdf}
-        \caption{Average error energy per epoch.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/3-0.9-roc.pdf}
-        \caption{ROC curve.}
-    \end{subfigure}
-    \caption{Learning curves for $\mathcal{L}=[3]$ network with $\eta=0.9$
-    (best).}
-    \label{fig:NN-best}
-\end{figure*}
-
-\section{Conclusions}\label{sec:conc}
-
-\printbibliography
-
-\appendices
-
-\section{Results for Embedded Data}
-This section presents the same results above presented but for the data
-embedded with the TSNE algorithm prior to training.
-\subsection{Support Vector Machines}
-\begin{figure}
-  \includegraphics[width=\columnwidth]{figs/svm-emb-linear-contour-0-1.pdf}
-  \caption{Linear kernel SVM contour with real labels.}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{figs/svm-emb-poly-contour-0-1.pdf}
-  \caption{Polynomial kernel SVM contour with real labels.}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{figs/svm-emb-rbf-contour-0-1.pdf}
-  \caption{RBF kernel SVM contour with real labels.}
-\end{figure}
-
-\subsection{Decision Tree}
-\begin{figure}
-    \includegraphics[width=\columnwidth]{figs/tree-emb-graph.pdf}
-    \caption{Decision tree.}
-\end{figure}
-
-\begin{figure}
-    \includegraphics[width=\columnwidth]{figs/tree-contour-0-1.pdf}
-    \caption{Decision Tree contour with real labels.}
-\end{figure}
-
-\subsection{Neural Networks}
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-gradients.pdf}
-        \caption{Gradients for each layer.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-error.pdf}
-        \caption{Average error energy per epoch.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-roc.pdf}
-        \caption{ROC curve.}
-    \end{subfigure}
-    \caption{Learning curves for $\mathcal{L}=[2,3,3]$ network with $\eta=0.9$
-    (worst).}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/3-0.5-emb-gradients.pdf}
-        \caption{Gradients for each layer.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/3-0.5-emb-error.pdf}
-        \caption{Average error energy per epoch.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/3-0.5-emb-roc.pdf}
-        \caption{ROC curve.}
-    \end{subfigure}
-    \caption{Learning curves for $\mathcal{L}=[3]$ with $\eta=0.5$ network
-    (2nd best).}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-0.2-emb-gradients.pdf}
-        \caption{Gradients for each layer.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-0.2-emb-error.pdf}
-        \caption{Average error energy per epoch.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-0.2-emb-roc.pdf}
-        \caption{ROC curve.}
-    \end{subfigure}
-    \caption{Learning curves for $\mathcal{L}=[2]$ with $\eta=0.2$ network
-    (best).}
-\end{figure*}
-
-\end{document}
+\caption{Performance scores for RBF SVM.}
+\label{tab:rbf_SVM}
+\begin{tabular}{cll}
+\hline
+\textbf{Set} & \multicolumn{1}{c}{\textbf{Sensitivity}} & \multicolumn{1}{c}{\textbf{Specificity}} \\ \hline
+Training & 0.13 & 1 \\
+Testing & 0 & 1 \\
+Validation & 0.25 & 1 \\ \hline
+\end{tabular}
+\end{table}

### 2020-11-18 article/article.tex
[ article ] new article structure and formating

@@
 \subsection{Support Vector Machines}
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-linear-contour-0-3.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-linear-contour-0-4.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-linear-contour-0-5.pdf}
-        \caption{}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-linear-contour-1-3.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-linear-contour-1-4.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-linear-contour-1-5.pdf}
-        \caption{}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-linear-contour-2-3.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-linear-contour-2-4.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-linear-contour-2-5.pdf}
-        \caption{}
-    \end{subfigure}
-    \caption{Linear kernel SVM contour with real labels.}
-    \label{fig:SVM-linear}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-poly-contour-0-3.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-poly-contour-0-4.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-poly-contour-0-5.pdf}
-        \caption{}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-poly-contour-1-3.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-poly-contour-1-4.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-poly-contour-1-5.pdf}
-        \caption{}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-poly-contour-2-3.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-poly-contour-2-4.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-poly-contour-2-5.pdf}
-        \caption{}
-    \end{subfigure}
-    \caption{Polynomial kernel SVM contour with real labels.}
-    \label{fig:SVM-poly}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-0-3.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-0-4.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-0-5.pdf}
-        \caption{}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-1-3.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-1-4.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-1-5.pdf}
-        \caption{}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-2-3.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-2-4.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-2-5.pdf}
-        \caption{}
-    \end{subfigure}
-    \caption{RBF kernel SVM contour with real labels.}
-    \label{fig:SVM-rbf}
-\end{figure*}
-
-\begin{table}
-\centering
-\caption{Performance scores for linear SVM.}
-\label{tab:linear_SVM}
-\begin{tabular}{ccc}
-\hline
-\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
-Training & 0 & 1 \\
-Testing & 0 & 1 \\
-Validation & 0 & 1 \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table}
-\centering
-\caption{Performance scores for polynomial SVM.}
-\label{tab:poly_SVM}
-\begin{tabular}{cll}
-\hline
-\textbf{Set} & \multicolumn{1}{c}{\textbf{Sensitivity}} & \multicolumn{1}{c}{\textbf{Specificity}} \\ \hline
-Training & 0.89 & 1 \\
-Testing & 0 & 1 \\
-Validation & 0.57 & 1 \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table}
-\centering
-\caption{Performance scores for RBF SVM.}
-\label{tab:rbf_SVM}
-\begin{tabular}{cll}
-\hline
-\textbf{Set} & \multicolumn{1}{c}{\textbf{Sensitivity}} & \multicolumn{1}{c}{\textbf{Specificity}} \\ \hline
-Training & 0.13 & 1 \\
-Testing & 0 & 1 \\
-Validation & 0.25 & 1 \\ \hline
-\end{tabular}
-\end{table}
+\input{inputs/svm}
 
 \subsection{Decision Trees}
-\begin{figure}
-    \includegraphics[width=\columnwidth]{figs/tree-graph.pdf}
-    \caption{Decision tree.}
-    \label{fig:dt}
-\end{figure}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/tree-contour-0-3.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/tree-contour-0-4.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/tree-contour-0-5.pdf}
-        \caption{}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/tree-contour-1-3.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/tree-contour-1-4.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/tree-contour-1-5.pdf}
-        \caption{}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/tree-contour-2-3.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/tree-contour-2-4.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/tree-contour-2-5.pdf}
-        \caption{}
-    \end{subfigure}
-    \caption{Decision Tree contour with real labels.}
-    \label{fig:dts}
-\end{figure*}
-
-\begin{table}
-\centering
-\caption{Performance scores for DT.}
-\label{tab:DT}
-\begin{tabular}{ccc}
-\hline
-\textbf{Set} & \multicolumn{1}{c}{\textbf{Sensitivity}} & \multicolumn{1}{c}{\textbf{Specificity}} \\ \hline
-Training & 1 & 1 \\
-Testing & 0.5 & 1 \\
-Validation & 0.75 & 1 \\ \hline
-\end{tabular}
-\end{table}
+\input{inputs/dt}
 
@@
 
+\newpage
 \appendices

### 2020-11-18 article/article.tex
[ article ] finished methodology

@@
 
+Furthermore, it is important to notice that the dataset is 6-dimensional, which
+clearly brings problems for visualizing the learning machines' outputs and
+decision boundaries. In this paper, the decision functions of the fitted
+learning machines will be presented using contour plots of the projected data.
+This process will better described: each 6-dimensional pattern generates an
+output whenever it is evaluated in the fitted model. The idea is to generate an
+equally-spaced grid in $[-1,1]^6$ and evaluate each point on this model, in
+order to plot the contour of the shattering function. The main issue is that a
+direct projection into a 2-dimensional space of each point on the grid is not
+necessarily a function, since several points can have the same projection, but
+different values of the shattering function. In order to address this issue,
+the mean of the points that mapped into the same projection is taken, giving an
+proxy of the general behavior in high dimensions. This ``mean'' projection
+contour plots also include the projection of the training data points into the
+same coordinates and scattered with the real labels, giving an idea of the
+classification performance in high dimensions. Remark: as stated, the survey
+data also includes the outputs of the Fuzzy Inference System; thus, the countour
+plots are presented only for relating first input with the first input, second
+with the second output and so on. This was done aiming at two objectives:
+keeping a reasonable number of plots in the document, and giving a more
+intuitive interpretation to these plots.
+
 \subsection{Decision Trees}
@@
 but again, the size of the dataset is fixed. Thus, $\epsilon$ was calculated by
-fixing the tree depth $k$ and setting $\delta=0.7$.............
+fixing the tree depth $k=4$ and setting $\delta=0.7$ yielding a value of
+$\epsilon=0.5381$, which is a suitable value for the classifier error.
 
@@
 embedded with the TSNE algorithm prior to training.
+
 \subsection{Support Vector Machines}
+The PAC learning, results using the same optimization-sensitivity methodology,
+are presented in Fig. \ref{fig:error-SVM-emb}
+
+\begin{figure}
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-emb-linear-error.pdf}
+        \caption{Linear SVM.}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{figs/svm-emb-poly-error.pdf}
+        \caption{Polynomial SVM}
+    \end{subfigure}
+    \caption{Estimated $\epsilon$ for different training set sizes.}
+    \label{fig:error-SVM-emb}
+\end{figure}
+
 \begin{figure}
@@
 \subsection{Decision Tree}
+The estimated value of $\epsilon$ for the given training dataset size, taking
+$m=2$, a tree depth $k=5$ and a fixed $\delta=0.3$ is 0.5763.
 \begin{figure}
@@
 \label{tab:DT_emb}
-\begin{tabular}{cll}
+\begin{tabular}{ccc}
 \hline
-\textbf{Set} & \multicolumn{1}{c}{\textbf{Sensitivity}} & \multicolumn{1}{c}{\textbf{Specificity}} \\ \hline
+\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
 Training & 1 & 1 \\

### 2020-11-18 article/inputs/svm.tex
[ article ] Added linear kernel svm results.

@@
+The Linear Kernel SVM had the worst performance in comparison to the others.
+This fact can be seen in Table \ref{tab:linear_SVM}, in which is observed that
+this machine does not classify any data point to the class 1.
+
+\begin{table}
+  \centering
+  \caption{Performance scores for linear SVM.}
+  \label{tab:linear_SVM}
+  \begin{tabular}{ccc}
+    \hline
+    \textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
+    Training & 0 & 1 \\
+    Testing & 0 & 1 \\
+    Validation & 0 & 1 \\ \hline
+  \end{tabular}
+\end{table}
+
+The fact that the Linear Kernel SVM could not learn the training data set shows
+us, intuitively, that the data set is not linearly separable and that the data
+set has some non-linearities that heavily difficult the learning of it.
+Furthermore, in Fig. \ref{fig:SVM-linear} it is seen that in each of the
+projections the decision function for the linear kernel SVM is always negative.
+
 \begin{figure*}
@@
     \caption{}
+    \label{fig:SVM-linear1a}
   \end{subfigure}
@@
     \caption{}
+    \label{fig:SVM-linear1c}
   \end{subfigure}
@@
     \caption{}
+    \label{fig:SVM-linear2a}
   \end{subfigure}
@@
     \caption{}
+    \label{fig:SVM-linear2c}
   \end{subfigure}
@@
 \end{figure*}
+
+On the other hand, it is important to remark the contours still preserve a
+linear structure. This fact assures us that the procedure for which these
+contours are calculated can, partially, represent what's happening in higher
+dimensions.
+
+Lastly, it is also seen that in Figs.
+\ref{fig:SVM-linear1a}-\ref{fig:SVM-linear1c},
+\ref{fig:SVM-linear2a}-\ref{fig:SVM-linear2c} that the data are sparsed over
+some discrete lines. This also verifies the realized projection as the variables
+of this figures are discrete.
 
@@
 \centering
-\caption{Performance scores for linear SVM.}
-\label{tab:linear_SVM}
-\begin{tabular}{ccc}
-\hline
-\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
-Training & 0 & 1 \\
-Testing & 0 & 1 \\
-Validation & 0 & 1 \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table}
-\centering
 \caption{Performance scores for polynomial SVM.}

### 2020-11-18 article/inputs/svm.tex
[ article ] Complemented idea.

@@
 This fact can be seen in Table \ref{tab:linear_SVM}, in which is observed that
-this machine does not classify any data point to the class 1.
+this machine does not classify any data point to the class 1 as the sensitivity
+value is 0 for the three datasets.
 

### 2020-11-18 article/article.tex
[ article ] finished results for NN

@@
 
-\author{\IEEEauthorblockN{Juan S. Cárdenas-Rodríguez}
+\author{\IEEEauthorblockN{Juan Sebastián Cárdenas-Rodríguez}
   \IEEEauthorblockA{\textit{Department of Mathematical Sciences} \\
@@
 can be found in the authors'
-\href{https://github.com/juanscr/ai-works}{GitHub repository}.
+\href{https://github.com/juanscr/ai-works}{GitHub repository}, although the
+plots were generated using Python 3.8.6.
 
@@
 but again, the size of the dataset is fixed. Thus, $\epsilon$ was calculated by
-fixing the tree depth $k=4$ and setting $\delta=0.7$ yielding a value of
+fixing the tree depth $k=4$ and setting $\delta=0.3$ yielding a value of
 $\epsilon=0.5381$, which is a suitable value for the classifier error.
@@
 
+The results in the following sections were obtained by using the 6-dimensional
+dataset. All the procedures were also applied to the embedded 2-dimensional
+data (via TSNE) but the results are presented in Appendix \ref{app:emb}.
+
 \subsection{Support Vector Machines}
@@
 \subsection{Neural Networks}
+Recall that only the worst and 2 best NN are kept for presenting the results.
+The worst NN (in the sense of the objective function) was trained with
+$\eta=0.9$ and it has a $\mathcal{L}=[1,2,3]$ architecture in the hidden layers.
+The learning curves for this MLP are presented in Fig. \ref{fig:NN-worst}.
+This architecture is expected to perform poorly, at least for the given number
+of epochs, since it is attempting to summarize all 6 inputs in a one dimensional
+value for the first hidden layer and then casting this value into higher
+dimensions. It is unkown for the authors if this machine can learn the data at
+all, since the behavior of the backpropagation algorithm is unpredictable as
+epochs advance. Note from Fig. \ref{subfig:grad-worst-NN}, the gradients are
+stable in the epoch horizon defined, from Fig. \ref{subfig:error-worst-NN} that
+the average energy error seems to reach a stable point, but different from 0,
+finally, from Fig. \ref{subfig:roc-worst-NN}, the ROC curve and AUC confirms the
+poor performance of this classifier. Finally, the Sensitivity-Specificity
+results (see Table \ref{tab:L123}) show that this NN has adequate values for the
+specificity but deplorable values for the sensitivity.
+
 \begin{figure*}
@@
         \caption{Gradients for each layer.}
+        \label{subfig:grad-worst-NN}
     \end{subfigure}
@@
         \caption{Average error energy per epoch.}
+        \label{subfig:error-worst-NN}
     \end{subfigure}
@@
         \caption{ROC curve.}
+        \label{subfig:roc-worst-NN}
     \end{subfigure}
@@
 \end{figure*}
+
+Furthermore, the second-best NN was obtained with $\mathcal{L}=[2]$ and the best
+with $\mathcal{L}=[3]$, both trained with $\eta=0.9$. It is believed that this
+MLP obtained better results since the number of weights to optimize was
+relatively low and, hence, the backpropagation algorithm converges quickly
+(taking into consideration) the elevated learning rate. The training curves for
+these two models are presented respectively in Figs. \ref{fig:NN-2best} and
+\ref{fig:NN-best}. Note that both networks show rich dynamics on the gradients
+through the training stage, the average error energy seems to be descending into
+0 and both ROC curves are close to the perfect constant value of 1. The
+Sensitivity-Specificity values also show good results on all three sets for the
+$\mathcal{L}=3$ architecture.
 
@@
 \centering
-\caption{Performance scores for $\mathcal{L}=[3]$ and $\eta=0.9$.}
-\label{tab:L3}
+\caption{Performance scores for $\mathcal{L}=[1,2,3]$ and $\eta=0.9$.}
+\label{tab:L123}
 \begin{tabular}{ccc}
@@
 \textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
-Training & 0.5 & 1 \\
-Testing & $\times$ & 1 \\
-Validation & 1 & 1 \\ \hline
+Training & 0 & 1 \\
+Testing & 0 & 1 \\
+Validation & 0 & 1 \\ \hline
 \end{tabular}
@@
 \centering
-\caption{Performance scores for $\mathcal{L}=[1,2,3]$ and $\eta=0.9$.}
-\label{tab:L123}
+\caption{Performance scores for $\mathcal{L}=[3]$ and $\eta=0.9$.}
+\label{tab:L3}
 \begin{tabular}{ccc}
@@
 \textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
-Training & 0 & 1 \\
-Testing & 0 & 1 \\
-Validation & 0 & 1 \\ \hline
+Training & 0.5 & 1 \\
+Testing & $\times$ & 1 \\
+Validation & 1 & 1 \\ \hline
 \end{tabular}
@@
 
-\section{Results for Embedded Data}
+\section{Results for Embedded Data}\label{app:emb}
 This section presents the same results above presented but for the data

### 2020-11-18 article/inputs/svm.tex
[ article ] Added polynomial kernel svm explanation.

@@
-The Linear Kernel SVM had the worst performance in comparison to the others.
-This fact can be seen in Table \ref{tab:linear_SVM}, in which is observed that
-this machine does not classify any data point to the class 1 as the sensitivity
-value is 0 for the three datasets.
+The Linear Kernel SVM had the worst performance in comparison to the others
+SVMs. This fact can be seen in Table \ref{tab:linear_SVM}, in which is observed
+that this machine does not classify any data point to the class 1 as the
+sensitivity value is 0 for the three datasets.
 
@@
 some discrete lines. This also verifies the realized projection as the variables
-of this figures are discrete.
+of this figures where measured as discrete variables in the used survey.
+
+The Polynomial Kernel SVM had the best performance in the SVM category,
+reflected in Table \ref{tab:poly_SVM}. One important thing to notice is that the
+machine, as well as the RBF kernel SVM, was able to learn the class 0 for all
+the datasets. This fact shows that the dynamic of class 0 is easier to
+generalize and, probably, is linearly separable from class 1.
+
+\begin{table}
+  \centering
+  \caption{Performance scores for polynomial SVM.}
+  \label{tab:poly_SVM}
+  \begin{tabular}{cll}
+    \hline
+    \textbf{Set} & \multicolumn{1}{c}{\textbf{Sensitivity}} & \multicolumn{1}{c}{\textbf{Specificity}} \\ \hline
+    Training & 0.89 & 1 \\
+    Testing & 0 & 1 \\
+    Validation & 0.57 & 1 \\ \hline
+  \end{tabular}
+\end{table}
+
+On the other hand, as shown by Figs. \ref{fig:SVM-poly3a}-\ref{fig:SVM-poly3c},
+it is seen that class 0 is detailed (mostly) by the points in the middle of the
+graph. This underlies a problem in classifying these data points as they do not
+present any drastic behavior. In this manner, this SVM was able to classify it
+with some precision and shows that more data are required to fully train the
+machine to learn class 1.
 
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-poly-contour-0-3.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/svm-poly-contour-0-3.pdf}
+    \caption{}
+    \label{fig:SVM-poly1a}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.32\textwidth}
+    \centering \includegraphics[width=\textwidth]{figs/svm-poly-contour-0-4.pdf}
     \caption{}
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-poly-contour-0-4.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/svm-poly-contour-0-5.pdf}
+    \caption{}
+    \label{fig:SVM-poly1c}
+  \end{subfigure}
+
+  \begin{subfigure}[b]{0.32\textwidth}
+    \centering \includegraphics[width=\textwidth]{figs/svm-poly-contour-1-3.pdf}
+    \caption{}
+    \label{fig:SVM-poly2a}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.32\textwidth}
+    \centering \includegraphics[width=\textwidth]{figs/svm-poly-contour-1-4.pdf}
     \caption{}
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-poly-contour-0-5.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/svm-poly-contour-1-5.pdf}
     \caption{}
+    \label{fig:SVM-poly2c}
   \end{subfigure}
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-poly-contour-1-3.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/svm-poly-contour-2-3.pdf}
+    \caption{}
+    \label{fig:SVM-poly3a}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.32\textwidth}
+    \centering \includegraphics[width=\textwidth]{figs/svm-poly-contour-2-4.pdf}
     \caption{}
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-poly-contour-1-4.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/svm-poly-contour-2-5.pdf}
     \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-poly-contour-1-5.pdf}
-        \caption{}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-poly-contour-2-3.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-poly-contour-2-4.pdf}
-        \caption{}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-poly-contour-2-5.pdf}
-        \caption{}
+    \label{fig:SVM-poly3c}
   \end{subfigure}
@@
 \end{figure*}
+
+Lastly, it is seen that Figs. \ref{fig:SVM-poly1a}-\ref{fig:SVM-poly1c},
+\ref{fig:SVM-poly2a}-\ref{fig:SVM-poly2c} are not critical in separating the
+data. This occurs because the independent variable in these plots is discrete
+and probably does not contain much information surrounding the problem. This
+will be also be highlighted by the decision tree.
 
@@
 \centering
-\caption{Performance scores for polynomial SVM.}
-\label{tab:poly_SVM}
-\begin{tabular}{cll}
-\hline
-\textbf{Set} & \multicolumn{1}{c}{\textbf{Sensitivity}} & \multicolumn{1}{c}{\textbf{Specificity}} \\ \hline
-Training & 0.89 & 1 \\
-Testing & 0 & 1 \\
-Validation & 0.57 & 1 \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table}
-\centering
 \caption{Performance scores for RBF SVM.}

### 2020-11-18 article/inputs/svm.tex
[ article ] Added RBF kernel explanation.

@@
 
+The RBF kernel SVM had the second-best performance, as at least it was able to
+recognize some of the data from class 1 (in comparison to the Linear SVM). This
+is expected as in each of the projections the data did not present any circular
+relationship. This issue with using an RBF kernel can be visualized in Fig.
+\ref{fig:svm-rbf}.
+
+It is important to note, that, as with all the SVMs, the contour plotted
+preserves the structure of the used kernel and therefore confirms that the
+procedure used is correct.
+
 \begin{figure*}
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-0-3.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/svm-rbf-contour-0-3.pdf}
     \caption{}
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-0-4.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/svm-rbf-contour-0-4.pdf}
     \caption{}
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-0-5.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/svm-rbf-contour-0-5.pdf}
     \caption{}
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-1-3.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/svm-rbf-contour-1-3.pdf}
     \caption{}
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-1-4.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/svm-rbf-contour-1-4.pdf}
     \caption{}
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-1-5.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/svm-rbf-contour-1-5.pdf}
     \caption{}
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-2-3.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/svm-rbf-contour-2-3.pdf}
     \caption{}
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-2-4.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/svm-rbf-contour-2-4.pdf}
     \caption{}
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-rbf-contour-2-5.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/svm-rbf-contour-2-5.pdf}
     \caption{}

### 2020-11-18 article/article.tex
[ article ] writing ideas for conclusions

@@
   (AUC) is an indicator of how good the data is being classified by the model,
-  with higher values being better usually better.
+  with higher values being usually better.
 \end{itemize}
+
+\subsection{Sensitivity-Specificity}
+The sensitivity is a ``measure of the proportion of actual positive cases that
+got predicted as postive (true positive)'' and the specificity is ``measure of
+proportion of actual negatives that got predicted as negatives (true negatives)
+'' \parencite{sens}. This values are, hence, calculated using the formulae
+\begin{align}
+  \mathrm{Sensitivity}=&\dfrac{TP}{TP+FN},\quad
+  \\\mathrm{Specificity} =&
+  \dfrac{TN}{TN+FP},
+\end{align}
+where TP stands for True Postives, FN for False Negatives, TN for True Negatives
+and FP for False Negatives, which are extracted from a confusion matrix.
 
@@
 \section{Conclusions}\label{sec:conc}
+The results presented gave insight on how the two classes could be separated.
+The authors are keen on the idea that these shattered points could be mapped
+into a more intuitive interpretation of individuals requiring psychological
+attention (class 0) and others that show apparent ``normal'' conditions (class
+1). Note that this is pure speculation and would need confirmation by better
+qualified personnel.
+
+As for future work, the hypothesis and results here presented could be reviewed
+by an expert, since this work is preliminary and the authors are no experts in
+Mental Health. Additionally, a better review of sophisticated techniques for
+visualizing learning machines could be done, since the 2-dimensional embedding
+of the decision function (contours) was more of an heurisitc approach proposed
+by the authors and it could be somehow improved. Finally, the inclusion of more
+metrics for evaluating the performance of the classifiers can be included as
+well, since only the Sensitivity-Specificity was done.
 

### 2020-11-18 article/article.tex
[ article ] Formatted and corrected typos.

@@
 Additionally, the work presented by \textcite{shatte2019} is also a complete
-compendium of recent ML applications in mental health, including the usage
-of Support Vector Machines (SVMs), Decision Trees (DTs), Neural Networks (NN)
-and beyond. This paper includes a systematic review of over three hundred papers
-and it concludes that these techniques have brought benefits
-across the areas of diagnosis, treatment, research and clinical administration.
+compendium of recent ML applications in mental health, including the usage of
+Support Vector Machines (SVMs), Decision Trees (DTs), Neural Networks (NN) and
+beyond. This paper includes a systematic review of over three hundred papers and
+it concludes that these techniques have brought benefits across the areas of
+diagnosis, treatment, research and clinical administration.
 
@@
 
-This document is organized as
-follows: Section \ref{sec:meth} shows the general methodology used in this work,
-moreover Section \ref{sec:res} shows the obtained results over the data and
-slight modifications, finally Section \ref{sec:conc} concludes this work and
-sets pillars for future works.
+This document is organized as follows: Section \ref{sec:meth} shows the general
+methodology used in this work, moreover Section \ref{sec:res} shows the obtained
+results over the data and slight modifications, finally Section \ref{sec:conc}
+concludes this work and sets pillars for future works.
 
@@
 \subsection{Survey}
-The used survey for extracting data was initially designed in the developing
-a Fuzzy Inference System, but the data was labeled according to
-unsupervised clustering techniques, obtaining 2 clusters through the subtractive
-algorithm \parencite{chiu1994} and then sharpened using Fuzzy-C-Means
+The used survey for extracting data was initially designed in the developing a
+Fuzzy Inference System, but the data was labeled according to unsupervised
+clustering techniques, obtaining 2 clusters through the subtractive algorithm
+\parencite{chiu1994} and then sharpened using Fuzzy-C-Means
 \parencite{dunn1973}. The data has 6 variables and 113 observations. This
@@
 Remark: the dataset includes both inputs (first three variables) and outputs
-(last three variables) of the Fuzzy Inference System. This will be later
-useful to organize relationships in the variables for more intuitive plots.
+(last three variables) of the Fuzzy Inference System. This will be later useful
+to organize relationships in the variables for more intuitive plots.
 
@@
 Approximately Correct'' (PAC) learning was not straight-forward, as the
-classifier's maximum permited error $\epsilon$ was estimated from the classic
+classifier's maximum permitted error $\epsilon$ was estimated from the classic
 formulae, rather than calculating the adequate sample size for a given $\delta$.
@@
 \parencite{kubat2017}. Let $N$ be number of samples in the training set,
-$\epsilon$ is the classifier maximum permited error rate, $\delta$ is the
+$\epsilon$ is the classifier maximum permitted error rate, $\delta$ is the
 probability that a classifier with error rate greater than $\epsilon$ is
 \text{error-free} on the training set, $m$ be the dimension of each training
-patttern, and let $VC$ be the Vapnik-Chervonenkis dimension of the given
-classifier. Hence, for learning in continuous domains, the lower bound for
-$N$ is
+pattern, and let $VC$ be the Vapnik-Chervonenkis dimension of the given
+classifier. Hence, for learning in continuous domains, the lower bound for $N$
+is
 
@@
 find a suitable value for $\epsilon$. The size of training set was varied in
-$(0.8N, 10N)$ for each kernel SVM and the estimated $\epsilon$ are presented
-in Fig. \ref{fig:error-SVM}, with a fixed $\delta$. Note that $\mathrm{VC}=7$
-for the linear SVM, since
-$m=6$, and $\mathrm{VC}=84$ for the polynomial SVM, since cubic polynomials were
-selected; furthermore, the VC dimension for the RBF SVM is infinite and this
-case was not included (see \parencite{burges1998}).
+$(0.8N, 10N)$ for each kernel SVM and the estimated $\epsilon$ are presented in
+Fig. \ref{fig:error-SVM}, with a fixed $\delta$. Note that $\mathrm{VC}=7$ for
+the linear SVM, since $m=6$, and $\mathrm{VC}=84$ for the polynomial SVM, since
+cubic polynomials were selected; furthermore, the VC dimension for the RBF SVM
+is infinite and this case was not included (see \parencite{burges1998}).
 
@@
   \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-linear-error.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/svm-linear-error.pdf}
     \caption{Linear SVM.}
@@
   \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-poly-error.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/svm-poly-error.pdf}
     \caption{Polynomial SVM}
@@
 necessarily a function, since several points can have the same projection, but
-different values of the shattering function. In order to address this issue,
-the mean of the points that mapped into the same projection is taken, giving an
+different values of the shattering function. In order to address this issue, the
+mean of the points that mapped into the same projection is taken, giving an
 proxy of the general behavior in high dimensions. This ``mean'' projection
@@
 classification performance in high dimensions. Remark: as stated, the survey
-data also includes the outputs of the Fuzzy Inference System; thus, the countour
+data also includes the outputs of the Fuzzy Inference System; thus, the contour
 plots are presented only for relating first input with the first input, second
@@
 
-The same idea from the SVM classifiers for plotting the countour of the decision
+The same idea from the SVM classifiers for plotting the contour of the decision
 boundaries of the fitted model was used, plotting the training dataset with the
@@
 given by
+%
 \begin{equation}
@@
 \end{equation}
+%
 but again, the size of the dataset is fixed. Thus, $\epsilon$ was calculated by
@@
 formulation of the NN learning machine and the details of its implementation,
-such as the backpropagation algorithm and the bias correction.
-The NN was implemented by the authors, including the bias correction and the
-momentum acceleration term.
+such as the backpropagation algorithm and the bias correction. The NN was
+implemented by the authors, including the bias correction and the momentum
+acceleration term.
 
@@
 
-All $117$ MLPs were trained sequentially, fixing a maximum of 50 epochs,
-and only the main results for the two bests and for the worst MLP configurations
+All $117$ MLPs were trained sequentially, fixing a maximum of 50 epochs, and
+only the main results for the two bests and for the worst MLP configurations
 will be presented, in order to keep this paper concrete. The order relation
@@
 with the real labels.
+%
 \begin{itemize}
   \item The sum of gradients per layer at the end of each epoch is an approach
-  visualizing if the training algorithm is solving the optimization problem,
-  since the sum of local gradients must converge to zero as each gradient
-  converges to zero. It is well-known that the vanish of gradients is a
-  necessary condition for optimality and the training algorithm is just an
-  optimization problem minimizing the output error (cost function).
+        visualizing if the training algorithm is solving the optimization
+        problem, since the sum of local gradients must converge to zero as each
+        gradient converges to zero. It is well-known that the vanish of
+        gradients is a necessary condition for optimality and the training
+        algorithm is just an optimization problem minimizing the output error
+        (cost function).
   \item The average error energy is the cost function of the optimization
-  problem. Let $y_i\in\mathbb{R}^n$ be the real output of a given input pattern
-  $x_i\in\mathbb{R}^m$ and let $\hat{y}_i\in\mathbb{R}^n$ be the output of the
-  NN for the same input pattern. Denoting each component by superscripts, the
-  average error energy $\xi_{av}$ on each epoch is then computed as
+        problem. Let $y_i\in\mathbb{R}^n$ be the real output of a given input
+        pattern $x_i\in\mathbb{R}^m$ and let $\hat{y}_i\in\mathbb{R}^n$ be the
+        output of the NN for the same input pattern. Denoting each component by
+        superscripts, the average error energy $\xi_{av}$ on each epoch is then
+        computed as
+        %
         \begin{equation}
@@
   \item The ROC curve is a tool that helps visualize the correct classifications
-  of the learning machine by plotting the true positive rate on the vertical
-  axis, and false positive rate on the horizontal axis. The Area Under the Curve
-  (AUC) is an indicator of how good the data is being classified by the model,
-  with higher values being usually better.
+        of the learning machine by plotting the true positive rate on the
+        vertical axis, and false positive rate on the horizontal axis. The Area
+        Under the Curve (AUC) is an indicator of how good the data is being
+        classified by the model, with higher values being usually better.
 \end{itemize}
@@
 The sensitivity is a ``measure of the proportion of actual positive cases that
-got predicted as postive (true positive)'' and the specificity is ``measure of
+got predicted as positive (true positive)'' and the specificity is ``measure of
 proportion of actual negatives that got predicted as negatives (true negatives)
 '' \parencite{sens}. This values are, hence, calculated using the formulae
+%
 \begin{align}
-  \mathrm{Sensitivity}=&\dfrac{TP}{TP+FN},\quad
-  \\\mathrm{Specificity} =&
-  \dfrac{TN}{TN+FP},
+  \mathrm{Sensitivity}=&\dfrac{TP}{TP+FN}, \\
+  \mathrm{Specificity} =& \dfrac{TN}{TN+FP},
 \end{align}
-where TP stands for True Postives, FN for False Negatives, TN for True Negatives
-and FP for False Negatives, which are extracted from a confusion matrix.
+%
+where TP stands for True Positives, FN for False Negatives, TN for True
+Negatives and FP for False Negatives, which are extracted from a confusion
+matrix.
 
@@
 presented.
+
 \begin{figure}
@@
 The results in the following sections were obtained by using the 6-dimensional
-dataset. All the procedures were also applied to the embedded 2-dimensional
-data (via TSNE) but the results are presented in Appendix \ref{app:emb}.
+dataset. All the procedures were also applied to the embedded 2-dimensional data
+(via TSNE) but the results are presented in Appendix \ref{app:emb}.
 
@@
 $\eta=0.9$ and it has a $\mathcal{L}=[1,2,3]$ architecture in the hidden layers.
-The learning curves for this MLP are presented in Fig. \ref{fig:NN-worst}.
-This architecture is expected to perform poorly, at least for the given number
-of epochs, since it is attempting to summarize all 6 inputs in a one dimensional
+The learning curves for this MLP are presented in Fig. \ref{fig:NN-worst}. This
+architecture is expected to perform poorly, at least for the given number of
+epochs, since it is attempting to summarize all 6 inputs in a one dimensional
 value for the first hidden layer and then casting this value into higher
-dimensions. It is unkown for the authors if this machine can learn the data at
+dimensions. It is unknown for the authors if this machine can learn the data at
 all, since the behavior of the backpropagation algorithm is unpredictable as
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/1-2-3-0.9-gradients.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/1-2-3-0.9-gradients.pdf}
     \caption{Gradients for each layer.}
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/1-2-3-0.9-error.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/1-2-3-0.9-error.pdf}
     \caption{Average error energy per epoch.}
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/1-2-3-0.9-roc.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/1-2-3-0.9-roc.pdf}
     \caption{ROC curve.}
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-0.9-gradients.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/2-0.9-gradients.pdf}
     \caption{Gradients for each layer.}
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-0.9-error.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/2-0.9-error.pdf}
     \caption{Average error energy per epoch.}
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-0.9-roc.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/2-0.9-roc.pdf}
     \caption{ROC curve.}
   \end{subfigure}
-    \caption{Learning curves for $\mathcal{L}=[2]$ network with $\eta=0.9$
-     (2nd best).}
+  \caption{Learning curves for $\mathcal{L}=[2]$ network with $\eta=0.9$ (2nd
+    best).}
   \label{fig:NN-2best}
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/3-0.9-gradients.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/3-0.9-gradients.pdf}
     \caption{Gradients for each layer.}
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/3-0.9-error.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/3-0.9-error.pdf}
     \caption{Average error energy per epoch.}
@@
   \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/3-0.9-roc.pdf}
+    \centering \includegraphics[width=\textwidth]{figs/3-0.9-roc.pdf}
     \caption{ROC curve.}
@@
 visualizing learning machines could be done, since the 2-dimensional embedding
-of the decision function (contours) was more of an heurisitc approach proposed
+of the decision function (contours) was more of an heuristic approach proposed
 by the authors and it could be somehow improved. Finally, the inclusion of more

### 2020-11-18 article/article.tex
[ article ] Finished formatting appendix and file.

@@
 
-\begin{table}
+\begin{table}[H]
   \centering
@@
 
+The machine that had the best performance was the Decision Tree, in comparison
+to the SVMs and the NNs. This happened because the other machines try to
+separate the data using all the given information, meanwhile the Decision Tree
+realizes that the other variables do not give any crucial data for separating.
+Furthermore, the variable ``Emotional Socialization'' is the most important for
+classifying data.
+
 As for future work, the hypothesis and results here presented could be reviewed
@@
 
+\newpage
 \printbibliography
 
-\newpage
+\clearpage
 \appendices
@@
 \section{Results for Embedded Data}\label{app:emb}
-This section presents the same results above presented but for the data
-embedded with the TSNE algorithm prior to training.
+This section presents the same results above presented but for the data embedded
+with the TSNE algorithm prior to training.
 
@@
 The PAC learning, results using the same optimization-sensitivity methodology,
-are presented in Fig. \ref{fig:error-SVM-emb}
+are presented in Figs. \ref{fig:error-SVM-emb}, \ref{fig:error-SVM-emb2}.
 
-\begin{figure}
+\newpage
+
+\begin{figure}[H]
   \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-emb-linear-error.pdf}
-        \caption{Linear SVM.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-emb-poly-error.pdf}
-        \caption{Polynomial SVM}
-    \end{subfigure}
-    \caption{Estimated $\epsilon$ for different training set sizes.}
+  \includegraphics[width=0.8\columnwidth]{figs/svm-emb-linear-error.pdf}
+  \caption{Estimated $\epsilon$ for different training set sizes (Linear SVM).}
   \label{fig:error-SVM-emb}
@@
 
-\begin{figure}
-  \includegraphics[width=\columnwidth]{figs/svm-emb-linear-contour-0-1.pdf}
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{figs/svm-emb-poly-error.pdf}
+  \caption{Estimated $\epsilon$ for different training set sizes (Poly SVM).}
+  \label{fig:error-SVM-emb2}
+\end{figure}
+
+\begin{figure}[H]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{figs/svm-emb-linear-contour-0-1.pdf}
   \caption{Linear kernel SVM contour with real labels.}
@@
   \centering
-    \begin{subfigure}[b]{0.32\textwidth}
+  \begin{subfigure}[b]{0.3\textwidth}
     \centering
@@
   \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-error.pdf}
+  \begin{subfigure}[b]{0.3\textwidth}
+    \centering \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-error.pdf}
     \caption{Average error energy per epoch.}
   \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-roc.pdf}
+  \begin{subfigure}[b]{0.3\textwidth}
+    \centering \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-roc.pdf}
     \caption{ROC curve.}
@@
   \centering
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/3-0.5-emb-gradients.pdf}
+  \begin{subfigure}[b]{0.3\textwidth}
+    \centering \includegraphics[width=\textwidth]{figs/3-0.5-emb-gradients.pdf}
     \caption{Gradients for each layer.}
   \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/3-0.5-emb-error.pdf}
+  \begin{subfigure}[b]{0.3\textwidth}
+    \centering \includegraphics[width=\textwidth]{figs/3-0.5-emb-error.pdf}
     \caption{Average error energy per epoch.}
   \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/3-0.5-emb-roc.pdf}
+  \begin{subfigure}[b]{0.3\textwidth}
+    \centering \includegraphics[width=\textwidth]{figs/3-0.5-emb-roc.pdf}
     \caption{ROC curve.}
   \end{subfigure}
-    \caption{Learning curves for $\mathcal{L}=[3]$ with $\eta=0.5$ network
-    (2nd best).}
+  \caption{Learning curves for $\mathcal{L}=[3]$ with $\eta=0.5$ network (2nd
+    best).}
 \end{figure*}
@@
   \centering
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-0.2-emb-gradients.pdf}
+  \begin{subfigure}[b]{0.3\textwidth}
+    \centering \includegraphics[width=\textwidth]{figs/2-0.2-emb-gradients.pdf}
     \caption{Gradients for each layer.}
   \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-0.2-emb-error.pdf}
+  \begin{subfigure}[b]{0.3\textwidth}
+    \centering \includegraphics[width=\textwidth]{figs/2-0.2-emb-error.pdf}
     \caption{Average error energy per epoch.}
   \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-0.2-emb-roc.pdf}
+  \begin{subfigure}[b]{0.3\textwidth}
+    \centering \includegraphics[width=\textwidth]{figs/2-0.2-emb-roc.pdf}
     \caption{ROC curve.}

### 2020-11-18 article/article.tex
[ article ] Added abstract and keywords.

@@
 \begin{abstract}
-  Hello.
+  In this article, three different machines are used to do supervised learning
+  in a dataset recollecting important variables surrounding mental health and
+  diagnostic prediction. Outputs such as ROC curves, output contours and
+  classifier performance was realized to measure the performance of each
+  machine. Lastly, it was concluded that the Decision Tree was the learning
+  machine that performed the best and that the variable Emotional Socialization
+  is the most important variable to classify the data points.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-  Nice.
+  Supervised learning, mental health, binary classification, high dimensional
+  data, embedded data, psychological attention
 \end{IEEEkeywords}

### 2020-12-05 hybrid-models/Lenet5.jl
[ HM ] Added lene5 file.

@@ -1,0 +1,60 @@
+# Packages
+using CUDAapi
+using Flux
+using MLDatasets: MNIST
+import ProgressMeter
+
+# Number of classes
+nclass = 10
+
+# Image size
+x_pixels = 28
+y_pixels = 28
+depth = 1
+imgsize = (x_pixels, y_pixels, depth)
+
+# Layers
+C1 = Conv((5, 5), depth => 6, relu)
+S2 = MaxPool((2, 2))
+C3 = Conv((5, 5), 6 => 16, relu)
+S4 = MaxPool((2, 2))
+C5 = Dense(256, 120, relu)
+F6 = Dense(120, 84, relu)
+out = Dense(84, nclass)
+
+# Architecture
+aux_reshape1 = x -> reshape(x, imgsize..., :)
+aux_reshape2 = x -> reshape(x, :, size(x, 4))
+lenet5 = Chain(aux_reshape1, C1, S2, C3, S4, aux_reshape2, C5, F6, out);
+
+# Data
+xtrain, ytrain = MNIST.traindata(Float64)
+xtrain = reshape(xtrain, imgsize..., :)
+
+# Creating batch
+ytrain = Flux.onehotbatch(ytrain, 0:9)
+train_loader = Flux.Data.DataLoader(xtrain, ytrain, batchsize=128);
+
+# Cuda model
+model = lenet5 |> gpu
+
+# Parameters
+ps = Flux.params(lenet5)
+opt = Flux.Optimise.Descent(3e-4)
+loss(y_appr, y) = Flux.Losses.mse(y_appr, y)
+epocs = 5
+
+# Training
+for epoc in 1:epocs
+    p = ProgressMeter.Progress(length(train_loader))
+
+    for (x, y) in train_loader
+        x, y = x |> gpu, y |> gpu
+        gs = Flux.gradient(ps) do
+            y_appr = model(x)
+            loss(y_appr, y)
+        end
+        Flux.Optimise.update!(opt, ps, gs)
+        ProgressMeter.next!(p)
+    end
+end

### 2020-12-06 src/plotting/Brain.py
[ src ] Removd redundant variable.

@@ -87,7 +87,7 @@ class Brain:
         plt.clf()
 
     def plot_roc(self, name_file):
-        datax, datay = create_data("../data/num-data.csv", "../data/indexes.csv",
+        _, datay = create_data("../data/num-data.csv", "../data/indexes.csv",
                                    sep=False)
         datay = np.resize(datay, datay.shape[0])
 

### 2020-12-06 hybrid-models/Lenet5.jl
[ HM ] Added initial changes.

@@ -1,9 +1,32 @@
-# Packages
+# ========== Packages ========== #
 using CUDAapi
 using Flux
 using MLDatasets: MNIST
+using Plots
+
 import ProgressMeter
 
+# ========== Functions ========== #
+function write_file(xtest, ytest, trained_model)
+end
+
+function extract_activation(input, trained_model, layers)
+    activation_spaces = []
+    for layer in layers
+        push!(activation_spaces, trained_model[1:layer](input))
+    end
+
+    # Save image
+    for act_space in activation_spaces
+    end
+end
+
+function extract_model_info(xtest, ytest, trained_model, layers)
+    input = xtest[:, :, :, 1] |> gpu
+    extract_activation(input, trained_model, layers)
+end
+
+# ========== Parameters ========== #
 # Number of classes
 nclass = 10
 
@@ -13,6 +36,15 @@ y_pixels = 28
 depth = 1
 imgsize = (x_pixels, y_pixels, depth)
 
+# Data
+xtrain, ytrain = MNIST.traindata(Float64)
+xtrain = reshape(xtrain, imgsize..., :)
+
+# Creating batch
+ytrain = Flux.onehotbatch(ytrain, 0:9)
+train_loader = Flux.Data.DataLoader(xtrain, ytrain, batchsize=128)
+
+# ========== Lenet 5 ========== #
 # Layers
 C1 = Conv((5, 5), depth => 6, relu)
 S2 = MaxPool((2, 2))
@@ -25,16 +57,9 @@ out = Dense(84, nclass)
 # Architecture
 aux_reshape1 = x -> reshape(x, imgsize..., :)
 aux_reshape2 = x -> reshape(x, :, size(x, 4))
-lenet5 = Chain(aux_reshape1, C1, S2, C3, S4, aux_reshape2, C5, F6, out);
+lenet5 = Chain(aux_reshape1, C1, S2, C3, S4, aux_reshape2, C5, F6, out)
 
-# Data
-xtrain, ytrain = MNIST.traindata(Float64)
-xtrain = reshape(xtrain, imgsize..., :)
-
-# Creating batch
-ytrain = Flux.onehotbatch(ytrain, 0:9)
-train_loader = Flux.Data.DataLoader(xtrain, ytrain, batchsize=128);
-
+# ========== Training ========== #
 # Cuda model
 model = lenet5 |> gpu
 
@@ -58,3 +83,14 @@ for epoc in 1:epocs
         ProgressMeter.next!(p)
     end
 end
+
[…]

### 2020-12-06 hybrid-models/article/article.tex
[ HM ] Separated source code from article.

--- 2020-11-18 article/article.tex
@@
-\documentclass[conference]{IEEEtran}
+\documentclass[11pt]{article}
 \usepackage[english]{babel}
@@
 %%%%%%%% BIB-LATEX STUFF
-\usepackage[style=ieee,
-            bibstyle=ieee,
-            citestyle=ieee,
+\usepackage[style=numeric,
+            bibstyle=numeric,
+            citestyle=numeric,
             hyperref=true,
@@
 
+%%%%%%%% ENUMERATE LABEL
+% https://www.latex-tutorial.com/tutorials/lists/
+\usepackage{enumitem}
+
 %%%%%%%% CODE RENDERING !!! UNCOMMENT IF NEEDED !!!
@@
 %%%%%%%% START DOCUMENT
-\title{Supervised Learning for Psychological Attention to High School Students}
 
-\author{\IEEEauthorblockN{Juan Sebastián Cárdenas-Rodríguez}
-  \IEEEauthorblockA{\textit{Department of Mathematical Sciences} \\
-    \textit{EAFIT University}\\
-    Medellín, Colombia \\
-    jscardenar@eafit.edu.co} \and \IEEEauthorblockN{David Plazas}
-  \IEEEauthorblockA{\textit{Department of Mathematical Sciences} \\
-    \textit{EAFIT University}\\
-    Medellín, Colombia \\
-    dplazas@eafit.edu.co} }
+\title{Title here}
+\author{Juan Sebasti\'an C\'ardenas-Rodríguez \\
+  \scalebox{0.7}{Mathematical Engineering, Universidad EAFIT}}
+\date{\today}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{abstract}
-  Hello.
-\end{abstract}
-
-\begin{IEEEkeywords}
-  Nice.
-\end{IEEEkeywords}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\textit{Note}: All the code and the latex file can be found in
-\href{https://github.com/juanscr/ai-works}{the GitHub repository}.
-
-\section{Introduction}
-
-Mental health is crucially important for every human being and has become one of
-the most important issues surrounding human health. According to the World
-Health Organization (WHO)\footnote{WHO's \href{https://bit.ly/34l2v94}{2001
-    report.}} report of 2001, mental disorders can affect 25\% of the
-population, therefore, suggesting the ongoing trend of people suffering from
-lack of mental health. Additionally, with the recent events caused by the
-COVID-19 pandemic, mental issues have risen as consequence of lockdowns all
-around the globe, as have been proved by recent studies
-\parencite{rossi2020,xiong2020}.
-
-Furthermore, mental health is more important to monitor in adolescents and kids
-as this group is in the process of developing their mental structure and
-character. In this manner, as they continue creating their view about the world
-they must be surrounded by a healthy environment that promotes healthy habits
-and relationships with their surroundings.
-
-As a result, schools and parents have an important responsibility to the
-students of creating this environment and wisely handling mental health issues.
-However, high schools do not always know how to handle or detect cases of mental
-health issues. Additionally, technology has led to targeted harassing becoming
-more popular over time, therefore, complicating the probability of detecting
-these cases.
-
-Some of the most common and important mental health issues are anxiety,
-depression, and hyperkinetic disorder. According to \textcite{schulte2016},
-around 10\% to 20\% of children suffer from hyperkinetic disorder. Additionally,
-school teachers just assume this disorder is a cause of undisciplined students
-and can take the hyperkinetic student to a depressive state. These three mental
-disorders can leave severe damage to a kid and can lead them to suicide.
-
-Hence, it is of the utmost importance to quickly and efficiently detect students
-that might be having a mental health issue to immediately start a process with
-him/her. Furthermore, this detection has to be done with measurable variables
-that can be easily obtained from questionnaires or school data.
-
-The present work is oriented to the application of supervised learning
-techniques (decision trees, support vector machines and neural networks) for
-classifying the data from the survey, aiming for the construction of a model to
-detect individuals with mental health issues. Recent developments and the
-increasing popularity of supervised techniques has contributed to their
-application in different areas, among them, mental health.
-
-The novel work by \textcite{thieme2020} makes and excellent literature review of
-Machine Learning (ML) in mental health, including the current state-of-the-art
-and formulates new strategies for integrating human-oriented research with
-multi-disciplinary. They also conclude that ML applied in mental health is
-``still in its infancy'' given the complexity and difficulties of constructing
-robust models for clinically reliable outputs.
-
-Additionally, the work presented by \textcite{shatte2019} is also a complete
-compendium of recent ML applications in mental health, including the usage of
-Support Vector Machines (SVMs), Decision Trees (DTs), Neural Networks (NN) and
-beyond. This paper includes a systematic review of over three hundred papers and
-it concludes that these techniques have brought benefits across the areas of
-diagnosis, treatment, research and clinical administration.
-
-Finally, another overview of applications of Artificial Intelligence (AI) for
-Mental Illnesses is the research published by \textcite{graham2019}, where the
-authors reviewed 28 research papers which include modern methodologies (and
-technologies) for predicting or classifying psychological illnesses such as
-depression, schizophrenia or suicidal behavior. The study discusses how the
-application of AI techniques supports the clinical practice while considering
-its limitations, it also presents some ethical implications and states which
-areas need further development.
-
-This document is organized as follows: Section \ref{sec:meth} shows the general
-methodology used in this work, moreover Section \ref{sec:res} shows the obtained
-results over the data and slight modifications, finally Section \ref{sec:conc}
-concludes this work and sets pillars for future works.
-
-\section{Methodology}\label{sec:meth}
-All the code developed for this work was implemented in Julia 1.5.3. and
-can be found in the authors'
-\href{https://github.com/juanscr/ai-works}{GitHub repository}, although the
-plots were generated using Python 3.8.6.
-
-\subsection{Survey}
-The used survey for extracting data was initially designed in the developing a
-Fuzzy Inference System, but the data was labeled according to unsupervised
-clustering techniques, obtaining 2 clusters through the subtractive algorithm
-\parencite{chiu1994} and then sharpened using Fuzzy-C-Means
-\parencite{dunn1973}. The data has 6 variables and 113 observations. This
-dataset was divided with the standard $60-20-20$ rule, creating a training
-dataset with $60\%$ of the complete data, a validation set with $20\%$ and a
-test set with $20\%$ as well. All data was normalized by dividing each dimension
-by its maximum (in absolute value), casting the data into the [-1,1] hypercube.
-
-Remark: the dataset includes both inputs (first three variables) and outputs
-(last three variables) of the Fuzzy Inference System. This will be later useful
-to organize relationships in the variables for more intuitive plots.
-
-\subsection{Support Vector Machines}
-\textcite{burges1998} published an excellent reference for the theoretical
-background on SVMs with different kernels and explains the formulation of the
-optimization problem. The SVMs were used directly from Scikit-Learn
-\parencite{scikit-learn, sklearn_api} using
-\href{https://bit.ly/3lDHADX}{Julia's API}. The SVMs were trained using three
-different kernels: linear, polynomial and RBF (radial base function).
-
-Given that the sample size is fixed, the analysis for the ``Probably
-Approximately Correct'' (PAC) learning was not straight-forward, as the
-classifier's maximum permitted error $\epsilon$ was estimated from the classic
-formulae, rather than calculating the adequate sample size for a given $\delta$.
-
-The PAC learning here applied is based on the ideas presented in
-\parencite{kubat2017}. Let $N$ be number of samples in the training set,
-$\epsilon$ is the classifier maximum permitted error rate, $\delta$ is the
-probability that a classifier with error rate greater than $\epsilon$ is
-\text{error-free} on the training set, $m$ be the dimension of each training
-pattern, and let $VC$ be the Vapnik-Chervonenkis dimension of the given
-classifier. Hence, for learning in continuous domains, the lower bound for $N$
-is
-
-\begin{equation}
-  N\geq \max\left\{ \dfrac{4}{\epsilon}\ln\left(\dfrac{2}{\delta}\right),
-    \dfrac{8\mathrm{VC}}{\epsilon}\ln\left(\dfrac{13}{\epsilon}\right) \right\}.
-\end{equation}
-
-It is clear that solving for $\epsilon$ is non-trivial for given values of
-$\delta$, $N$ and $\mathrm{VC}$; thus, an optimization approach was used to
-estimate $\epsilon$ for the input values, solving the nonlinear optimization
-problem
-
-\begin{equation}
-  \begin{split}
-    \min_{\epsilon\in\mathbb{R}_+}\ &J=\,\epsilon^2\\
-    \mathrm{s.t.}\ &\dfrac{4}{\epsilon}\ln\left(\dfrac{2}{\delta} \right)\leq N\\
-    \quad&\dfrac{8\mathrm{VC}}{\epsilon}\ln\left(\dfrac{13}{\epsilon}\right)\leq N.
-  \end{split}
-\end{equation}
-
-The problem was initially constrained to $\epsilon\in[0,1]$, but it had not
-feasible solution for the size of the training set, yielding values of
-$\epsilon$ greater than 1. Instead, the constrained was removed and a
-sensitivity analysis was made for the training set size, varying the latter to
-find a suitable value for $\epsilon$. The size of training set was varied in
-$(0.8N, 10N)$ for each kernel SVM and the estimated $\epsilon$ are presented in
-Fig. \ref{fig:error-SVM}, with a fixed $\delta$. Note that $\mathrm{VC}=7$ for
-the linear SVM, since $m=6$, and $\mathrm{VC}=84$ for the polynomial SVM, since
-cubic polynomials were selected; furthermore, the VC dimension for the RBF SVM
-is infinite and this case was not included (see \parencite{burges1998}).
-
-Note that $\epsilon$ in the linear SVM enters the feasible value for training
-sets above 150 samples and stabilizing around $\epsilon=0.3$ for large training
-set samples value. In contrast, $\epsilon$ for the polynomial SVM never reaches
-a suitable value below 1, indicating that this classifier requires more than 600
-samples in the training set to satisfy the PAC learning.
-
-\begin{figure}
-  \centering
-  \begin{subfigure}[b]{0.45\textwidth}
-    \centering \includegraphics[width=\textwidth]{figs/svm-linear-error.pdf}
-    \caption{Linear SVM.}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.45\textwidth}
-    \centering \includegraphics[width=\textwidth]{figs/svm-poly-error.pdf}
-    \caption{Polynomial SVM}
-  \end{subfigure}
-  \caption{Estimated $\epsilon$ for different training set sizes.}
-  \label{fig:error-SVM}
-\end{figure}
-
-Furthermore, it is important to notice that the dataset is 6-dimensional, which
-clearly brings problems for visualizing the learning machines' outputs and
-decision boundaries. In this paper, the decision functions of the fitted
-learning machines will be presented using contour plots of the projected data.
-This process will better described: each 6-dimensional pattern generates an
-output whenever it is evaluated in the fitted model. The idea is to generate an
-equally-spaced grid in $[-1,1]^6$ and evaluate each point on this model, in
-order to plot the contour of the shattering function. The main issue is that a
-direct projection into a 2-dimensional space of each point on the grid is not
-necessarily a function, since several points can have the same projection, but
-different values of the shattering function. In order to address this issue, the
-mean of the points that mapped into the same projection is taken, giving an
-proxy of the general behavior in high dimensions. This ``mean'' projection
-contour plots also include the projection of the training data points into the
-same coordinates and scattered with the real labels, giving an idea of the
-classification performance in high dimensions. Remark: as stated, the survey
-data also includes the outputs of the Fuzzy Inference System; thus, the contour
-plots are presented only for relating first input with the first input, second
-with the second output and so on. This was done aiming at two objectives:
-keeping a reasonable number of plots in the document, and giving a more
-intuitive interpretation to these plots.
-
-\subsection{Decision Trees}
-We refer to \textcite{bramer2007} for the general ideas behind the decision tree
-classifier. The DTs were used directly from Scikit-Learn
-\parencite{scikit-learn, sklearn_api} using
-\href{https://bit.ly/3lDHADX}{Julia's API}. The DT were trained using all
-default parameters in the suite, but using the ``entropy'' (information gain)
-criterion for measuring the quality of splits.
-
-The same idea from the SVM classifiers for plotting the contour of the decision
-boundaries of the fitted model was used, plotting the training dataset with the
-real labels and the contour for the decision function.
-
-Additionally, it is well-known that the bound for the training dataset size is
-given by
-%
-\begin{equation}
-  N\geq \dfrac{\ln(2)}{2\epsilon^2}\left[(2^k-1)(1+\log_2 m) + 1 + \ln\left(
-      \dfrac{1}{\delta}\right)\right],
-\end{equation}
-%
-but again, the size of the dataset is fixed. Thus, $\epsilon$ was calculated by
-fixing the tree depth $k=4$ and setting $\delta=0.3$ yielding a value of
-$\epsilon=0.5381$, which is a suitable value for the classifier error.
-
-\subsection{Neural Networks}
-The book of \textcite{aggarwal2018} was used as primary reference for the
-formulation of the NN learning machine and the details of its implementation,
-such as the backpropagation algorithm and the bias correction. The NN was
-implemented by the authors, including the bias correction and the momentum
-acceleration term.
-
-The NNs trained used a fully-connected Multi-Layer Perceptron (MLP) using
-different number of neurons and different learning rates. The detailed process
-will be now described: let $L$ be the number of hidden layers in the MLP and let
-$\mathcal{L}\in\mathbb{R}^{L}$ be a vector containing the number of neurons on
-each hidden layer. The number of hidden layers was varied as $L=1,2,3$ and let
-$l_i$ be the number of neurons in the $i$-th layer of the MLP, hence, each
-$l_i\in\mathcal{L}$ was varied in $1,2,3$ as well. This gives a total of
-$3^1+3^2+3^3=39$ different permutations just for the architecture of the MLP,
-and this was repeated for learning rates as $\eta=0.2,0.5,0.9$, yielding a total
-of $117$ NNs to be trained.
-
-All $117$ MLPs were trained sequentially, fixing a maximum of 50 epochs, and
-only the main results for the two bests and for the worst MLP configurations
-will be presented, in order to keep this paper concrete. The order relation
-between the trained NNs was established by evaluating the cost function at the
-end of the final epoch. All MLPs used the sigmoid activation function.
-
-The results are presented using three learning curves: the sum of local
-gradients per layer at the end of each epoch, the average error energy and a
-Receiver Operating Characteristic (ROC) curve, comparing the obtained results
-with the real labels.
-%
-\begin{itemize}
-  \item The sum of gradients per layer at the end of each epoch is an approach
-        visualizing if the training algorithm is solving the optimization
-        problem, since the sum of local gradients must converge to zero as each
-        gradient converges to zero. It is well-known that the vanish of
-        gradients is a necessary condition for optimality and the training
-        algorithm is just an optimization problem minimizing the output error
-        (cost function).
-  \item The average error energy is the cost function of the optimization
-        problem. Let $y_i\in\mathbb{R}^n$ be the real output of a given input
-        pattern $x_i\in\mathbb{R}^m$ and let $\hat{y}_i\in\mathbb{R}^n$ be the
-        output of the NN for the same input pattern. Denoting each component by
-        superscripts, the average error energy $\xi_{av}$ on each epoch is then
-        computed as
-        %
-        \begin{equation}
-          \xi_{av}=\dfrac{1}{2}\sum_{i=1}^{N}\sum_{k=1}^n\left(y^k_i-\hat{y}^k_i\right)^2,
-        \end{equation}
-        where $N$ is the training sample size. Thus, it is clear that
-        $\xi_{av}\rightarrow0$ is a good initial approach for evaluating the
-        learning performance.
-  \item The ROC curve is a tool that helps visualize the correct classifications
-        of the learning machine by plotting the true positive rate on the
-        vertical axis, and false positive rate on the horizontal axis. The Area
-        Under the Curve (AUC) is an indicator of how good the data is being
-        classified by the model, with higher values being usually better.
-\end{itemize}
-
-\subsection{Sensitivity-Specificity}
-The sensitivity is a ``measure of the proportion of actual positive cases that
-got predicted as positive (true positive)'' and the specificity is ``measure of
-proportion of actual negatives that got predicted as negatives (true negatives)
-'' \parencite{sens}. This values are, hence, calculated using the formulae
-%
-\begin{align}
-  \mathrm{Sensitivity}=&\dfrac{TP}{TP+FN}, \\
-  \mathrm{Specificity} =& \dfrac{TN}{TN+FP},
-\end{align}
-%
-where TP stands for True Positives, FN for False Negatives, TN for True
-Negatives and FP for False Negatives, which are extracted from a confusion
-matrix.
-
-\section{Results}\label{sec:res}
-For giving an idea of the dataset treated in this work (visualization), the data
-was embedded into a 2-dimensional space using the T-student Stochastic
-Neighborhood Embedding (TSNE) \href{https://github.com/lejon/TSne.jl}{in Julia}
-\parencite{maaten2008}. In Fig. \ref{fig:emb_dat}, the embedded dataset is
-presented.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{figs/embedded-data.pdf}
-  \caption{Embedded dataset.}
-  \label{fig:emb_dat}
-\end{figure}
-
-The results in the following sections were obtained by using the 6-dimensional
-dataset. All the procedures were also applied to the embedded 2-dimensional data
-(via TSNE) but the results are presented in Appendix \ref{app:emb}.
-
-\subsection{Support Vector Machines}
-\input{inputs/svm}
-
-\subsection{Decision Trees}
-\input{inputs/dt}
-
-\subsection{Neural Networks}
-Recall that only the worst and 2 best NN are kept for presenting the results.
-The worst NN (in the sense of the objective function) was trained with
-$\eta=0.9$ and it has a $\mathcal{L}=[1,2,3]$ architecture in the hidden layers.
-The learning curves for this MLP are presented in Fig. \ref{fig:NN-worst}. This
-architecture is expected to perform poorly, at least for the given number of
-epochs, since it is attempting to summarize all 6 inputs in a one dimensional
-value for the first hidden layer and then casting this value into higher
-dimensions. It is unknown for the authors if this machine can learn the data at
-all, since the behavior of the backpropagation algorithm is unpredictable as
-epochs advance. Note from Fig. \ref{subfig:grad-worst-NN}, the gradients are
-stable in the epoch horizon defined, from Fig. \ref{subfig:error-worst-NN} that
-the average energy error seems to reach a stable point, but different from 0,
-finally, from Fig. \ref{subfig:roc-worst-NN}, the ROC curve and AUC confirms the
-poor performance of this classifier. Finally, the Sensitivity-Specificity
-results (see Table \ref{tab:L123}) show that this NN has adequate values for the
-specificity but deplorable values for the sensitivity.
-
-\begin{figure*}
-  \centering
-  \begin{subfigure}[b]{0.32\textwidth}
-    \centering \includegraphics[width=\textwidth]{figs/1-2-3-0.9-gradients.pdf}
-    \caption{Gradients for each layer.}
-    \label{subfig:grad-worst-NN}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.32\textwidth}
-    \centering \includegraphics[width=\textwidth]{figs/1-2-3-0.9-error.pdf}
-    \caption{Average error energy per epoch.}
-    \label{subfig:error-worst-NN}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.32\textwidth}
-    \centering \includegraphics[width=\textwidth]{figs/1-2-3-0.9-roc.pdf}
-    \caption{ROC curve.}
-    \label{subfig:roc-worst-NN}
-  \end{subfigure}
-  \caption{Learning curves for $\mathcal{L}=[1,2,3]$ network $\eta=0.9$
-    (worst).}
-  \label{fig:NN-worst}
-\end{figure*}
-
-Furthermore, the second-best NN was obtained with $\mathcal{L}=[2]$ and the best
-with $\mathcal{L}=[3]$, both trained with $\eta=0.9$. It is believed that this
-MLP obtained better results since the number of weights to optimize was
-relatively low and, hence, the backpropagation algorithm converges quickly
-(taking into consideration) the elevated learning rate. The training curves for
-these two models are presented respectively in Figs. \ref{fig:NN-2best} and
-\ref{fig:NN-best}. Note that both networks show rich dynamics on the gradients
-through the training stage, the average error energy seems to be descending into
-0 and both ROC curves are close to the perfect constant value of 1. The
-Sensitivity-Specificity values also show good results on all three sets for the
-$\mathcal{L}=3$ architecture.
-
-\begin{figure*}
-  \centering
-  \begin{subfigure}[b]{0.32\textwidth}
-    \centering \includegraphics[width=\textwidth]{figs/2-0.9-gradients.pdf}
-    \caption{Gradients for each layer.}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.32\textwidth}
-    \centering \includegraphics[width=\textwidth]{figs/2-0.9-error.pdf}
-    \caption{Average error energy per epoch.}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.32\textwidth}
-    \centering \includegraphics[width=\textwidth]{figs/2-0.9-roc.pdf}
-    \caption{ROC curve.}
-  \end{subfigure}
-  \caption{Learning curves for $\mathcal{L}=[2]$ network with $\eta=0.9$ (2nd
-    best).}
-  \label{fig:NN-2best}
-\end{figure*}
-
-\begin{figure*}
-  \centering
-  \begin{subfigure}[b]{0.32\textwidth}
-    \centering \includegraphics[width=\textwidth]{figs/3-0.9-gradients.pdf}
-    \caption{Gradients for each layer.}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.32\textwidth}
-    \centering \includegraphics[width=\textwidth]{figs/3-0.9-error.pdf}
-    \caption{Average error energy per epoch.}
-  \end{subfigure}
-  \begin{subfigure}[b]{0.32\textwidth}
-    \centering \includegraphics[width=\textwidth]{figs/3-0.9-roc.pdf}
-    \caption{ROC curve.}
-  \end{subfigure}
-  \caption{Learning curves for $\mathcal{L}=[3]$ network with $\eta=0.9$
-    (best).}
-  \label{fig:NN-best}
-\end{figure*}
-
-\begin{table}
-  \centering
-  \caption{Performance scores for $\mathcal{L}=[1,2,3]$ and $\eta=0.9$.}
-  \label{tab:L123}
-  \begin{tabular}{ccc}
-    \hline
-    \textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
-    Training & 0 & 1 \\
-    Testing & 0 & 1 \\
-    Validation & 0 & 1 \\ \hline
-  \end{tabular}
-\end{table}
-
-\begin{table}
-  \centering
-  \caption{Performance scores for $\mathcal{L}=[2]$ and $\eta=0.9$.}
-  \label{tab:L2}
-  \begin{tabular}{ccc}
-    \hline
-    \textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
-    Training & $\times$ & 1 \\
-    Testing & $\times$ & 1 \\
-    Validation & $\times$ & 1 \\ \hline
-  \end{tabular}
-\end{table}
-
-\begin{table}
-  \centering
-  \caption{Performance scores for $\mathcal{L}=[3]$ and $\eta=0.9$.}
-  \label{tab:L3}
-  \begin{tabular}{ccc}
-    \hline
-    \textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
-    Training & 0.5 & 1 \\
-    Testing & $\times$ & 1 \\
-    Validation & 1 & 1 \\ \hline
-  \end{tabular}
-\end{table}
-
-\section{Conclusions}\label{sec:conc}
-The results presented gave insight on how the two classes could be separated.
-The authors are keen on the idea that these shattered points could be mapped
-into a more intuitive interpretation of individuals requiring psychological
-attention (class 0) and others that show apparent ``normal'' conditions (class
-1). Note that this is pure speculation and would need confirmation by better
-qualified personnel.
-
-As for future work, the hypothesis and results here presented could be reviewed
-by an expert, since this work is preliminary and the authors are no experts in
-Mental Health. Additionally, a better review of sophisticated techniques for
-visualizing learning machines could be done, since the 2-dimensional embedding
-of the decision function (contours) was more of an heuristic approach proposed
-by the authors and it could be somehow improved. Finally, the inclusion of more
-metrics for evaluating the performance of the classifiers can be included as
-well, since only the Sensitivity-Specificity was done.
-
 \printbibliography
-
-\newpage
-\appendices
-
-\section{Results for Embedded Data}\label{app:emb}
-This section presents the same results above presented but for the data
-embedded with the TSNE algorithm prior to training.
-
-\subsection{Support Vector Machines}
-The PAC learning, results using the same optimization-sensitivity methodology,
-are presented in Fig. \ref{fig:error-SVM-emb}
-
-\begin{figure}
-    \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-emb-linear-error.pdf}
-        \caption{Linear SVM.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/svm-emb-poly-error.pdf}
-        \caption{Polynomial SVM}
-    \end{subfigure}
-    \caption{Estimated $\epsilon$ for different training set sizes.}
-    \label{fig:error-SVM-emb}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{figs/svm-emb-linear-contour-0-1.pdf}
-  \caption{Linear kernel SVM contour with real labels.}
-\end{figure}
-
-\begin{table}
-\centering
-\caption{Performance scores for linear SVM.}
-\label{tab:linear_SVM_emb}
-\begin{tabular}{ccc}
-\hline
-\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
-Training & 0 & 1 \\
-Testing & 0 & 1 \\
-Validation & 0 & 1 \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{figs/svm-emb-poly-contour-0-1.pdf}
-  \caption{Polynomial kernel SVM contour with real labels.}
-\end{figure}
-
-\begin{table}
-\centering
-\caption{Performance scores for polynomial SVM.}
-\label{tab:poly_SVM_emb}
-\begin{tabular}{ccc}
-\hline
-\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
-Training & 0 & 1 \\
-Testing & 0 & 1 \\
-Validation & 0 & 1 \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{figs/svm-emb-rbf-contour-0-1.pdf}
-  \caption{RBF kernel SVM contour with real labels.}
-\end{figure}
-
-\begin{table}
-\centering
-\caption{Performance scores for polynomial RBF.}
-\label{tab:rbf_SVM_emb}
-\begin{tabular}{ccc}
-\hline
-\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
-Training & 0 & 1 \\
-Testing & 0 & 1 \\
-Validation & 0 & 1 \\ \hline
-\end{tabular}
-\end{table}
-
-\subsection{Decision Tree}
-The estimated value of $\epsilon$ for the given training dataset size, taking
-$m=2$, a tree depth $k=5$ and a fixed $\delta=0.3$ is 0.5763.
-\begin{figure}
-    \includegraphics[width=\columnwidth]{figs/tree-emb-graph.pdf}
-    \caption{Decision tree.}
-\end{figure}
-
-\begin{figure}
-    \includegraphics[width=\columnwidth]{figs/tree-contour-0-1.pdf}
-    \caption{Decision Tree contour with real labels.}
-\end{figure}
-
-\begin{table}
-\centering
-\caption{Performance scores for DT.}
-\label{tab:DT_emb}
-\begin{tabular}{ccc}
-\hline
-\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
-Training & 1 & 1 \\
-Testing & 0 & 1 \\
-Validation & 0.63 & 0.94 \\ \hline
-\end{tabular}
-\end{table}
-
-\subsection{Neural Networks}
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-gradients.pdf}
-        \caption{Gradients for each layer.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-error.pdf}
-        \caption{Average error energy per epoch.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-3-3-0.9-emb-roc.pdf}
-        \caption{ROC curve.}
-    \end{subfigure}
-    \caption{Learning curves for $\mathcal{L}=[2,3,3]$ network with $\eta=0.9$
-    (worst).}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/3-0.5-emb-gradients.pdf}
-        \caption{Gradients for each layer.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/3-0.5-emb-error.pdf}
-        \caption{Average error energy per epoch.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/3-0.5-emb-roc.pdf}
-        \caption{ROC curve.}
-    \end{subfigure}
-    \caption{Learning curves for $\mathcal{L}=[3]$ with $\eta=0.5$ network
-    (2nd best).}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-0.2-emb-gradients.pdf}
-        \caption{Gradients for each layer.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-0.2-emb-error.pdf}
-        \caption{Average error energy per epoch.}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figs/2-0.2-emb-roc.pdf}
-        \caption{ROC curve.}
-    \end{subfigure}
-    \caption{Learning curves for $\mathcal{L}=[2]$ with $\eta=0.2$ network
-    (best).}
-\end{figure*}
-
-\begin{table}
-\centering
-\caption{Performance scores for $\mathcal{L}=[2]$ and $\eta=0.2$.}
-\label{tab:L2_emb}
-\begin{tabular}{ccc}
-\hline
-\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
-Training & $\times$ & 1 \\
-Testing & $\times$ & 1 \\
-Validation & $\times$ & 1 \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table}
-\centering
-\caption{Performance scores for $\mathcal{L}=[3]$ and $\eta=0.5$.}
-\label{tab:L3_emb}
-\begin{tabular}{ccc}
-\hline
-\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
-Training & $\times$ & 1 \\
-Testing & $\times$ & 1 \\
-Validation & $\times$ & 1 \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table}
-\centering
-\caption{Performance scores for $\mathcal{L}=[2,3,3]$ and $\eta=0.9$.}
-\label{tab:L233_emb}
-\begin{tabular}{ccc}
-\hline
-\textbf{Set} & \textbf{Sensitivity} & \textbf{Specificity} \\ \hline
-Training & 0 & 1 \\
-Testing & 0 & 1 \\
-Validation & 0 & 1 \\ \hline
-\end{tabular}
-\end{table}
-
 \end{document}

### 2020-12-06 supervised-learning/article/inputs/dt.tex
[ SL ] Created folder for supervised learning.

In Fig. \ref{fig:dt} the decision tree structure can be found. It is important
to remark that this tree did not consider any of the discrete variables is
critical to separate the data. This was also highlighted by the SVMs, as only
the dimension that used Emotional Socialization was important to separate the
data. One crucial feature of decision trees is that they create an intuitive
structure for the dataset; in this manner, it confirms the behavior already
established for the SVM's and presents a hierarchy between the variables.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/tree-graph.pdf}
  \caption{Decision tree.}
  \label{fig:dt}
\end{figure}

In Table \ref{tab:DT} it is seen that the performance of this machine was
superior to all of the other machines in terms of specificity and sensitivity.
In this manner, this highlights that the other discrete variables may not be as
important and they may present difficulties for other machines that try to take
into account all of the variables.

\begin{table}
  \centering
  \caption{Performance scores for DT.}
  \label{tab:DT}
  \begin{tabular}{ccc}
    \hline
    \textbf{Set} & \multicolumn{1}{c}{\textbf{Sensitivity}} & \multicolumn{1}{c}{\textbf{Specificity}} \\ \hline
    Training & 1 & 1 \\
    Testing & 0.5 & 1 \\
    Validation & 0.75 & 1 \\ \hline
  \end{tabular}
\end{table}

Lastly, in Fig \ref{fig:dts} the behavior of the tree is seen. It is noticed
that the tree was apple to learn the best at classifying the class 1 separating
the space between the sides and the middle. Furthermore, it did not present any
important value for the other variables.

\begin{figure*}
  \centering
  \begin{subfigure}[b]{0.32\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/tree-contour-0-3.pdf}
    \caption{}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/tree-contour-0-4.pdf}
    \caption{}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/tree-contour-0-5.pdf}
    \caption{}
  \end{subfigure}

  \begin{subfigure}[b]{0.32\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/tree-contour-1-3.pdf}
    \caption{}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/tree-contour-1-4.pdf}
    \caption{}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/tree-contour-1-5.pdf}
    \caption{}
  \end{subfigure}

  \begin{subfigure}[b]{0.32\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/tree-contour-2-3.pdf}
    \caption{}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/tree-contour-2-4.pdf}
    \caption{}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/tree-contour-2-5.pdf}
    \caption{}
  \end{subfigure}
  \caption{Decision Tree contour with real labels.}
  \label{fig:dts}
\end{figure*}

### 2020-12-08 hybrid-models/src/Lenet5.jl
[ HM ] Added data extraction of lenet5.

@@ -1,29 +1,98 @@
 # ========== Packages ========== #
+using BSON: @save, @load
 using CUDAapi
 using Flux
 using MLDatasets: MNIST
 using Plots
+using Statistics
 
 import ProgressMeter
 
 # ========== Functions ========== #
+function get_image(input_case)
+    return reverse(input_case[:, :, 1], dims=2)'
+end
+
 function write_file(xtest, ytest, trained_model)
+    open("../results/lenet5.csv", "w") do io
+        # Real values
+        write(io, "Real\n")
+        for y in ytest
+            write(io, string(y, "\n"))
+        end
+
+        # Trained model output
+        write(io, "Model output\n")
+        for i in 1:size(xtest)[4]
+            input = xtest[:, :, :, i]
+            y_model = trained_model(input)
+
+            # Printing
+            for y in y_model
+                write(io, string(y, ","))
+            end
+            write(io, "\n")
+        end
+    end
 end
 
 function extract_activation(input, trained_model, layers)
-    activation_spaces = []
-    for layer in layers
-        push!(activation_spaces, trained_model[1:layer](input))
-    end
+    # X-test graph
+    input_cpu = input |> cpu
+    heatmap(get_image(input_cpu[:, :, 1]), color=:greys)
+    savefig("../article/figs/input-act-space.pdf")
 
-    # Save image
-    for act_space in activation_spaces
+    # Plotting activation spaces
+    for i in 1:length(layers)
+        layer = layers[i]
+        act_space = trained_model[1:layer](input) |> cpu
+
+        mean_act = mean(act_space, dims = 3)
+        heatmap(get_image(mean_act[:, :, 1]), color=:greys)
+        savefig(string("../article/figs/act-space-", i, ".pdf"))
     end
 end
 
 function extract_model_info(xtest, ytest, trained_model, layers)
-    input = xtest[:, :, :, 1] |> gpu
+    input = xtest[:, :, :, 2] |> gpu
     extract_activation(input, trained_model, layers)
+
+    # Write file
+    trained_model_cpu = trained_model |> cpu
+    write_file(xtest, ytest, trained_model_cpu)
+end
+
+function train(lenet5, train_loader; η=3e-4, epocs=200, create=true)
+    if !create
+        @load "lenet5.bson" model
[…]

### 2020-12-09 hybrid-models/src/extract-info/Lenet5.py
[ HM ] Calculated scores for lenet5.

@@ -1,0 +1,26 @@
+#!/usr/bin/env python3
+
+import numpy as np
+from sklearn.metrics import f1_score, accuracy_score
+
+# Read data
+file_csv = open("../../results/lenet5.csv").readlines()
+file_csv = list(map(lambda x: x.split(","), file_csv))
+
+# Number of test cases
+n_test = 10000
+
+# Data
+y_real = np.zeros(n_test)
+y_pred = np.zeros(n_test)
+
+for i in range(1, n_test + 1):
+    y_real[i - 1] = int(file_csv[i][0][:-1])
+
+for j in range(n_test + 2, len(file_csv)):
+    num_list = np.array(file_csv[j][:-1], dtype=float)
+    y_pred[j - n_test - 2] = np.argmax(num_list)
+
+
+print("F1 =", f1_score(y_real, y_pred, average='weighted'))
+print("Acc =", accuracy_score(y_real, y_pred))

### 2020-12-09 hybrid-models/article/article.tex
[ HM ] Added finished article.

@@
-\documentclass[11pt]{article}
+\documentclass[conference]{IEEEtran}
 \usepackage[english]{babel}
@@
 %%%%%%%% BIB-LATEX STUFF
-\usepackage[style=numeric,
-            bibstyle=numeric,
-            citestyle=numeric,
+\usepackage[style=ieee,
+            bibstyle=ieee,
+            citestyle=ieee,
             hyperref=true,
@@
 
-%%%%%%%% ENUMERATE LABEL
-% https://www.latex-tutorial.com/tutorials/lists/
-\usepackage{enumitem}
-
 %%%%%%%% CODE RENDERING !!! UNCOMMENT IF NEEDED !!!
@@
 %%%%%%%% START DOCUMENT
+\title{Experiments in Deep Learning}
 
-\title{Title here}
-\author{Juan Sebasti\'an C\'ardenas-Rodríguez \\
-  \scalebox{0.7}{Mathematical Engineering, Universidad EAFIT}}
-\date{\today}
+\author{\IEEEauthorblockN{Juan Sebastián Cárdenas-Rodríguez}
+  \IEEEauthorblockA{\textit{Department of Mathematical Sciences} \\
+    \textit{EAFIT University}\\
+    Medellín, Colombia \\
+    jscardenar@eafit.edu.co} \and \IEEEauthorblockN{David Plazas}
+  \IEEEauthorblockA{\textit{Department of Mathematical Sciences} \\
+    \textit{EAFIT University}\\
+    Medellín, Colombia \\
+    dplazas@eafit.edu.co} }
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{abstract}
+  This work presents results of experiments of some artificial intelligence
+  techniques. The work begins comparing the performance of a multilayer
+  perceptron in two scenarios: using a complete dataset andd using a synthesized
+  dataset by means of an autoencoder. The complete dataset worked better for the
+  classification task. Then, the results of training a LeNet5 architecture for
+  the MNIST hand-written digits dataset are presented, showing outstanding
+  results for a fair number of epochs. Finally, an intial approach to the GANs
+  architecture was done by two approaches: a GAN for the MNIST dataset and an
+  StyleGAN for generating and mixing styles in humand-like and anime-like faces.
+  The last part, using state-of-the-art implementations with \texttt{CUDA}.
+\end{abstract}
+
+\begin{IEEEkeywords}
+  Autoencoders, convolutional networks, GAN, StyleGAN2, MNIST, CUDA.
+\end{IEEEkeywords}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+All the source can be found in \href{https://bit.ly/3qCUuVv}{this Github
+  repository}. All the source code was tested using \texttt{Julia 1.5.3} and
+\texttt{Python 3.9.0}.
+
+\section{Introduction}
+In this work, different experiments realized, surrounding deep learning, for the
+Artificial Intelligence course of "Universidad EAFIT" are shown.
+
+In Section \ref{sec:meth} a brief introduction of the architecture and
+experiments realized are explained, in Section \ref{sec:res} the results for the
+conducted experiments are shown and in Section \ref{sec:conc} the conclusions
+for each experiment are presented.
+
+\section{Methodology}\label{sec:meth}
+\subsection{Autoencoder}
+The general ideas for the autoencoder were studied during the class and they are
+also briefly described in the course book. The autoencoders are a powerful tool
+for synthesizing information of a given input, reducing its dimensions. The most
+simple encoding architecture is a multilayer perceptron using only one hidden
+layer and using the same input as output.
+
+In our specific case, the autoencoder was used for reduction of the input
+dataset, mapping the original inputs into a 2-dimensional feature space. Then,
+the reduced dataset was compared with the original one by training the same
+classification task as in our previous work, using the best hyperparameters.
+
+\subsection{LeNet5}
+The general representation of the LeNet5 architecture is presented in Fig.
+\ref{fig:lenet5} and all the details can be found in its seminal paper in
+\parencite{lecun1998gradient}. Note that this architecture can be ``divided''
+into a convolutional component and a dense component, the former refers to an
+extraction of spatial features through filtering; the latter is designed to
+classify the input image according to all the feature extraction in the
+convolutional layers.
+
+\begin{figure*}
+  \centering \includegraphics[width=\textwidth]{figs/letnet5.png}
+  \caption{LeNet5 architecture (taken from \parencite{lecun1998gradient}).}
+  \label{fig:lenet5}
+\end{figure*}
+
+\subsection{GAN}
+The Generative Adversarial Network (GAN) was extracted from the implementation
+available in \href{https://bit.ly/39Wwirg}{this link}, and adapted for the MNIST
+dataset (originally for the Fashion-MNIST database). The general goal behind the
+GAN architecture is to construct a generator and a discriminant, such that the
+generator always attempts to cheat the discriminant by generating better data on
+each training iteration. More specifically, the objective of the generator is to
+minimize the probability of cheating and the discriminant aims to maximize the
+probability of a correct classification.
+
+\subsection{StyleGAN}
+The architecture behind the StyleGAN used in this work was initially proposed in
+\parencite{karras2019style} and then improved to the second version in
+\parencite{karras2020analyzing}. The implementation and some documentation can
+be found in \href{https://github.com/NVlabs/stylegan2}{this repository}, where
+they also offer a set of pre-trained StyleGAN architectures for different
+datasets. We focused on two networks: one trained for the FFHQ human face
+dataset, and other trained for generating Anime Portraits. An excellent gallery
+of the applications of StyleGAN2 in different types of images is presented in
+\href{https://github.com/justinpinkney/awesome-pretrained-stylegan2}{this
+  repository}.
+
+The installation of the suggested repository is really awkward, as some
+dependencies are hard to find for each system. For this, the authors suggest
+having a mirror of \texttt{Ubunt 18.04} and following the tutorial given
+\href{https://bit.ly/2VUagNB}{by this link}.
+
+\subsection{MNIST}
+The MNIST dataset contains 70k handwritten digits. This digits are represented
+by images of size $28 \times 28$ using a grey scale of colors. It was originally
+used by \parencite{lecun1998gradient} for training the LeNet5 architecture and
+is commonly used to have a base test for different machine architectures.
+
+This dataset will be used in this work for testing the LeNet5 and GAN
+architecture.
+
+\section{Results}\label{sec:res}
+
+\subsection{Autoencoder}
+As mentioned in the previous section, the dataset for the previous work was used
+to train the autoencoder. In Fig. \ref{fig:grad-encoder}, the gradients for the
+hidden and output layers are presented, where it can be observed that the data
+could not be completely learned using the architecture of a 6-dimensional input
+and output, and 2 neurons in the hidden layer, since the gradients for the
+output layers do not stabilize in zero, as expected, meaning that there is still
+error between the output of the autoencoder and the expected output.
+
+\begin{figure}
+  \centering \includegraphics[width=\columnwidth]{figs/gradients-encoder.pdf}
+  \caption{Gradients for learning the input data.}
+  \label{fig:grad-encoder}
+\end{figure}
+
+In spite of this, the data was reduced into the 2-dimensional output of the
+hidden layer. This new dataset was then passed into a multilayer perceptron with
+1 hidden layer and 3 neurons on this layer (best architecture from past works).
+One network was trained using the complete dataset and another using the reduced
+one. The results of the classification of the synthesized data are presented in
+Fig. \ref{fig:grad-encoder}, where one can observe that some points seem to be
+misclassified.
+
+\begin{figure}
+  \centering \includegraphics[width=\columnwidth]{figs/reduced-dim-data.pdf}
+  \caption{Data projection in 2D using the trained autoencoder.}
+  \label{fig:red-data}
+\end{figure}
+
+Furthermore, the training curves for the neural network in high dimensions
+(original data) are presented in Fig. \ref{fig:high-dims}. Note that the average
+error energy is descending fast and the gradients seem to be converging to
+zeros. However, Fig. \ref{fig:reduced-dims} shows the learing curves for the
+data in reduced by means of the autoencoder and it can be observed that the
+gradients are still far from converging to the optimal point and the average
+error energy is not decreasing as fast as for the data in high dimensions. This
+implies that the classifier works better in high dimensions, at least for 50
+epochs.
+
+\begin{figure}
+  \centering
+  \begin{subfigure}[b]{0.45\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/grads-learn-data.pdf}
+    \caption{Training gradients.}
+  \end{subfigure}
+    %
+  \begin{subfigure}[b]{0.45\textwidth}
+    \centering
+    \includegraphics[width=0.9\textwidth]{figs/avg-err-learn-data.pdf}
+    \caption{Training average error.}
+  \end{subfigure}
+  \caption{High dimensional dataset.}
+  \label{fig:high-dims}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \begin{subfigure}[b]{0.45\textwidth}
+    \centering
+    \includegraphics[width=0.9\textwidth]{figs/grads-learn-data-reduced.pdf}
+    \caption{Training gradients the reduced dataset.}
+  \end{subfigure}
+    %
+  \begin{subfigure}[b]{0.45\textwidth}
+    \centering
+    \includegraphics[width=0.9\textwidth]{figs/avg-err-learn-data-reduced.pdf}
+    \caption{Training average error the reduced dataset.}
+  \end{subfigure}
+  \caption{Reduced dataset.}
+  \label{fig:reduced-dims}
+\end{figure}
+
+\subsection{LeNet5}
+
+As mentioned in the previous section, this architecture was tested using the
+LeNet5 architecture. For the training, a pure gradient descent approach was used
+with an $\eta = 0.01$ and $200$ epochs. Furthermore, to accelerate training
+\texttt{CUDA} was used yielding a 2 second time of execution per epoch. This
+allowed to train the network several times and quickly test how to tune the
+hyperparameters of the training.
+
+In Table \ref{tab:scores} the scores for the LeNet5 network after training can
+be found. This scores were calculated using only the testing dataset in order to
+understand if the network could generalize to other points outside the dataset.
+It is seen that the architecture was able to successfully generalize most of the
+testing dataset; furthermore, this generalization would be improved with a more
+detailed revision in the hyperparameters of training without significantly
+changing the time of execution.
+
+\begin{table}
+  \centering
+  \begin{tabular}{cc}
+    \hline
+    $F_1$ Score & 0.977 \\
+    Accuracy    & 0.977 \\ \hline
+  \end{tabular}
+  \caption{Performance metrics for LeNet5 using testing MNIST dataset.}
+  \label{tab:scores}
+\end{table}
+
+After understanding that the architecture had successfully generalized over the
+testing dataset, it was relevant to understand how the network was able to
+classify each of the new data points. In this manner, in Fig.
+\ref{fig:lenet5-acts} the activation spaces of the first four layers can be
+seen. As each of this activation spaces contained more than 1 feature, the mean
+of each of the features per layer was calculated to get a basic idea of how
+LeNet5 worked. This activation spaces were extracted using as input the Fig.
+\ref{fig:input-act}.
+
+\begin{figure}
+  \centering \includegraphics[width=\columnwidth]{figs/input-act-space.pdf}
+  \caption{Input for extracting the activation spaces.}
+  \label{fig:input-act}
+\end{figure}
+
+Some important details arose when analyzing each of the activation spaces. In
+the first place, the first layer and second layer were responsible of removing
+the basic fodder that the handwritten digit contained. In this manner, after
+these two layers a simplified representation of the number was obtained. This is
+pretty useful for removing unneeded information such as the caligraphy of the
+person who wrote it and so fourth.
+
+In the second place, the other layers zoom in the digit to find any distinctive
+curve that could separate the number from the others. This would allow to
+recognize small details that human use to recognize handwritten digits and find
+out which class does the digit belong to. It is important to remark that this
+analysis could be extended using more samples.
+
+\begin{figure*}
+  \centering
+  \begin{subfigure}[b]{0.45\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/act-space-1.pdf}
+    \caption{Activation space of first layer.}
+  \end{subfigure}
+    %
+  \begin{subfigure}[b]{0.45\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/act-space-2.pdf}
+    \caption{Activation space of second layer.}
+  \end{subfigure}
+
+  \begin{subfigure}[b]{0.45\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/act-space-3.pdf}
+    \caption{Activation space of third layer.}
+  \end{subfigure}
+    %
+  \begin{subfigure}[b]{0.45\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/act-space-4.pdf}
+    \caption{Activation space of fourth layer.}
+  \end{subfigure}
+  \caption{Activation spaces for LeNet5 architecture.}
+  \label{fig:lenet5-acts}
+\end{figure*}
+
+Lastly, although is useful to see and understand a little bit about this
+activation spaces the LeNet5 architecture is still a black box model. In this
+manner, it is almost impossible to fully comprehend how the architecture
+connects itself and classifies the digits. In this manner, it is still a mystery
+to the authors how this works, specially in the last two layers that information
+is flattened into fully connected layers.
+
+\subsection{GAN for MNIST}
+The code used for this experiments was initially done for the Fashion-MNIST
+dataset. The authors extended the implementation specifically for the classic
+MNIST dataset and added functions for plotting. The training was done using the
+60k training subset, the images have 28$\times$28 pixels and only one color
+channel. The training was performed using a batch size of 512 images. The
+generator was trained using the \texttt{Adam} optimizer with parameters of 0.001
+and \texttt{beta\_1}=0.5. The discriminant was trained using the
+\texttt{RMSprop} with parameter of 0.005.
+
+The loss functions for both the discriminant and the generator are presented in
+Fig. \ref{fig:loss-gan} and the evolution of the generator of the GAN for 150
+epochs can be found in \href{https://bit.ly/39QXrvO}{this link.}
+
+\begin{figure}
+  \centering \includegraphics[width=\columnwidth]{figs/loss-GAN.pdf}
+  \caption{Loss during training for 150 epochs.}
+  \label{fig:loss-gan}
+\end{figure}
+
+\subsection{StyleGAN}
+
+For the StyleGAN two different pre-trained networks were used. In first place,
+the StyleGAN trained using the classic FFHQ database was used. In Fig.
+\ref{fig:grid-ffhq} the style mixing using this StyleGAN network was
+constructed. The style mixing is realized by mixing the styles of the images
+generated by the StyleGAN of the left column and the upper row. Therefore, it
+generates a new set of individuals that have mixed styles.
+
+\begin{figure}
+  \centering \includegraphics[width=\columnwidth]{figs/grid-ffhq.png}
+  \caption{Style mixing using FFHQ StyleGAN.}
+  \label{fig:grid-ffhq}
+\end{figure}
+
+It was sup rising to the author's how seamless the mixing of styles was
+realized, even taking some aspects from each picture that are not as tangible as
+lighting conditions. For example, all the first row of mixed images have that
+studio-like lighting; on the other hand, the last row of mixed images preserve
+the natural lighting proper of being outside. This features observed by the
+StyleGAN are astonishing and highlights the importance of ethics in artificial
+intelligence.
+
+In order to test how the FFHQ StyleGAN behaved with other instances of objects
+that do not belong originally to the trained data, some other samples were used
+to see how the style transfer would do. In this manner, in Fig.
+\ref{fig:stylegan-cat} the transfer style for a cat target image can be found.
+
+\begin{figure*}
+  \centering
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/ffhq-0.png}
+    \caption{Target image.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/ffhq-1.png}
+    \caption{200 iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/ffhq-2.png}
+    \caption{400 iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/ffhq-3.png}
+    \caption{600 iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/ffhq-4.png}
+    \caption{800 iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/ffhq-5.png}
+    \caption{1000 iterations.}
+  \end{subfigure}
+  \caption{Transfer style for FFHQ StyleGAN.}
+  \label{fig:stylegan-cat}
+\end{figure*}
+
+It is seen how, weirdly, attempts to transfer the learn style to a cat that does
+not belong to this original style preserving the style of both. In the first
+place, it is seen that for more iterations of the network it diverges more from
+the original dataset and gets closer to the target image. It is important to
+highlight that, at the end, a weird mix is obtained without belonging to any of
+the two classes.
+
+To further experiment, the style mixing for an Anime Portrait StyleGAN can be
+found in Fig. \label{grid-anime}. This mixing is really interesting as the
+StyleGAN has the ability to mix art styles, color schemes and even other
+non-tangible characteristics of each of the images.
+
+\begin{figure}
+  \centering \includegraphics[width=\columnwidth]{figs/grid-anime.png}
+  \caption{Style mixing using Anime Portraits StyleGAN.}
+  \label{fig:grid-anime}
+\end{figure}
+
+It is really interesting to see the ability of the artificial neural networks to
+understand and replicate this kind of art works. Furthermore, this behavior
+replicates, similarly, how humans reproduce and create art as many speculate
+that human creation comes from a similar process of style mixing. Additionally,
+this raises question if human creativity is merely a process of mixing previous
+knowledge or comes from true intelligence. In this manner, a kid's drawing is
+similar to a not-trained StyleGAN?
+
+This questions will remained unanswered. But the authors think they are of great
+importance to fully comprehend human intelligence and it's reach.
+
+In Figs. \ref{fig:ts-anime1}, \ref{fig:ts-anime2} and \ref{fig:ts-anime3} the
+transfer styles for the authors and the course teacher can be found
+respectively.
+
+\begin{figure*}
+  \centering
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/anime-deipols-0.png}
+    \caption{Target image.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/anime-deipols-1.png}
+    \caption{200 iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/anime-deipols-2.png}
+    \caption{400 iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/anime-deipols-3.png}
+    \caption{600 iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/anime-deipols-4.png}
+    \caption{800 iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/anime-deipols-5.png}
+    \caption{1000 iterations.}
+  \end{subfigure}
+  \caption{Transfer style for first human test.}
+  \label{fig:ts-anime1}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/anime-js-0.png}
+    \caption{Target image.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/anime-js-1.png}
+    \caption{200 iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/anime-js-2.png}
+    \caption{400 iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/anime-js-3.png}
+    \caption{600 iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/anime-js-4.png}
+    \caption{800 iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/anime-js-5.png}
+    \caption{1000 iterations.}
+  \end{subfigure}
+  \caption{Transfer style for second human test.}
+  \label{fig:ts-anime2}
+\end{figure*}
+
+\begin{figure*}
+  \centering
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/anime-olga-0.png}
+    \caption{Target image.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/anime-olga-1.png}
+    \caption{200 iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/anime-olga-2.png}
+    \caption{400 iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/anime-olga-3.png}
+    \caption{600 iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/anime-olga-4.png}
+    \caption{800 iterations.}
+  \end{subfigure}
+  \begin{subfigure}[b]{0.15\textwidth}
+    \centering \includegraphics[width=0.9\textwidth]{figs/anime-olga-5.png}
+    \caption{1000 iterations.}
+  \end{subfigure}
+  \caption{Transfer style for third human test.}
+  \label{fig:ts-anime3}
+\end{figure*}
+
+\section{Conclusions}\label{sec:conc}
+
+This work presented some applications of artificial intelligence techniques in
+different contexts. Although all experiments did not give completely successful
+results, all of them were implemented and/or used for their specific purpose in
+modern environments (\texttt{Python} and \texttt{Julia}) with fairly average
+hardware.
+
+First, the autoencoder was successfully implemented and contrasted with the real
+high dimensional dataset. Additionally, the LetNet5 architecture was
+successfully constructed based on \texttt{Julia}'s libraries and properly
+trained for the MNIST dataset in outstanding time (with good performance
+measures). Furthermore, the normal GAN architecture was also successfully
+trained and evaluated for the MNIST dataset as well. Finally, the StyleGAN was
+applied with two different pre-trained networks in both style transfer and style
+mixing, with fairly good execution time using personal hardware.
+
+\newpage
 \printbibliography
+
 \end{document}

### 2020-12-09 fuzzy-daples/src/FIS.jl
[ fuz ] added FIS controller code

@@ -1,0 +1,143 @@
+# Install required modules
+using Pkg
+Pkg.add("Plots")
+Pkg.add(url="https://github.com/juanscr/Fuzzy.jl")
+
+# Import modules
+using Plots
+using Fuzzy
+
+# Import functions from auxiliary file
+include("Tools.jl");
+
+# Creates figures folder for output
+if ~isdir(joinpath(pwd(), "figs"))
+    mkdir("figs");
+end
+cwd = joinpath(pwd(), "figs");
+
+## Membership functions
+# Controllers
+contMF_low = SigmoidMF(-20, 0.25, 0);
+contMF_med = BellMF(0.25, 4, 0.5);
+contMF_high = SigmoidMF(10, 0.6, 1);
+in_controllers = [contMF_low, contMF_med, contMF_high];
+plotMFs(in_controllers, [0 1], ["Low", "Medium", "High"],
+    joinpath(cwd, "contMFs.pdf")
+)
+
+# x(t)
+xMF_null = TrapezoidalMF(0, 0, 0.1, 0.2);
+xMF_controlled = BellMF(0.15, 5, 0.3);
+xMF_high = TrapezoidalMF(0.4, 0.5, 1, 1);
+in_xs = [xMF_null, xMF_controlled, xMF_high];
+plotMFs(in_xs, [0 1], ["Null", "Controlled", "High"],
+    joinpath(cwd, "stateMFs.pdf")
+)
+
+# Output controllers
+# Δs
+ω = 0.005;
+a = 10/ω;
+ΔMF_dec = SigmoidMF(-a, -ω/3, -ω);
+ΔMF_con = GaussianMF(0, ω/25);
+ΔMF_inc = SigmoidMF(a, ω/3, ω);
+out_controllers = [ΔMF_dec, ΔMF_con, ΔMF_inc];
+plotMFs(out_controllers, [-ω ω],
+    ["Decrease", "Constant", "Increase"], joinpath(cwd, "outMFs.pdf")
+)
+
+## Inputs
+in_u = Dict();
+in_u["low"] = contMF_low;
+in_u["medium"] = contMF_med;
+in_u["high"] = contMF_high;
+
+in_v = Dict();
+in_v["low"] = contMF_low;
+in_v["medium"] = contMF_med;
+in_v["high"] = contMF_high;
+
+in_x = Dict();
+in_x["null"] = xMF_null;
[…]

### 2020-12-09 fuzzy-daples/src/Tools.jl

@@ -1,0 +1,234 @@
+using Pkg
+Pkg.add("LaTeXStrings")
+using Plots
+using LaTeXStrings
+using Fuzzy
+
+# 4th-Order Runge-Kutta
+function rk4(f, x0, h, T)
+    nvars = size(x0, 1)
+    arr_size = Int(T/h)
+    xs = zeros(ComplexF64, nvars, arr_size)
+    xs[:,1] = x0
+    t = 0
+    ts = zeros(1)
+    for i in 2:arr_size
+        push!(ts, t)
+        x_aux = xs[:, i-1]
+        k1 = f(t, x_aux)
+        t += h/2
+        k2 = f(t, x_aux + k1*h/2)
+        k3 = f(t, x_aux + k2*h/2)
+        t += h/2
+        k4 = f(t, x_aux + k3*h)
+        xs[:, i] = x_aux + h*(k1 + 2*k2 + 2*k3 + k4)/6
+    end
+    return ts, xs
+end
+
+# Standard Euler's method
+function euler(f, x0, h, T)
+    nvars = size(x0, 1)
+    arr_size = Int(T/h)
+    xs = zeros(ComplexF64, nvars, arr_size)
+    xs[:,1] = x0
+    t = 0
+    ts = zeros(1)
+    for i in 2:arr_size
+        push!(ts, t)
+        x_aux = xs[:, i-1]
+        k1 = f(t, x_aux)
+        xs[:, i] = x_aux + h*f(t, x_aux)
+        t += h
+    end
+    return ts, xs
+end
+
+# Standarize plot format
+function plotPL(x, y,
+    add = nothing;
+    z = nothing,
+    label = "",
+    color = :black,
+    lw = 2,
+    legend = :right,
+    fontsize = 12,
+    font = "times",
+    xlabel = "",
+    ylabel = "",
+    zlabel = "",
+    st = :surface,
+    cam = (-30, 30)
+)
+    if isnothing(add)
+        global fig = plot(x, y,
+            label = label,
+            color = color,
+            lw = lw,
+            legend = legend,
+            xlabel = xlabel,
+            ylabel = ylabel,
+            titlefont = (fontsize, font),
+            xtickfont = (fontsize, font),
+            ytickfont = (fontsize, font),
+            legendfontsize = fontsize
+        )
+    else
+        plot!(add, x, y,
+            label = label,
+            color = color,
+            lw = lw,
+            legend = legend,
+            xlabel = xlabel,
+            ylabel = ylabel,
[…]

### 2020-12-09 unsupervised-daples/src/ClusterValidation.jl
[ uns ] added unsupervised code

@@ -1,0 +1,80 @@
+# Returns a list with matrices corresponding to the data in the i-th cluster
+function get_data_clusters(data, U)
+    k, n = size(U)
+    clusters = []
+    for j in 1:k
+        aux = argmax(U, dims=1)[[x[1] for x in argmax(U, dims=1)] .== j]
+        data_cluster = data[[x[2] for x in aux], :]
+        push!(clusters, data_cluster)
+    end
+    return clusters
+end
+
+# Calculates de Davies-Bouldin intra-cluster index
+function DB(data, protos, U, dist; arg=nothing)
+    k, n = size(U)
+    _, p = size(data)
+    clusters = get_data_clusters(data, U)
+    μs = zeros(k)
+    for i in 1:k
+        Cᵢ = clusters[i]
+        cᵢ = reshape(protos[i, :], (1, p))
+        μs[i] = sum(dist(Cᵢ, cᵢ, arg)) / size(Cᵢ, 1)
+    end
+
+    dbs = zeros(k)
+    for i in 1:k
+        aux = zeros(k)
+        cᵢ = reshape(protos[i, :], (1, p))
+        for j in 1:k
+            cⱼ = reshape(protos[j, :], (1, p))
+            if i == j
+                continue
+            end
+            dist_protos = dist(cᵢ, cⱼ, arg)[1]
+            aux[j] = (μs[i] + μs[j]) / dist_protos
+        end
+        dbs[i] = maximum(aux)
+    end
+    return sum(dbs) / k
+end
+
+# Prints the above method for the K-Means and Fuzzy-C-Means results
+function print_DB(data, Ps, Us, dist; arg=nothing)
+    print("")
+    tags = ["K-Means", "Fuzzy-C-Means"]
+    for i in 1:size(Ps, 1)
+        s = DB(data, Ps[i], Us[i], dist, arg=arg)
+        println("Davies-Bouldin index for "*tags[i]*": "*string(s))
+    end
+end
+
+# Calculates de Calinski-Harabasz
+function CH(data, protos, U, dist; arg=nothing)
+    k, n = size(U)
+    _, p = size(data)
+    clusters = get_data_clusters(data, U)
+    c = mean(data, dims=1)
+
+    dists = vec(dist(protos, c, arg)).^2
+    ns = [size(clusters[i], 1) for i in 1:k]
+    num = sum(ns .* dists)
+
+    denom = 0
+    for i in 1:k
[…]

### 2020-12-09 unsupervised-daples/src/CountryAnalysis.jl

@@ -1,0 +1,127 @@
+include("Fuzzy-C-Means.jl");
+include("K-Means.jl");
+include("Mountain.jl");
+include("Subtractive.jl");
+include("Spectral.jl")
+
+include("Tools.jl");
+include("PlotTools.jl");
+
+# Read data
+data, countries, header = read_countries("data/country-data.csv");
+
+## Statistical Analysis (over original data)
+dig = 2
+dir = "Data-Analysis"
+
+# Mean Vector
+μ = mean(data, dims = 1)
+println(h, "Mean Vector:\n", round.(μ; digits=dig))
+
+# Covariance Matrix
+Σ = cov(data)
+println("Covariance Matrix:")
+print_2Dmatrix(round.(Σ, digits=dig))
+
+# Screes (PCA) - Covariance
+js, screes_cov = screes(data)
+fig = plotPL(js, screes_cov, xlabel=L"j", ylabel=L"$\lambda_j$")
+save(fig, "screes_cov.pdf", dir=dir)
+
+# Screes (PCA) - Correlation
+js, screes_cor = screes(data, corr=true)
+fig = plotPL(js, screes_cor, xlabel=L"j", ylabel=L"$\lambda_j$")
+save(fig, "screes_cor.pdf", dir=dir)
+
+# Homogeneity test
+function homogeneity(data, part, filename; legend=:bottomright)
+    # Depth scores
+    S₁ = data[1:part, :]
+    S₂ = data[part+1:end, :]
+    Z₁, Z₂ = depths(S₁, S₂)
+    fig = ddplot(Z₁, Z₂, "ddplot_"*filename*".pdf", dir=dir, legend=legend)
+    return Z₁, Z₂, fig
+end
+
+# Multicollinearity
+cΣ = cond(Σ);
+println(h, "Condition number of Covariance Matrix: ", cΣ);
+new_data, rms, R, og_R = remove_collinear(data)
+
+# Homogeneity
+res = homogeneity(data, 84, "og")
+res = homogeneity(new_data, 84, "new_dims")
+
+## # Unsupervised Learning
+# Normalize data
+norm_data = normalize(data)
+
+# Dimension Reduction
+red_data = normalize(tsne(data, 3))
+
+## Explore space
+# Apply Mountain and Subtractive to explore the space with some parameters
+function explore_space(data, dataset, dir; n_grid=5)
+    # Explore space by Mountain clustering
+    σs = [0.1, 0.25, 0.5]
[…]

### 2020-12-09 unsupervised-daples/src/Fuzzy-C-Means.jl

@@ -1,0 +1,64 @@
+include("Tools.jl");
+
+# Initialize membership matrix with random vector
+#   c -> Number of clusters
+#   n -> Number of data points
+function initialize_membership(c, n)
+    U = zeros(c, n)
+    for j in 1:n
+        r = rand(c, 1)
+        U[:, j] = r / sum(r)
+    end
+    return U
+end
+
+# Cost Function
+#   Uᵐ -> (c, n) fuzzy membership matrix
+#   dists -> (c, n) Distance matrix
+function cost_fun(Uᵐ, dists)
+    return sum(Uᵐ .* dists.^2)
+end
+
+# Algorithm
+#   data -> (n, p) dataset matrix
+#   c -> Number of clusters
+#   dist -> Similarity function
+#   m -> Weighting exponent for fuzzy membership
+#   γ -> Tolerance for stop criterion
+#   arg -> Additional parameter for similarity function
+#   norm -> Whether the data will be normalized or not
+function fuzzy_c_means(data, c, dist, m; γ=0.001, arg=nothing, norm=true)
+    # Normalize data
+    data = norm ? normalize(data) : data
+    n, p = size(data)
+    # Initialize
+    U = initialize_membership(c, n)
+    Uᵐ = U.^m
+    # Iterate
+    improv = Inf
+    dists = zeros(c, n)
+    cost = 0
+    improvs = []
+    protos_iter = []
+    while improv >= γ
+        # Find current clusters
+        global protos = Uᵐ * data ./ sum(Uᵐ, dims=2)
+        push!(protos_iter, protos)
+        for j in 1:c
+            dists[j, :] = dist(data, reshape(protos[j, :], (1, p)), arg)
+        end
+        # Evaluate improvement
+        prev_cost = cost
+        cost = cost_fun(Uᵐ, dists)
+        improv = abs(prev_cost - cost)
+        push!(improvs, improv)
+        # New memberships
+        for i in 1:c
+            for j in 1:n
+                U[i, j] = 1 / sum((dists[i, j] ./ dists[:, j]) .^ (2 / (m - 1)))
+            end
+        end
+        Uᵐ = U.^m
+    end
+    return data, protos, U, improvs, protos_iter
+end

### 2020-12-09 unsupervised-daples/src/IrisAnalysis.jl

@@ -1,0 +1,74 @@
+include("CountryAnalysis.jl")
+include("ClusterValidation.jl")
+
+data, tags = read_iris("data/iris.data")
+
+## Statistical Analysis (over original data)
+dig = 2
+dir = "Data-Analysis-Iris"
+
+# Mean Vector
+μ = mean(data, dims = 1)
+println("Mean Vector:\n", round.(μ; digits=dig))
+
+# Covariance Matrix
+Σ = cov(data)
+println("Covariance Matrix:")
+print_2Dmatrix(round.(Σ, digits=dig))
+
+# Screes (PCA) - Covariance
+js, screes_cov = screes(data)
+fig = plotPL(js, screes_cov, xlabel=L"j", ylabel=L"$\lambda_j$")
+save(fig, "screes_cov_iris.pdf", dir=dir)
+
+# Screes (PCA) - Correlation
+js, screes_cor = screes(data, corr=true)
+fig = plotPL(js, screes_cor, xlabel=L"j", ylabel=L"$\lambda_j$")
+save(fig, "screes_cor_iris.pdf", dir=dir)
+
+# Multicollinearity
+cΣ = cond(Σ)
+println("Condition number of Covariance Matrix: ", cΣ)
+new_data, rms, R, og_R = remove_collinear(data)
+
+# Homogeneity
+res = homogeneity(data, 75, "iris", legend=:topright)
+res = homogeneity(new_data, 75, "new_dims_iris", legend=:topright)
+
+## # Unsupervised Learning
+# Normalize data
+norm_data = normalize(data)
+
+# Dimension Reduction
+red_data = normalize(tsne(data, 3))
+
+## Explore space
+# Set to 'true' to run the combinations
+explore = false
+# Using normalized high-dimensions data
+dataset_og = "og_iris"
+dir_og = "OG-Iris-Analysis"
+if explore
+    explore_space(norm_data, dataset_og, dir_og)
+end
+
+# Using normalized embedded-dimensions data
+dataset_red = "red_iris"
+dir_red = "Red-Iris-Analysis"
+if explore
+    explore_space(red_data, dataset_red, dir_red)
+end
+
+## Improve clusters
+# Original data
+Ps_og, Us_og = clusterize(norm_data, 3, dataset_og, dir_og)
+# Embedded data
+Ps_red, Us_red = clusterize(red_data, 3, dataset_red, dir_red)
+
+## Internal clustering validation
[…]

### 2020-12-09 unsupervised-daples/src/K-Means.jl

@@ -1,0 +1,48 @@
+using Pkg
+
+Pkg.add("StatsBase")
+using StatsBase
+
+include("Tools.jl");
+
+# Cost Function
+#   U -> (k, n) membership matrix
+#   dists -> (k, n) Distance matrix
+function cost_fun(U, dists)
+    return sum(U .* dists)
+end
+
+# Algorithm
+#   data -> (n, p) dataset matrix
+#   k -> Number of clusters
+#   dist -> Similarity function
+#   γ -> Tolerance for stop criterion
+#   arg -> Additional parameter for similarity function
+#   norm -> Whether the data will be normalized or not
+function k_means(data, k, dist; γ=0.001, arg=nothing, norm=true)
+    # Normalize data
+    data = norm ? normalize(data) : data
+    # Initialize prototypes
+    n = size(data, 1)
+    indexes = collect(1:n)
+    selection = sample(indexes, k, replace=false)
+    protos = data[selection, :]
+    protos_iter = [protos]
+    # Iterate k-means
+    improv = Inf
+    cost = 0
+    improvs = []
+    while improv >= γ
+        # New groups and prototypes
+        U, dists = find_membership(data, dist, protos, arg)
+        protos = (U * data) ./ sum(U, dims=2)
+        push!(protos_iter, protos)
+        # Evaluate improvement
+        prev_cost = cost
+        cost = cost_fun(U, dists)
+        improv = abs(prev_cost - cost)
+        push!(improvs, improv)
+    end
+    U, _ = find_membership(data, dist, protos, arg)
+    return data, protos, U, improvs, protos_iter
+end

### 2020-12-09 unsupervised-daples/src/Mountain.jl

@@ -1,0 +1,158 @@
+include("Tools.jl");
+
+# Construct grid
+#   data -> (n, p) dataset matrix
+#   n_grid -> Number of points on each dimension
+function construct_grid(data, n_grid)
+    n, p = size(data)
+    uppers = data[argmax(data, dims=1)]
+    lowers = data[argmin(data, dims=1)]
+    aux = []
+    for i in 1:p
+        h = (uppers[i] - lowers[i]) / n_grid
+        push!(aux, lowers[i]:h:uppers[i])
+    end
+    grid = collect(Iterators.product(aux...))
+    return grid, aux
+end
+
+# Evaluate function with each point on the grid
+#   grid -> (n₁,...,nₚ) matrix
+#   f -> Function to apply
+function eval_grid(grid, f)
+    return f.(grid)
+end
+
+# Algorithm
+#   data -> (n, p) dataset matrix
+#   dist -> Similarity function
+#   n_grid -> Number of points on each dimension
+#   σ -> Original neighborhood parameter in initial density
+#   β -> Update neighborhood in new density
+#   n_it -> Maximum number of iterations
+#   arg -> Additional parameter for similarity function
+#   γ -> Tolerance for stop criterion
+#   norm -> Whether the data will be normalized or not
+function mountain_cluster(data, dist, n_grid, σ, β;
+    n_it = 10, γ=0.4, arg=nothing, norm=true, full=true, v=false
+)
+    # Normalize data
+    data = norm ? normalize(data) : data
+    n, p = size(data)
+    # Construct grid
+    grid, aux = construct_grid(data, n_grid)
+    # Define the initial density function
+    f(v) = sum(exp.(-dist(data, reshape(collect(v), (1, p)), arg).^2 / (2*σ^2)))
+    # Iterate
+    evals = [eval_grid(grid, f)]
+    for k in 1:n_it
+        v ? println("Iter ", k) : nothing
+        # Find the point with maximum density
+        ind_max = argmax(evals[k])
+        pₖ = reshape(collect(grid[ind_max]), (1, p))
+        if k == 1
+            global M = evals[k][ind_max]
+            global protos = pₖ
+            v ? println(M) : nothing
+        else
+            # Stop criterion or accept cluster center
+            Mk = evals[k][ind_max]
+            v ? println(Mk) : nothing
+            if abs(Mk/M) < γ
+                break
+            else
+                protos = vcat(protos, pₖ)
+            end
[…]

### 2020-12-09 unsupervised-daples/src/PlotTools.jl

@@ -1,0 +1,365 @@
+using Pkg
+Pkg.add("GLM")
+Pkg.add("LaTeXStrings")
+Pkg.add("Plots")
+
+using GLM
+using LaTeXStrings
+using Plots
+
+# Standardize file saving
+function save(fig, out_file; dir="")
+    if ~isdir(joinpath(pwd(), "figs"))
+        mkdir("figs");
+    end
+    if ~isdir(joinpath(pwd(), "figs", dir))
+        mkdir(joinpath(pwd(), "figs", dir))
+    end
+    plot_wd = joinpath(pwd(), "figs", dir);
+    savefig(fig, joinpath(plot_wd, out_file))
+end
+
+# Standardize plots and surfaces
+function plotPL(x, y,
+    add = nothing;
+    z = nothing,
+    label = "",
+    color = :black,
+    lw = 2,
+    legend = :right,
+    fontsize = 12,
+    font = "times",
+    xlabel = "",
+    ylabel = "",
+    zlabel = "",
+    st = :surface,
+    cam = (-30, 30)
+)
+    if isnothing(add)
+        if isnothing(z)
+            global fig = plot(x, y,
+                label = label,
+                color = color,
+                lw = lw,
+                legend = legend,
+                xlabel = xlabel,
+                ylabel = ylabel,
+                titlefont = (fontsize, font),
+                xtickfont = (fontsize, font),
+                ytickfont = (fontsize, font),
+                # guidefont = (fontsize, font),
+                legendfontsize = fontsize
+            )
+        else
+            global fig = plot(x, y, z,
+                label = label,
+                lw = lw,
+                legend = legend,
+                xlabel = xlabel,
+                ylabel = ylabel,
+                zlabel = zlabel,
+                titlefont = (fontsize, font),
+                xtickfont = (fontsize, font),
+                ytickfont = (fontsize, font),
+                ztickfont = (fontsize, font),
+                # guidefont = (fontsize, font),
+                legendfontsize = fontsize,
+                st = st
+            )
+        end
+    else
+        if isnothing(z)
+            plot!(add, x, y,
+                label = label,
+                color = color,
+                lw = lw,
+                legend = legend,
+                xlabel = xlabel,
+                ylabel = ylabel,
+                titlefont = (fontsize, font),
+                xtickfont = (fontsize, font),
+                ytickfont = (fontsize, font),
[…]

### 2020-12-09 unsupervised-daples/src/Spectral.jl

@@ -1,0 +1,75 @@
+include("K-Means.jl")
+include("PlotTools.jl")
+
+# Graph Laplacian
+#   data -> (n, p) dataset matrix
+#   dist -> Similarity function
+#   m -> Minimum number of nearest neighbors
+#   arg -> Additional parameter for similarity function
+function laplacian_matrix(data, dist; m=6, arg=nothing)
+    n, p = size(data)
+    dists = zeros(n, n)
+    adj_matrix = zeros(n, n)
+    for j in 1:n
+        dists[j, :] = dist(data, reshape(data[j, :], (1, p)), arg)
+    end
+    for i in 1:n
+        for j in 1:m
+            ind_min = argmin(dists[i, :])
+            adj_matrix[i, ind_min] = 1
+            adj_matrix[ind_min, i] = 1
+            dists[i, ind_min] = Inf
+        end
+    end
+
+    degree_matrix = diagm(vec(sum(adj_matrix, dims=2)))
+    L = degree_matrix - adj_matrix
+    return L
+end
+
+# Algorithm
+#   data -> (n, p) dataset matrix
+#   k -> Number of clusters
+#   dist -> Similarity function
+#   m -> Minimum number of nearest neighbors
+#   arg -> Additional parameter for similarity function
+function spectral_cluster(data, k, dist; m=6, arg=nothing)
+    L = laplacian_matrix(data, dist, arg=arg, m=m)
+    eigvals, eigvecs = eigen(L)
+    eigvecs = eigvecs[:, sortperm(eigvals)]
+    W = eigvecs[:, 1:k]
+    _, _, U, _, _ = k_means(W, k, dist)
+    return U
+end
+
+# Test spectral clustering with circular data
+function test_spectral()
+    r1 = 5
+    r2 = 1
+    xs1 = collect(-r1:0.05:r1)
+    xs2 = collect(-r2:0.05:r2)
+    data1 = []
+    data2 = []
+    f(x, r) = sqrt(r^2 - x^2) + rand(Normal(0, 0.5), 1)[1]
+
+    data1 = zeros(2*size(xs1, 1), 2)
+    data1[:, 1] = vcat(xs1, xs1)
+
+    data2 = zeros(2*size(xs2, 1), 2)
+    data2[:, 1] = vcat(xs2, xs2)
+
+    for i in 1:size(xs1, 1)
+        data1[i, 2] = f(xs1[i], r1)
[…]

### 2020-12-09 unsupervised-daples/src/Subtractive.jl

@@ -1,0 +1,91 @@
+include("Tools.jl");
+
+# Algorithm
+#   data -> (n, p) dataset matrix
+#   c -> Number of clusters
+#   dist -> Similarity function
+#   rₐ -> Neighborhood parameter
+#   ϵ_up -> Upper tolerance for acceptance
+#   ϵ_down -> Lower tolerance for rejection
+#   n_it -> Maximum number of iterations
+#   arg -> Additional parameter for similarity function
+#   norm -> Whether the data will be normalized or not
+function subtractive_cluster(data, dist, rₐ;
+    ϵ_up = 0.5, ϵ_down = 0.15, n_it=10, arg=nothing, norm=true
+)
+    # Normalize data
+    data = norm ? normalize(data) : data
+    n, p = size(data)
+    rᵦ = 1.5 * rₐ
+    # Initial Densities
+    D = zeros(n, 1)
+    for j = 1:n
+        D[j, 1] = sum(exp.(-dist(data,
+            reshape(data[j, :], (1, p)), arg).^2 ./ (rₐ/2)^2))
+    end
+    # Iterate
+    evals = []
+    update = true
+    for k in 1:n_it
+        # Find point with maximum density
+        ind_max = argmax(D)[1]
+        pₖ = reshape(data[ind_max, :], (1, p))
+        if k == 1
+            global M = D[ind_max]
+            global protos = pₖ
+            push!(evals, M)
+        else
+            # Accept/Reject procedure from original paper
+            Mₖ = D[ind_max]
+            if Mₖ > ϵ_up * M
+                protos = vcat(protos, pₖ)
+                push!(evals, Mₖ)
+            elseif Mₖ < ϵ_down * M
+                break
+            else
+                dmin = minimum(dist(protos, pₖ, arg))
+                if (dmin/rₐ + Mₖ/M) >= 1
+                    protos = vcat(protos, pₖ)
+                    push!(evals, Mₖ)
+                    update = true
+                else
+                    D[ind_max] = 0
+                    update = false
+                end
+            end
+        end
+        # Updates the density with found cluster
+        if update
+            D -= D[ind_max] * exp.(-dist(data,
+                reshape(data[ind_max, :], (1, p)), arg).^2 ./ (rᵦ/2)^2)
+        end
+    end
+    # Find nearest points to found cluster centers
+    U, _ = find_membership(data, dist, protos, arg)
[…]

### 2020-12-09 unsupervised-daples/src/TestIris.jl

@@ -1,0 +1,47 @@
+include("Fuzzy-C-Means.jl");
+include("K-Means.jl");
+include("Mountain.jl");
+include("Subtractive.jl");
+
+include("PlotTools.jl");
+include("Tools.jl");
+
+## Read Iris Dataset
+data, tags = read_iris("data/iris.data")
+dist = euclidean
+
+## Mountain
+n_grid = 10
+σ = 0.1
+β = 0.15
+data, protos_mount, U_mount, grid, aux, evals_mount = mountain_cluster(
+    data, dist, n_grid, σ, β; n_it = 10, γ=0.4, arg=nothing, norm=true
+)
+
+## Subtractive
+rₐ = 0.5
+_, protos_sub, U_sub, evals_sub = subtractive_cluster(
+    data, dist, rₐ; ϵ_up = 0.5, ϵ_down = 0.15, n_it=10, arg=nothing, norm=true
+)
+k = size(protos_sub, 1)
+
+## K-Means
+_, protos_kmeans, U_kmeans, improvs_kmeans = k_means(
+    data, k, dist; γ=0.001, arg=nothing, norm=true
+)
+
+## Fuzzy C-Means
+m = 2
+_, protos_cmeans, U_cmeans, improvs_cmeans = fuzzy_c_means(
+    data, k, dist, m; γ=0.001, arg=nothing, norm=true
+)
+
+## Output Plots
+# Generate 3D proyections
+plot_nDimGroups(protos_mount, U_mount, data, "mountain-Iris", dir="Iris-Mount")
+plot_nDimGroups(protos_sub, U_sub, data, "subtractive-Iris", dir="Iris-Sub")
+plot_nDimGroups(protos_kmeans, U_kmeans, data, "KM-Iris", dir="Iris-KM")
+plot_nDimGroups(protos_cmeans, U_cmeans, data, "FCM-Iris", dir="Iris-FCM")
+
+# Generate GIFs for densities
+generate_density_gif(aux, evals_mount, "iris.gif", dir="IrisDensityGifs")

### 2020-12-09 unsupervised-daples/src/TestIrisTSNE.jl

@@ -1,0 +1,13 @@
+include("Tools.jl");
+include("PlotTools.jl");
+
+iris_data, tags = read_iris("data/iris.data");
+new_data = tsne(normalize(iris_data), verbose=true);
+
+iris_setosa = new_data[tags .== "Iris-setosa", :];
+iris_versicolor = new_data[tags .== "Iris-versicolor", :];
+iris_virginica = new_data[tags .== "Iris-virginica", :];
+
+fig = scatterPL(iris_setosa[:, 1], iris_setosa[:, 2], color=:red);
+scatterPL(iris_versicolor[:, 1], iris_versicolor[:, 2], fig, color=:black);
+scatterPL(iris_virginica[:, 1], iris_virginica[:, 2], fig, color=:orange)

### 2020-12-09 unsupervised-daples/src/TestMixtures.jl

@@ -1,0 +1,67 @@
+include("Fuzzy-C-Means.jl");
+include("K-Means.jl");
+include("Mountain.jl");
+include("Subtractive.jl");
+
+include("Tools.jl");
+include("PlotTools.jl");
+
+# Create dataset from a Mixture of Multivariate Normal Distributions
+#   k -> Number of different distributions (clusters)
+#   p -> Number of variables (set as 2 for standard plotting)
+#   n -> Size of EACH of the k samples
+#   data -> (k*n, p) data matrix
+p = 2;
+k = 3;
+n = 500;
+data = generate_MvN_Mixture(p, k, n)
+
+# Define the similarity measure in the procedure
+#   dist -> Function. It can be set to 'euclidean', 'manhattan', 'mahal' or
+#           'pnorm'. More similarities will be implemented.
+#   arg -> Extra parameter of the 'dist' function. It affects only the 'mahal'
+#          and the 'pnorm' similarity measures, as the INVERSE of the weighting
+#          matrix and the value of p, respectively.
+dist = euclidean
+arg = nothing
+
+# Directory inside 'figs' where the following results will be stored
+dir = "MvN-Mixture"
+
+## Testing
+# Based on the dataset created, each clustering algorithm is applied and the
+# results are saved on a 2D plot, which is saved inside 'dir', within 'figs'.
+# The 'plot_k_clusters' method can only plot 2D data (see 'Tools.jl').
+
+# K-Means
+data, protos, U, improvs, protos_iter = k_means(data, k, dist, arg=arg)
+plot_k_clusters(protos, U, data, "mixture_k_means.pdf", dir=dir;
+    protos_iter = protos_iter
+)
+
+# Mountain
+data, protos, U, _, _, _ = mountain_cluster(data, dist, 25, 0.1, 0.2, arg=arg)
+plot_k_clusters(protos, U, data, "mixture_mountain.pdf", dir=dir)
+
+# Fuzzy C Means
+data, protos, U, improvs, protos_iter = fuzzy_c_means(data, k, dist, 2, arg=arg)
+plot_k_clusters(protos, U, data, "mixture_fuzzy_c_means.pdf", dir=dir;
+    protos_iter = protos_iter
+)
+
+# Subtractive
+data, protos, U, evals = subtractive_cluster(data, dist, 0.5, arg=arg)
[…]

### 2020-12-09 unsupervised-daples/src/Tools.jl

@@ -1,0 +1,180 @@
+using Pkg
+Pkg.add("Distributions")
+Pkg.add("LinearAlgebra")
+Pkg.add("TSne")
+
+using Distributions
+using LinearAlgebra
+using TSne
+
+## Similarities
+function pnorm(data, y, arg)
+    return (sum(abs.(data .- y).^arg, dims=2)).^(1/arg)
+end
+
+function euclidean(data, y, arg)
+    return pnorm(data, y, 2)
+end
+
+function manhattan(data, y, arg)
+    return pnorm(data, y, 1)
+end
+
+function mahal(data, y, IV)
+    diff = data .- y
+    return sqrt.(sum(diff * IV .* diff, dims=2))
+end
+
+## Misc
+# Find memebership matrix of data to given cluster centers
+function find_membership(data, dist, protos, arg)
+    n = size(data, 1)
+    k, p = size(protos)
+    U = zeros(k, n)
+    dists = zeros(k, n)
+    for j in 1:k
+        dists[j, :] = dist(data, reshape(protos[j, :], (1, p)), arg)
+    end
+    indexes_min = argmin(dists, dims=1)
+    U[indexes_min] .= 1
+    return U, dists
+end
+
+# Randomizes parameters for a Multivariate Normal Distributions for gen([a,b])
+function rand_params_MvN(a, b, p)
+    u = Uniform(a, b)
+    μ = rand(u, p)
+    Σ = rand(p, p)
+    Σ = 0.5 * (Σ + Σ') + p*I
+    return μ, Σ
+end
+
+# Generates data from a Multivariate Normal Distribution
+function generate_MvN_Mixture(p, k, n; b = 25)
+    data = rand(MvNormal(rand_params_MvN(0, b, p)...), n)';
+    for j = 1:k-1
+        data = vcat(data, rand(MvNormal(rand_params_MvN(0, b, p)...), n)')
+    end
+    return data
+end
+
+# Normalize data with max|x_i| -> [-1,1] hypercube.
+function normalize(data)
+    return data ./ maximum(abs.(data), dims=1)
+end
+
+# Read Iris dataset
+function read_iris(iris_file)
+    iris_file = open(iris_file, "r") do io
+        read(io, String)
+    end
+    lines = split(iris_file, "\n")[1:end-1]
+    lines = replace.(lines, "\r" => "")
+    data = split.(lines, ",")
+    tags = map(x -> x[end], data)
[…]

### 2020-12-09 fuzzy-juanscr/article/article.tex
[ FJ ] Added fuzzy-juanscr first project.

\documentclass[conference]{IEEEtran}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}

%%%%%%%% SUB-FIGURE PACKAGE
\usepackage{subcaption}

%%%%%%%% HYPERREF PACKAGE
\usepackage{hyperref}
\hypersetup{linkcolor=blue}
\hypersetup{citecolor=blue}
\hypersetup{urlcolor=blue}
\hypersetup{colorlinks=true}

%%%%%%%% DEFINITION AND THEOREM DEFINITIONS
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\theoremstyle{remark}
\newtheorem{question}{Question}

\newtheorem{theorem}{Theorem}[section]

%%%%%%%% MULTI-COLUMNS PACKAGE
\usepackage{multicol}

%%%%%%%% BIB-LATEX STUFF
\usepackage[style=ieee,
            bibstyle=ieee,
            citestyle=ieee,
            hyperref=true,
            backend=biber]{biblatex}
\addbibresource{ref.bib} %Put relative path to ref

%%%%%%%% PERSONAL COMMANDS
\usepackage{amssymb}

%%%% Important sets
\renewcommand{\O}{\mathbb{O}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{{\mathbb{Z}}}
\newcommand{\Q}{{\mathbb{Q}}}
\newcommand{\R}{{\mathbb{R}}}

%%%% Usual operations
\newcommand{\pow}[2]{#1^{#2}}
\newcommand{\expp}[1]{e^{#1}}
\newcommand{\fst}{\mathrm{fst}}
\newcommand{\snd}{\mathrm{snd}}

%%%% Lambda Calculus
\newcommand{\dneq}{\,\, \# \,\,}
\renewcommand{\S}{\pmb{\mathrm{S}}}
\newcommand{\I}{\pmb{\mathrm{I}}}
\newcommand{\K}{\pmb{\mathrm{K}}}
\newcommand{\ch}[1]{\ulcorner #1 \urcorner}

%%%% Ordinal Lambda Calculus
\newcommand{\ordAlph}{\Sigma_{\text{Ord}}}
\newcommand{\termOrd}{\text{Term}_\text{Ord}}
\newcommand{\fl}{\mathrm{fl}}
\newcommand{\sk}{\mathrm{sk}}

%% Superscript to the left
% https://latex.org/forum/viewtopic.php?t=455
\usepackage{tensor}
\newcommand{\app}[3]{\tensor*[^{#1}]{\left(#2, #3\right)}{}}

%%%% Make optional parameter
% https://tex.stackexchange.com/questions/217757/special-behavior-if-optional-argument-is-not-passed
\usepackage{xparse}

%%%% Statistics
\NewDocumentCommand{\E}{o m}{
  \IfNoValueTF{#1}
  {\mathbb{E}\left[#2\right]}
  {\mathbb{E}^{#1}\left[ #2\right]}
}
\NewDocumentCommand{\V}{o m}{
  \IfNoValueTF{#1}
  {\mathrm{Var}\left[#2\right]}
  {\mathrm{Var}^{#1}\left[ #2\right]}
}
\RenewDocumentCommand{\P}{o o m}{
  \IfNoValueTF{#1}
  {\IfNoValueTF{#2}
    {\mathrm{P}\left(#3\right)}
    {\mathrm{P}^{#2}\left(#3\right)}}
  {\IfNoValueTF{#2}
    {\mathrm{P}_{#1}\left(#3\right)}
    {\mathrm{P}_{#1}^{#2} \left(#3\right)}}
}

%%%% Lambda Calculus
\NewDocumentCommand{\cx}{o}{
  \IfNoValueTF{#1}
  {\left[\quad\right]}
  {\left[\, #1 \,\right]}
}

%%%% Create absolute value function
% https://tex.stackexchange.com/questions/43008/absolute-value-symbols
\usepackage{mathtools}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
\makeatletter
\let\oldabs\abs
\def\abs{\@ifstar{\oldabs}{\oldabs*}}
%
\let\oldnorm\norm
\def\norm{\@ifstar{\oldnorm}{\oldnorm*}}
\makeatother

%%%%%%%% LOGIC TREES
\usepackage{prftree}

%%%%%%%% SPLIT EQUATIONS
% https://tex.stackexchange.com/questions/51682/is-it-possible-to-pagebreak-aligned-equations
\allowdisplaybreaks

%%%%%%%% FLOAT SPECIFIER
% https://www.overleaf.com/learn/latex/Errors/LaTeX_Error:_Unknown_float_option_%60H%27
\usepackage{float}

%%%%%%%% TO USE SHORT COMMANDS FOR VECTOR LINES
\usepackage{esvect}

%%%%%%%% ENUMERATE LABEL
% https://www.latex-tutorial.com/tutorials/lists/
\usepackage{enumitem}

%%%%%%%% DIFFERENT FONTS FOR MATH
\usepackage{mathrsfs}

\begin{document}

%%%%%% TITLE HEAD
\title{Expert System for Psychological Attention to High School Students}

\author{\IEEEauthorblockN{Juan Sebastián Cárdenas-Rodríguez}
  \IEEEauthorblockA{\textit{Department of Mathematical Science}\\
    \textit{Universidad EAFIT} \\
    Medellín, Colombia \\
    jscardenar@eafit.edu.co}}

\maketitle

\begin{abstract}
  In this work, a basic prototype for a Mamdani fuzzy inference system to detect
  depression, anxiety and hyperactivity in high school students can be found. It
  was shown that the expert system had some errors inherent from the rules
  defined. Lastly, some comparisons between some $T$-norms and defuzzification
  methods were realized.
\end{abstract}

\section{Introduction}
Mental health is crucially important for every human being and has become one of
the most important issues surrounding human health. According to the World
Health Organization\footnote{WHO's \href{https://bit.ly/34l2v94}{2001 report.}}
report of 2001, mental disorders can affect 25\% of the population, therefore,
suggesting the ongoing trend of people suffering from lack of mental health.

Furthermore, mental health is more important to monitor in adolescents and kids
as this group is in the process of developing their mental structure and
character. In this manner, as they continue creating their view about the world
they must be surrounded by a healthy environment that promotes healthy habits
and relationships with their surroundings.

As a result, schools and parents have an important responsibility to the
students of creating this environment and wisely handling mental health issues.
However, high schools do not always know how to handle or detect cases of mental
health issues. Additionally, technology has led to targeted harassing becoming
more popular over time, therefore, difficulting the probability of detecting
these cases.

Some of the most common and important mental health issues are anxiety,
depression, and hyperkinetic disorder. According to \textcite{schulte2016}, around
10\% to 20\% of children suffer from hyperkinetic disorder. Additionally, school
teachers just assume this disorder is a cause of undisciplined students and can
take the hyperkinetic student to a depressive state. These three mental
disorders can leave severe damage to a kid and can lead them to suicide.

Hence, it is of the utmost importance to quickly and efficiently detect students
that might be having a mental health issue to immediately start a process with
him/her. Furthermore, this detection has to be done with measurable variables
that can be easily obtained from questionnaires or school data.

Following the above, in this work an expert system constructed by using fuzzy
sets \parencite{zadeh1965} in a fuzzy inference system purposed by
\textcite{mamdani1981}.

\section{State of the Art}
Several expert systems to diagnose mental disorders for different groups of
people have been realized, to realize preventive diagnosis to a certain group.
The benefits of realizing this preventive diagnosis are much, as the case of the
mental disorder can be treated at the early stage and start treatment quickly.
Such is the case of the expert system developed by \textcite{nunes2009}.

According to Nunes, psychological disorders can incapacitate a worker from doing
their respective job. This occurs due to lack of an early diagnosis, as when the
disorder is detected in most cases the worker already shows signs of incapacity.
Nunes attempted to develop a hybrid expert system to make an early diagnosis of
psychological disorders.

Although Nunes's work does not present an expert system, it does highlight the
difficulty to construct one. When diagnosing a person, many factors need to be
considered such as biological data, interviews with the patient, symptoms, and
more. Furthermore, the relationship between these variables is hardly
quantifiable.

More successfully is the expert system created by \textcite{kim2006}. This
expert system uses information from psychologists, which are stored in a set of
rules that they use to diagnose a patient. The authors of that work suggest
that, although still a prototype, can become greatly elaborated with many more
clinical case studies. Furthermore, this prototype allows for non-experts to
detect cases on their children or students for the mental disorders that were
studied.

Lastly, \textcite{jabeen2018} created a cellphone application that used an
expert system to detect cases of depression and anxiety in college students.
This cellphone returned the level of sickness the student had of each mental
disorder and allowed them to ask for treatment. It is important to notice that
30\% to 35\% of students reported an abnormal level of mental disorder, highly
encouraging to further study these types of expert systems to detect these
cases.

In conclusion, although some good attempts have been realized surrounding
psychological diagnosis using expert systems, this problem is far from solved.
Each expert system has its own flaws and, therefore, it is important to continue
to build expert systems for psychological diagnosis to further improve this area
and improve people's lifestyle overall.

\section{Model}
As stated in the introduction, a Mamdani fuzzy inference system will be purposed
to solve the suggested problem. Hence, in this section the input variables of
the system, the output variables and the rules of the system will be explained.

\subsection{Input Variables}
In the first place, the first variable is the \textit{level of attention} that a
student has in class. The attention of a student can be a good indicator of
their mental health, as students with mental disorders tend to have more
difficulties focusing in class. Furthermore, specially hyperkinetic disorders
present lower attention levels than people with no disorder.

There have been several different investigations surrounding how to measure
engagement or attention, such as \textcite{wang2014}. For simplicity, this work
will measure the level of attention in the range $[0, 5]$. It is acknowledged
that this range is not strongly based on any literature but as this work focus
is the expert system, it is considered to be fitting.

There will be three different categorical values for this input low, average and
high. The low value is defined by a $\mathrm{sigmoid}$ function with parameters
$a=-5$, $c=1.7$ and $\mathrm{limit} = 0$. The average value is defined by a
$\mathrm{gauss}$ function with parameters $\mathrm{center}=2.5$ and
$\sigma = 0.7$. Lastly, the high value is defined by a $\mathrm{sigmoid}$
function with parameters $a = 5$, $c=3.3$ and $\mathrm{limit} = 5$. Each
membership function can be found in Figure~\ref{fig:att_mf}.

\begin{figure}[t]
  \centering
  \includegraphics[scale=.3]{figs/att.pdf}
  \caption{Membership functions for the level of attention in class.}
  \label{fig:att_mf}
\end{figure}

In the second place, the \textit{academic performance} of the student will be
used as input. This input was selected as someone with low grades can lead the
student to feel depressed and have anxiety. Furthermore, excellent academic
performance can also induce anxiety on the student if pressured by parents.

The academic performance will be measured as the average of the grade of the
student. For this work, academic performance will be measured between $[0, 5]$
but it can be adjusted depending on the grading system.

Similarly to the first input, the same three categorical values will be
selected. The low value is defined by a $\mathrm{bell}$ function with parameters
$a=1.5$, $b = 4$ and $c=0$. The average value is defined by a $\mathrm{gauss}$
function with parameters $\mathrm{center}=3$ and $\sigma = 0.7$. Lastly, the
high value is defined by a $\mathrm{bell}$ function with parameters $a = 1$,
$b=4$ and $c=5$. Each membership function can be found in
Figure~\ref{fig:ap_mf}.

\begin{figure}[t]
  \centering
  \includegraphics[scale=.3]{figs/ap.pdf}
  \caption{Membership functions for the academic performance.}
  \label{fig:ap_mf}
\end{figure}

Lastly, the \textit{emotional socialization} will be considered. As expressed by
\textcite{horner2013}, emotional socialization is one of the key features that
can determine the student's psychological health. Positively reaffirmed students
with their negative emotions can often have the best deal with feelings such as
anger, sadness, and more. Furthermore, this variable can be measured by
questionnaires to parents that would allow detecting a case easily.

The emotional socialization will be measured between $[-252, 252]$. This range
was selected based on the test done by \textcite{fabes2001} to measure emotional
socialization, as it measures positive or punitive reaffirmation of students
with this scale.

There same categorical values are chosen. The low value is defined by a
$\mathrm{sigmoid}$ function with parameters $a=-0.05$, $c=-126$ and
$\mathrm{limit} = -252$. The average value is defined by a $\mathrm{gauss}$
function with parameters $\mathrm{center}=0$ and $\sigma = 70$. Lastly, the high
value is defined by a $\mathrm{sigmoid}$ function with parameters $a = 0.05$,
$c=126$ and $\mathrm{limit} = 252$. Each membership function can be found in
Figure~\ref{fig:es_mf}.

\begin{figure}[t]
  \centering
  \includegraphics[scale=.3]{figs/es.pdf}
  \caption{Membership functions for the emotional socialization.}
  \label{fig:es_mf}
\end{figure}

\subsection{Output Variables}
The selected outputs are the level of \textit{depression}, \textit{anxiety} and
\textit{hyperactivity}. These three mental disorders, as explained in the
introduction, have an important role in the mental disorders presented by
students.

Each output was selected to have the same categorical values and membership
functions, to preserve simplicity. Furthermore, each output will be measured
between $[0, 100]$ to resemble a percentage of the suffering from each disease.

The two categorical values for the three outputs are low and high. The low
membership function is given by a $\mathrm{sigmoid}$ with parameters $a=-0.15$,
$c=50$ and $\mathrm{limit} = 0$. The high membership function is given by a
$\mathrm{sigmoid}$ with parameters $a=0.15$, $c=50$ and $\mathrm{limit} = 100$.
Each membership function can be found in Figure~\ref{fig:out_mf}.

\begin{figure}[t]
  \centering
  \includegraphics[scale=.3]{figs/outputs.pdf}
  \caption{Membership functions for outputs.}
  \label{fig:out_mf}
\end{figure}

\subsection{Rules}
For each rule, the level of attention will be referred as ATT, the academic
performance will be referred as AP, the emotional socialization will be referred
as ES and each of the output will be mentioned as their initial.

The rules selected are
\begin{enumerate}
  \item If the ATT is low and AP is low and ES is low then D is high and A
    is high and H is high.

  \item If the ATT is low and AP is low and ES is medium then D is high and A is
    low and H is high.

  \item If the ATT is low and AP is low and ES is high then D is low and A is
    low and H is high.

  \item If the ATT is low and the AP is medium and ES is low then D is high and
    A is low and H is high.

  \item If the ATT is low and the AP is medium and ES is medium then D is low
    and A is low and H is high.

  \item If the ATT is low and the AP is high and ES is low then D is high and A
    is low and H is high.

  \item If the ATT is low and AP is not high and ES is low then D is high and A
    is high and H is low.

  \item If the ATT is medium and AP is low and ES is low then D is high and A is
    low and H is low.

  \item If the ATT is high and the AP is low and ES is medium then D is low
    and A is low and H is high.

  \item If the ATT is high and the AP is low and ES is low then D is high and A
    is low and H is low.

  \item If the ATT is high and the AP is high and the ES is not low then D is
    low and A is high and H is low.

  \item If the ATT is high and the AP is high and the ES is high then D is low
    and A is low and H is low.

  \item If the ATT is high and the AP is not low and the ES is high then D is
    low and A is low and H is low.
\end{enumerate}

Although not every possible rule was considered, the selected set is enough to
show a prototype of this type of systems.

\section{Results}
The fuzzy inference system was implemented in the programming language
\texttt{Julia} and it was tested with the version 1.4.2. The codes can be found
annexed.

\subsection{Experiments Defuzzification}
For this set of experiments, different defuzzification methods were tested to
see the difference between them. Furthermore, for each one, the value for the
emotional socialization was fixed at -200. Additionally, this was only observed
for the depression output to make a fair comparison between them. Lastly, for
each figure, the $T$-norm is $\min$.

The first result can be seen in Figure \ref{fig:low_es}. This experiment was
observing the effect of using the weighted average defuzzification function. It
is noticed that this method, qualitatively speaking, it's the second softest
result. This is a really good property, especially comparing the computation
time that it takes to run.
\begin{figure}[t]
  \centering
  \includegraphics[scale=.3]{figs/low_es}
  \caption{Hyperplane for emotional socialization of -200 with weighted
    average.}
  \label{fig:low_es}
\end{figure}

This figure explains nicely how the variables relate to each other and confirm
that the rules partially describe correctly the desired behavior.

In the first place, it can be seen that the lowest valley for the level of
depression is seen when the attention level and academic performance is the
highest. This basic behavior has sense, as the student is having a high reward
for his attention leading him to not feel depressed.

In the second place, when the attention or academic performance is the lowest it
tends to have the biggest depression which presents a small incongruency. This
is because it is not obvious that a student with a small attention rate but a
good performance would be depressed as it's a low-risk high reward attitude. In
this manner, it is noticed that the defined set of rules have flaws.

Lastly, one of the maximum values is seen when the student has the biggest
attention but the lowest performance. This makes sense, as a student that is
constantly studying but does not perform well will feel frustration and
depression.

In Figures \ref{fig:low_es_mom}, \ref{fig:low_es_cog} the results for two more
defuzzification methods can be found. With the experiments made it is seen that
the weighted average defuzzification method was the best result at least for the
selected output.

\begin{figure}[t]
  \centering
  \includegraphics[scale=.3]{figs/low_es_mom}
  \caption{Hyperplane for emotional socialization of -200 with mean of maximum.}
  \label{fig:low_es_mom}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[scale=.3]{figs/low_es_cog}
  \caption{Hyperplane for emotional socialization of -200 with center of area.}
  \label{fig:low_es_cog}
\end{figure}

For the mean of maximum defuzzification method, it is seen that the output was
not as soft as the one obtained by weighted average. This is not a desired
behavior and, as especially in human behavior, soft curves are preferred.
However, the behavior is pretty much identical.

Lastly, for the center of area defuzzification method a softer curve was
obtained with a similar behavior. The downgrade for this method was the
computation time as, although not measured, it was significantly slower. For
further work, it is important to notice how much is the difference between those
methods to clearly decide the best option.

\subsection{Experiment T-Norm}
For this experiments, the academic performance was fixed in 5 and the weighted
average defuzzification method was used. Finally, to observe the system with
more detailed the anxiety output was selected.

\begin{figure}[t]
  \centering
  \includegraphics[scale=.3]{figs/high_ap}
  \caption{Hyperplane for academic performance of 5 using the minimum.}
  \label{fig:high_ap}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[scale=.3]{figs/high_ap-a-prod}
  \caption{Hyperplane for academic performance of 5 using algebraic product.}
  \label{fig:high_ap_a_prod}
\end{figure}

In Figures \ref{fig:high_ap}, \ref{fig:high_ap_a_prod} the experiments for this
section with different $T$-norms can be found. It is important to remark that it
is seen that the hyperplanes did change slightly their form, even if the fuzzy
inference system stayed the same. This highlights the importance of selection the
norm and how each one affects the outputs.

It is seen that the algebraic product does have a more softer output than the
minimum. Furthermore, although the minimum norm is bigger than the algebraic
product, that inequality is not preserved through the output as seen in
$(0, 200)$ point. This is important to notice as selecting a bigger norm does
not imply a bigger output.

Lastly, it is stated that the surface does not reflect the desire behavior. In
first glance, a student with small attention span and high socialization should
not have that much anxiety. Therefore, as shown in the previous experiments, the
fuzzy inference system purposed has some incoherent behavior and it is not ready
to take expert decisions.

\section{Conclusion}
In conclusion, a basic prototype for a Mamdani fuzzy inference system was
constructed. This fuzzy inference system presents some incoherent behavior but
has partially some good outputs. This reinforces the idea that tackling this
problem from this angle can be done but it does has some complexities hard to
represent.

Furthermore, a comparison between $T$-norms and defuzzification methods was
realized, which showed some of the incongruities. Additionally, it allowed to
compare between the outputs in which the best defuzzification method used was
the weighted average as it was the fastest one with a good semi-soft curvature.

\printbibliography
\end{document}

### 2020-12-09 unsupervised-juanscr/second-work/article/article.tex
[ UJ ] Added unsupervised-juanscr.

\documentclass[conference]{IEEEtran}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{multirow}

%%%%%%%% SUB-FIGURE PACKAGE
\usepackage{subcaption}

%%%%%%%% HYPERREF PACKAGE
\usepackage{hyperref}
\hypersetup{linkcolor=blue}
\hypersetup{citecolor=blue}
\hypersetup{urlcolor=blue}
\hypersetup{colorlinks=true}

%%%%%%%% DEFINITION AND THEOREM DEFINITIONS
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\theoremstyle{remark}
\newtheorem{remark}{Remark}

\theoremstyle{remark}
\newtheorem{question}{Question}

\newtheorem{theorem}{Theorem}[section]

%%%%%%%% MULTI-COLUMNS PACKAGE
\usepackage{multicol}

%%%%%%%% BIB-LATEX STUFF
\usepackage[style=ieee,
            bibstyle=ieee,
            citestyle=ieee,
            hyperref=true,
            backend=biber]{biblatex}
\addbibresource{ref.bib} %Put relative path to ref

%%%%%%%% PERSONAL COMMANDS
\usepackage{amssymb}

%%%% Important sets
\renewcommand{\O}{\mathbb{O}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{{\mathbb{Z}}}
\newcommand{\Q}{{\mathbb{Q}}}
\newcommand{\R}{{\mathbb{R}}}

%%%% Usual operations
\newcommand{\pow}[2]{#1^{#2}}
\newcommand{\expp}[1]{e^{#1}}
\newcommand{\fst}{\mathrm{fst}}
\newcommand{\snd}{\mathrm{snd}}

%%%% Lambda Calculus
\newcommand{\dneq}{\,\, \# \,\,}
\renewcommand{\S}{\pmb{\mathrm{S}}}
\newcommand{\I}{\pmb{\mathrm{I}}}
\newcommand{\K}{\pmb{\mathrm{K}}}
\newcommand{\ch}[1]{\ulcorner #1 \urcorner}

%%%% Ordinal Lambda Calculus
\newcommand{\ordAlph}{\Sigma_{\text{Ord}}}
\newcommand{\termOrd}{\text{Term}_\text{Ord}}
\newcommand{\fl}{\mathrm{fl}}
\newcommand{\sk}{\mathrm{sk}}

%% Superscript to the left
% https://latex.org/forum/viewtopic.php?t=455
\usepackage{tensor}
\newcommand{\app}[3]{\tensor*[^{#1}]{\left(#2, #3\right)}{}}

%%%% Make optional parameter
% https://tex.stackexchange.com/questions/217757/special-behavior-if-optional-argument-is-not-passed
\usepackage{xparse}

%%%% Statistics
\NewDocumentCommand{\E}{o m}{
  \IfNoValueTF{#1}
  {\mathbb{E}\left[#2\right]}
  {\mathbb{E}^{#1}\left[ #2\right]}
}
\NewDocumentCommand{\V}{o m}{
  \IfNoValueTF{#1}
  {\mathrm{Var}\left[#2\right]}
  {\mathrm{Var}^{#1}\left[ #2\right]}
}
\RenewDocumentCommand{\P}{o o m}{
  \IfNoValueTF{#1}
  {\IfNoValueTF{#2}
    {\mathrm{P}\left(#3\right)}
    {\mathrm{P}^{#2}\left(#3\right)}}
  {\IfNoValueTF{#2}
    {\mathrm{P}_{#1}\left(#3\right)}
    {\mathrm{P}_{#1}^{#2} \left(#3\right)}}
}

%%%% Lambda Calculus
\NewDocumentCommand{\cx}{o}{
  \IfNoValueTF{#1}
  {\left[\quad\right]}
  {\left[\, #1 \,\right]}
}

%%%% Create absolute value function
% https://tex.stackexchange.com/questions/43008/absolute-value-symbols
\usepackage{mathtools}
\DeclarePairedDelimiter\abs{\lvert}{\rvert}%
\DeclarePairedDelimiter\norm{\lVert}{\rVert}%
\makeatletter
\let\oldabs\abs
\def\abs{\@ifstar{\oldabs}{\oldabs*}}
%
\let\oldnorm\norm
\def\norm{\@ifstar{\oldnorm}{\oldnorm*}}
\makeatother

%%%%%%%% LOGIC TREES
\usepackage{prftree}

%%%%%%%% SPLIT EQUATIONS
% https://tex.stackexchange.com/questions/51682/is-it-possible-to-pagebreak-aligned-equations
\allowdisplaybreaks

%%%%%%%% FLOAT SPECIFIER
% https://www.overleaf.com/learn/latex/Errors/LaTeX_Error:_Unknown_float_option_%60H%27
\usepackage{float}

%%%%%%%% TO USE SHORT COMMANDS FOR VECTOR LINES
\usepackage{esvect}

%%%%%%%% ENUMERATE LABEL
% https://www.latex-tutorial.com/tutorials/lists/
\usepackage{enumitem}

%%%%%%%% DIFFERENT FONTS FOR MATH
\usepackage{mathrsfs}

\begin{document}

%%%%%% TITLE HEAD
\title{Unsupervised Learning Work}

\author{\IEEEauthorblockN{Juan Sebastián Cárdenas-Rodríguez}
  \IEEEauthorblockA{\textit{Department of Mathematical Science}\\
    \textit{Universidad EAFIT} \\
    Medellín, Colombia \\
    jscardenar@eafit.edu.co}}

\maketitle

\begin{abstract}
  In this work, an analysis of some unsupervised learning methods is tested in
  order to fully understand the inner work of the algorithms. Furthermore,
  optimal number of clusters and classification of the iris data set and a
  personal recollected data set is done. Finally, the source code for this work
  is given with all the algorithms and experiments.
\end{abstract}

\section{Introduction}
Mental health is crucially important for every human being and has become one of
the most important issues surrounding human health. According to the World
Health Organization\footnote{WHO's \href{https://bit.ly/34l2v94}{2001 report.}}
report of 2001, mental disorders can affect 25\% of the population, therefore,
suggesting the ongoing trend of people suffering from lack of mental health.

Furthermore, mental health is more important to monitor in adolescents and kids
as this group is in the process of developing their mental structure and
character. In this manner, as they continue creating their view about the world
they must be surrounded by a healthy environment that promotes healthy habits
and relationships with their surroundings.

As a result, schools and parents have an important responsibility to the
students of creating this environment and wisely handling mental health issues.
However, high schools do not always know how to handle or detect cases of mental
health issues. Additionally, technology has led to targeted harassing becoming
more popular over time, therefore, difficulting the probability of detecting
these cases.

Some of the most common and important mental health issues are anxiety,
depression, and hyperkinetic disorder. According to \textcite{schulte2016}, around
10\% to 20\% of children suffer from hyperkinetic disorder. Additionally, school
teachers just assume this disorder is a cause of undisciplined students and can
take the hyperkinetic student to a depressive state. These three mental
disorders can leave severe damage to a kid and can lead them to suicide.

Hence, it is of the utmost importance to quickly and efficiently detect students
that might be having a mental health issue to immediately start a process with
him/her. Furthermore, this detection has to be done with measurable variables
that can be easily obtained from questionnaires or school data.

Therefore, in this work an evaluation of the Psychological Attention Detection
(PAD) data set recollected with the help of the teacher will be classified and
evaluated. Furthermore, a testing data set will be used to first verify the
procedure done.

\section{Method} \label{sec:method}

There will be used 5 different clustering algorithms, for which 2 of them are
exploratory and 3 of them have a fixed number of clusters and find the best
classification given that number.

For the exploratory algorithms, the mountain clustering algorithm created by
\cite{yager1994} and the substractive clustering algorithm done by
\cite{chiu1994} will be used. It is acknowledge that both of this algorithms are
equivalent and only change the initial candidates for the prototypes.

On the other hand, for the fixed number of clusters the renown K-means algorithm
will be used. Furthermore, the Fuzzy C-means algorithm and the unnormalized
Laplacian spectral clustering presented by \cite{von2007} will be used. This are
mainly used in the real data set to verify how much does the clustering improve
when found the number of clusters.

\subsection{Clustering Validation}

For the cluster validation, two different inter-cluster indexes will be used. In
the first place, the \cite{calinski1974} index will be used. This a commonly
used inter-cluster index. Let $n$ be the number of data points, $K$, the number
of clusters, $C_{i}$ a set that contains the point of each cluster $i$,
$n_{i} = \abs{C_{i}}$ and $c_{i}$ the prototype for each cluster. The equation
for this index is given by:

\begin{equation*}
  \mathrm{CH} = \frac{n - K}{K - 1} \cdot
  \frac{\displaystyle\sum_{i=1}^{K} n_i \norm{c_i - \mu}^2}
  {\displaystyle\sum_{i=1}^K \sum_{x \in C_i} \norm{x - c_i}^2}
\end{equation*}

The idea for this measurement is to maximize this index in order to find a
better classification.

On the second hand, the inter-index done by \cite{davies1979} will be used. The
equation, using the same notation as the one above, for this index is given by:

\begin{align*}
  \mathrm{DB}
  &= \frac{1}{K} \sum_{i=1}^{K} \max_{j\neq i}\left\{\frac{\mu_{i} + \mu_{j}}
    {\norm{c_{i} - c_{j}}}\right\} \text{ where } \\
  \mu_{i} &= \frac{1}{n_{i}} \sum_{x \in C_{i}} \norm{x - c_{i}}
\end{align*}

Lastly, for the testing data set an extra-cluster index will be measured in
order to see if the classification is valid. Although this construction was done
empirically by the author, the idea to calculate the badly classified data
points. For this, one would classify good classification if a point belongs to a
cluster where the majority of the points have the same tag. Therefore, the
extra-cluster index is given by the number of badly classified points. It is
clearly seen that the idea is to minimize this value to obtain a better
classification.

The parameters chosen for each of the algorithms executed, are explicitly shown
on the source code as this article will focus mainly on the data analysis. The
source code was tested with \texttt{julia} 1.5.1 and it is given in an
\texttt{IJulia} notebook.

\section{Testing Data Set}

This section will cover the learnings and experiments done with the iris data
set in order to then apply the same principles in the real data set and explain
my reasoning in a smaller scale. Furthermore, in this section the higher
dimensions will not be covered as it is not essential for this testing data set.

In the first place, an exploration on the parameters for the substractive
clustering was realized in order to minimize the DH index and therefore find a
correct value for the parameters to find an optimal number of clusters. In
Figures \ref{fig:exp3d}, \ref{fig:exp3dman} and \ref{fig:exp3dmah} each of the
explorations with different norms can be found.

\begin{figure}[t]
  \centering
  \includegraphics[scale=.35]{figs/iris/exploring-3d}
  \caption{Parameters $r_{a}$ and $r_{b}$ compared to DB index, with euclidean
    norm.}
  \label{fig:exp3d}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[scale=.35]{figs/iris/exploring-3d-man}
  \caption{parameters $r_{a}$ and $r_{b}$ compared to db index, with manhattan
    norm.}
  \label{fig:exp3dman}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[scale=.35]{figs/iris/exploring-3d-mah}
  \caption{parameters $r_{a}$ and $r_{b}$ compared to db index, with mahalanobis
    norm.}
  \label{fig:exp3dmah}
\end{figure}

With this set of tests, it is clear that lower values of the parameter $r_{b}$
allow for a better classification as the DH index is lower. On the other hand,
in the author's work there is not a clear option to select from each of the
norms as they are almost the same. In this manner, a clear selection can not be
realized. The embedded iris data set will be used to further explain how to
choose the norm and each of the approach realized.

\subsection{Embedded Iris Data Set}

The iris data set was embedded to a 2D data set to simplify analysis and
visualization. It is important to remark that each time the embedding is
realized the data set is changed. Therefore, the results for this section will
be using one of the results obtained. The embedded data set can be seen in
Figure \ref{fig:embdata}.

\begin{figure}[t]
  \centering
  \includegraphics[scale=.35]{figs/iris/embedded-data-set}
  \caption{Embedded iris data set.}
  \label{fig:embdata}
\end{figure}

In the first place, the substractive clustering method was evaluated for
different values of parameters in order to understand how varying the parameters
affect the DH index. This would allow to have an understanding on what range of
parameters should be evaluated to test for an optimal number of clusters. In
Figure \ref{fig:expemb3d} the result of the DH index for the classification
given by the substractive clustering method for parameters $r_{a}$ and $r_{b}$
are shown using the euclidean norm.

\begin{figure}[t]
  \centering
  \includegraphics[scale=.35]{figs/iris/exploring-3d-emb}
  \caption{Parameters $r_{a}$ and $r_{b}$ compared to DB index, with euclidean
    norm.}
  \label{fig:expemb3d}
\end{figure}

In this manner, it is seen that for lower values of the parameter a better
result for the DH index is obtained. Furthermore, to confirm that the euclidean
norm did not biased the results also the manhattan and mahalanobis norm were
tested. In Figures \ref{fig:expemb3dman} and \ref{fig:expemb3dmah} the results
of each norm can be found.

\begin{figure}[t]
  \centering
  \includegraphics[scale=.35]{figs/iris/exploring-3d-emb-man}
  \caption{Parameters $r_{a}$ and $r_{b}$ compared to db index, with manhattan
    norm for embedded iris data set.}
  \label{fig:expemb3dman}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[scale=.35]{figs/iris/exploring-3d-emb-mah}
  \caption{Parameters $r_{a}$ and $r_{b}$ compared to db index, with mahalanobis
    norm for embedded iris data set.}
  \label{fig:expemb3dmah}
\end{figure}

The manhattan norm did confirmed that lower values of the parameter improve the
intra-cluster index. On the contrary it is seen that the for bigger values the
DH index suddenly converges to 0. This occurs because the method did not select
a second cluster, hence proving useless in clustering the data.

Using the mahalanobis norm much interpretation could not be obtained as there is
not an evident relationship between the parameters and the DH index. In this
manner, the euclidean norm will be used for the rest of this exercise as it
presents a clear trend and it is easy to run.

Accordingly to the analysis made, to test the mountain clustering method the
parameter $\sigma$ can be fixed in the interval $(0, 0.5)$ to obtain an optimal
result. Additionally, for simplicity, the other parameter was fixed at
$\beta = 1.5\sigma$. Therefore, in Figures \ref{fig:expembch},
\ref{fig:expembdb} and \ref{fig:expembn} the CH index, DB index and number of
clusters for different values of $\sigma$ can be found respectively.

\begin{figure}[t]
  \centering
  \includegraphics[scale=.35]{figs/iris/exploring-2d-emb-ch}
  \caption{CH index for embedded iris data set.}
  \label{fig:expembch}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[scale=.35]{figs/iris/exploring-2d-emb-db}
  \caption{DB index for embedded iris data set.}
  \label{fig:expembdb}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[scale=.35]{figs/iris/exploring-2d-emb-n}
  \caption{Number of clusters for embedded iris data set.}
  \label{fig:expembn}
\end{figure}

The goal, following the ideas of Section \ref{sec:method}, is to maximize the CH
index and minimize the DB index. In this manner, it is concluded with this
exploratory analysis that the best number of clusters would be to use 3 as it
satisfies the criterion explained. Furthermore, it is seen that the best
prototypes obtained by this method was given by the initial parameter tested
$\sigma=0.2$.

Furthermore, this is confirmed also by an extra cluster analysis, as the iris
data set has three different labels i.e. the data is clustered into 3 groups.
Therefore, it is important to notice that an exploratory analysis of the
clusters allows to find a good set of groups even if the ``real data'' is not
known.

Now with the fixed selected number of clusters, the three fixed clustering
methods can be used to obtain better clustering and prototypes. The results of
each of the three clustering methods can be seen in Figures \ref{fig:embk},
\ref{fig:embfc} and \ref{fig:embsc}.

\begin{figure}[t]
  \centering
  \includegraphics[scale=.35]{figs/iris/emb-k-means}
  \caption{K-means clustering for embedded iris data set.}
  \label{fig:embk}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[scale=.35]{figs/iris/emb-fc-means}
  \caption{Fuzzy c-means clustering for embedded iris data set.}
  \label{fig:embfc}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[scale=.35]{figs/iris/emb-spectral-clustering}
  \caption{Spectral clustering for embedded iris data set.}
  \label{fig:embsc}
\end{figure}

In the first place, it is noticed that the K-means algorithm successfully
partitioned the data as one would instinctively cluster it. The same can be said
surrounding the spectral clustering method. On the other hand, the fuzzy c-means
converged to some centers that do not seem according to the data set given.
Although some values for $m$ where tested and the same result was obtained, the
value for this parameter could be the cause of this convergence.

In the second place, to understand why would this algorithms be necessary
instead of using only the exploratory algorithms comparison between the
performance of the mountain clustering and the other algorithms is showed in
Table \ref{tab:compemb}.

\begin{table}
  \begin{tabular}{ccccc}
    \hline
    & Mountain & K-Means & Fuzzy C-Means & Spectral \\
    Ext. Index & 5       & 2         & 2            & 2                   \\
    DB Index   & 20.58   & 12.17     & 130.93       & N/A                 \\
    CH Index   & 5180.66 & 108011.97 & 2603.10      & N/A \\ \hline
  \end{tabular}
  \caption{Comparison between each of the methods.}
  \label{tab:compemb}
\end{table}

Without taking into account the fuzzy c-means algorithm, the fixed cluster
algorithms improved the intra-cluster and extra-cluster values in comparison
with the exploratory algorithm. This occurs because fixed cluster algorithms,
such as K-means, improve on an objective function instead of trying to explore
the space for a good clustering number. Hence, this method help the ``goodness''
of the clusters.

In conclusion, the embedded data set allowed to visualize the behavior of the
data without breaking their structure drastically. Furthermore, the clustering
algorithms where able to detect the optimal number of clusters and, almost,
completely characterize the data. Lastly, it allows for a quicker run of this
algorithms as it reduces the dimensions of the original data set.

\section{PAD Data Set}
In the first place, a preliminary analysis will be done with the embedded data
set to extract some information about the structure of the original data set as
the data set cannot be visualized. Furthermore, this analysis allows to have a
basic visualization on what it would be expected to have on higher dimensions.

\subsection{Embedded PAD Data Set}

In Figure \ref{fig:embds} the embedded data set can be seen. At first glance, it
is seen, intuitively, that this reduced data set posses two different marked
groups. In this manner, an exploratory analysis is deemed to not be necessary
for this special case. Therefore, just by visualizing, the fixed cluster
algorithms will be tested with 2 clusters. Furthermore, the norm was selected to
be the euclidean norm as the clusters are clearly circular.

\begin{figure}[t]
  \centering
  \includegraphics[scale=.3]{figs/real/embedded}
  \caption{Embedded data set.}
  \label{fig:embds}
\end{figure}

Consequently, in Figures \ref{fig:embdsk}, \ref{fig:embdsfc} and
\ref{fig:embdssc} the results for the chosen three fixed cluster algorithms can
be found. As it was expected, the results for each of the algorithms is perfect
as the separation between the groups is pretty significant. Each of the
algorithms converge quickly, confirming this statement.

On the other hand, as the separation is that marked, it is hard to actually find
a significant difference between the classification done by each of the methods.
Furthermore, as is not possible to check for external indexes this grouping it's
hard to verify.

\begin{figure}[t]
  \centering
  \includegraphics[scale=.35]{figs/real/emb-k-means}
  \caption{K-means clustering for embedded PAD data set.}
  \label{fig:embdsk}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[scale=.35]{figs/real/emb-fc-means}
  \caption{Fuzzy c-means clustering for embedded PAD data set.}
  \label{fig:embdsfc}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[scale=.35]{figs/real/emb-spectral-clustering}
  \caption{Spectral clustering for embedded PAD data set.}
  \label{fig:embdssc}
\end{figure}

On the other hand, the main goal for obtaining this data was to be able to
diagnose if a student should be receive psychological attention to bring them
early help before their situation goes out of control. In this manner, it is
curious that the embedded data separated so clearly between two groups on the
opposite vertex of the rectangle that encloses the data. It is important to
further analyze if this separation fulfills the desired role.

In conclusion, the embedding of the data presented a clear separation between
two groups that where easily separated. Furthermore, as the embedding preserves
topology for the data, the euclidean norm will be the norm used for the next
experiments although the number of clusters will still be tested with
exploration clustering algorithms.

\subsection{PAD Data Set}

Following the ideas explored in the testing data set, a table for the changes of
the DH index by changing the parameter of the substractive clustering algorithm
was realized in order to understand which set of parameters should be essential
to obtain a good number of clusters. For this experiment, the value for $r_{a}$
was changed while $r_{b}$ was fixed at $1.5r_{a}$. In this manner, in table
\ref{tab:expds} the results for this exploration can be found.

\begin{table}
  \centering
  \begin{tabular}{cccc}
    \hline
    $r_a$ & $n_i$ & DB    & CH     \\
    0.2   & 87    & 1.10  & 36.35  \\
    0.3   & 30    & 4.79  & 42.23  \\
    0.4   & 11    & 15.97 & 55.40  \\
    0.5   & 5     & 31.21 & 85.90  \\
    0.7   & 3     & 30.88 & 146.97 \\
    0.8   & 2     & 35.86 & 232.13 \\
    1.5   & 2     & 28.67 & 150.46 \\ \hline
  \end{tabular}
  \caption{Properties of clusters for different values of $r_{a}$}
  \label{tab:expds}
\end{table}

In the table, the values that are jumped with a bigger difference than 0.1 is
that it stayed constant for the evaluation. In this manner, it is seen that
there was an ``optimal'' found at $r_{a}=0.8$ as seen in how the CH index
changes. Furthermore, as it stays constant for a bit it makes sense that it
would actually be in a valley until changing again. Lastly, this value coincides
with the one obtained with the embedded data.

In this manner, at this moment the embedded data takes meaning in the manner
that, although it extremely simplified the data set, it allows to extract
characteristics that still may preserve in higher dimensions. Furthermore, this
is also verified by seen the obtained value for the inter cluster.

Analogously, let's find the values for the respective indexes when the fixed
clustering method is used. Furthermore, let's test this values for both 2 and 3
clusters in order to fully confirm the number of groups. In Table \ref{tab:clds}
the results for each of the methods for different number of clusters can be
found.

\begin{table}
  \centering
  \begin{tabular}{cccc}
    \hline
    \multicolumn{1}{l}{$n_i$} & Method   & DB     & CH     \\ \hline
    \multirow{2}{*}{2}        & K-means  & 42.00  & 174.55 \\
                              & FC-Means & 50.95  & 118.20 \\ \hline
    \multirow{2}{*}{3}        & K-means  & 36.13  & 131.14 \\
                              & FC-Means & 148.29 & 3.26   \\ \hline
  \end{tabular}
  \caption{Result for each of the clustering algorithms.}
\label{tab:clds}
\end{table}

In this manner, it is clearly seen that the optimal number of classifications
done is 2 as, specially, fuzzy c-means do not have a good behavior when trying
to separate the group onto three groups. Therefore, the obtained result for the
embedded data still continue to be valid in higher dimensions.

On the other hand, the spectral clustering can not be thoroughly tested as the
indexes for testing clusters need a center and spectral clustering does classify
by graph connections. Therefore, this method for this and the following
experiment will not be used.

In conclusion, as obtained with the embedded data, the optimal number of
clusters to classify the PAD data set is 2. This affirms how embedding data can
be useful to get preliminary information from the data, with an easy
visualization in processable information. Lastly, the different fixed clustering
methods help to decide the optimum value by evaluating the different
inter-cluster indexes.

\subsection{Higher Dimension PAD Data Set}

To increase the dimension of the PAD data set, two main characteristics were
extracted from the original data. In the first place, the moving average for
each of the data is calculated. Lastly, the discrete Fourier transform was
calculated for each of the data and the absolute value of each transform was
extracted to not use complex values. Hence, for each of this characteristics new
6 columns are generated hence tripling the dimensions of the original data set.

Following the ideas in the previous section, in Table \ref{tab:exphds} the
results of the indexes for different values of $r_{a}$ are shown. It is
important to remark that the mountain clustering algorithm is not used in this
section to avoid the grid creation that, usually is really computationally
heavy; furthermore, the substractive and mountain algorithm are basically the
same but with different candidates.

\begin{table}
  \centering
  \begin{tabular}{cccc}
    \hline
    $r_a$ & $n_i$ & DB    & CH    \\
    0.3   & 112   & 0.37  & 7.76  \\
    0.4   & 84    & 2.27  & 8.28  \\
    0.5   & 40    & 6.54  & 11.35 \\
    0.6   & 14    & 16.22 & 19.86 \\
    0.7   & 7     & 35.39 & 29.71 \\
    0.8   & 4     & 42.05 & 48.70 \\
    0.9   & 3     & 45.09 & 64.94 \\
    1.3   & 2     & 61.75 & 93.15 \\
    1.5   & 2     & 70.02 & 74.51 \\ \hline
  \end{tabular}
  \caption{Properties of clusters for different values of $r_{a}$}
  \label{tab:exphds}
\end{table}

Analogously, it is seen that a similar behavior than the normal data set is
found. As $r_{a}$ starts changing, in each iteration there is an improvement in
one of the indexes, therefore not giving an optimal solution. Finally, in
$r_{a}=1.3$ an optimal value as changing the parameter even further degenerates
both indexes without improving. In this manner, as expected, the number of
clusters given are still 2.

In conclusion, the higher data set allowed to extensively confirm the already
established hypothesis. In this manner, these three data spaces proven give us a
full view of the data set and fully inform us about it's behavior and
classification.

\section{Conclusion}

In conclusion, in the iris data set and the PAD data set it was shown the
usefulness of the clustering algorithms to correctly explain a data set.
Furthermore, it was seen that using different dimensions for the same data set
helps to grasp and confirm information of the data set, to find discrepancies
and to evaluate the structure of the data.

\printbibliography
\end{document}

### 2021-01-17 supervised/exam/juanscr/ActFunctions.jl
[ supervised ] added @juanscr exam.

@@ -1,0 +1,79 @@
+# Continuous function with first derivatives type
+abstract type C1Function end
+
+# ========== Activation Functions ========== #
+# Sigmoid Activation Function
+mutable struct Sigmoid<:C1Function
+    eval::Function
+    eval_diff::Function
+
+    function Sigmoid()
+        this = new()
+        this.eval = function eval(x)
+            return 1 / (1 + exp(-x))
+        end
+
+        this.eval_diff = function eval_diff(x)
+            return eval(x) * (1 - eval(x))
+        end
+
+        return this
+    end
+end
+
+# Hyperbolic tangent
+mutable struct Tanh<:C1Function
+    eval::Function
+    eval_diff::Function
+
+    function Tanh()
+        this = new()
+        this.eval = function eval(x)
+            return tanh(x)
+        end
+
+        this.eval_diff = function eval_diff(x)
+            return 1 - eval(x) ^ 2
+        end
+
+        return this
+    end
+end
+
+# Linear
+mutable struct Linear<:C1Function
+    eval::Function
+    eval_diff::Function
+
+    function Linear()
+        this = new()
+        this.eval = function eval(x)
+            return x
+        end
+
+        this.eval_diff = function eval_diff(x)
+            return 1
+        end
+
+        return this
+    end
+end
+
+# ReLu
+mutable struct ReLu<:C1Function
+    eval::Function
+    eval_diff::Function
+
+    function ReLu()
+        this = new()
+        this.eval = function eval(x)
+            return maximum([x, 0])
+        end
+
+        this.eval_diff = function eval_diff(x)
+            return x < 0 ? 0 : 1
+        end
+
+        return this
+    end
+end

### 2021-01-17 supervised/exam/juanscr/LogicGates.jl

@@ -1,0 +1,63 @@
+# ========== Global Beahvior ========== #
+include("ActFunctions.jl");
+include("Brain.jl");
+using LaTeXStrings
+using Random
+
+save(x) = savefig(string("figs/", x))
+
+# Fixed seed for testing
+Random.seed!(1234)
+
+# ========== Testing ========== #
+# Functions
+sig = Sigmoid()
+tan = Tanh()
+linear = Linear()
+relu = ReLu()
+
+# Dataset for logic gates
+datax = [0 0; 0 1; 1 0; 1 1]
+datay = [zeros(size(datax)[1], 1), zeros(size(datax)[1], 1), zeros(size(datax)[1], 1)]
+and(x, y) = x & y
+or(x, y) = x | y
+for i in 1:size(datax)[1]
+    datay[1][i, 1] = xor(datax[i, :]...)
+    datay[2][i, 1] = and(datax[i, :]...)
+    datay[3][i, 1] = or(datax[i, :]...)
+end
+
+# Learn data
+m = 2
+n = 1
+l = [2, 2, 2]
+brains = [Brain(m, n, l, [sig for i in 1:(length(l) + 1)]),
+          Brain(m, n, l, [sig for i in 1:(length(l) + 1)]),
+          Brain(m, n, l, [sig for i in 1:(length(l) + 1)])]
+
+
+# Learning each dataset
+grads = []
+epocs = [100000, 5000, 5000]
+for i in 1:length(brains)
+    grad, _, _ = brains[i].learn_data(datax, datay[i], η=0.5, epocs=epocs[i],
+                                      α=0.2)
+    push!(grads, grad)
+end
+
+# Plot gradients
+layers = [latexstring("l = ", i + 1) for i in 1:length(brains[1].ω)]
+labels = ["xor", "and", "or"]
+for i in 1:length(grads)
+    for j in 1:size(datax)[1]
+        println("Data ", datax[j, 1], ", ", datax[j, 2])
+        println(brains[i].propagate(datax[j, :]))
+        println()
+    end
+    println("#########################")
+    plot(grads[i],
+         label = reshape(layers, 1, length(layers)),
+         xlabel = L"$n$",
+         ylabel = L"$\sum_i \delta^l_i$")
+    save(string("grads-", labels[i], "-mom.pdf"))
+end

### 2021-01-17 supervised/exam/daples/src/BackPropagation.jl
[ supervised ] added @daples exam.

@@ -1,0 +1,83 @@
+using Random
+include("Tools.jl");
+
+function propagate(x, Ws, ϕ, hidden_layers)
+    Vs = []
+    Φs = []
+    push!(Vs, x)
+    push!(Φs, vcat(x, [1]))
+    aux = Φs[end]
+    for i in 1:(hidden_layers + 1)
+        v = Ws[i]' * aux
+        push!(Vs, v)
+        aux = i == hidden_layers + 1 ? ϕ[i+1](v) : vcat(ϕ[i+1](v), [1])
+        push!(Φs, aux)
+    end
+    return Vs, Φs
+end
+
+function nn(X, Y, L, ϕ, ∂ϕ; η=0.05, α=0.1, s=10, seed=nothing)
+    isnothing(seed) ? nothing : Random.seed!(seed)
+    # Dimensions
+    m = size(X, 2) + 1
+    N, n = size(Y)
+    hidden_layers = size(L, 1)
+    layers = size(L, 1) + 2
+
+    # Auxiliary Structures
+    augL = [m - 1, L..., n]
+    Ξ = zeros(N, s) # error energies per epoch
+    ∇s = zeros(s, hidden_layers + 1) # sum of gradients at the end of each epoch
+    Ws = []
+    ΔWs = []
+
+    # Fill weights
+    for l in 1:(layers - 1)
+        push!(Ws, init_weights(augL[l] + 1, augL[l+1]))
+        push!(ΔWs, zeros(augL[l] + 1, augL[l+1]))
+    end
+
+    # Optimization
+    Vs = nothing
+    E = nothing
+    ΔW = nothing
+    δs = nothing
+    Φs = nothing
+    for h in 1:s
+        E = zeros(size(Y)) # errors in one epoch
+        ∇ = zeros(hidden_layers + 1)
+        for p in 1:N
+            δs = []
+            x = reshape(X[p, :], (m - 1, 1))
+            y = reshape(Y[p, :], (n, 1))
+
+            # Propagate
+            Vs, Φs = propagate(x, Ws, ϕ, hidden_layers)
+            y_nn = Φs[end]
+            E[p, :] = y - y_nn
+
+            # Backpropagate
+            aux = true
+            for i in layers:-1:2
+                e = reshape(E[p, :], (n, 1))
+                if aux
+                    δ = ∂ϕ[i](Vs[i]) .* e
+                    aux = false
+                else
[…]

### 2021-01-17 supervised/exam/daples/src/Exam.jl

@@ -1,0 +1,110 @@
+include("BackPropagation.jl")
+include("PlotTools.jl")
+include("Tools.jl")
+
+full_data, header = read_data("data/datosimulacionC.csv");
+full_data = normalize(full_data);
+
+# Input data: Variables Sp, Xv and OD
+full_X = full_data[:, [1, 2, 3, 5, 6]];
+N, m = size(full_X);
+
+# Output data: Variable X
+full_Y = reshape(full_data[:, 4], (N, 1));
+
+# Training set 60%
+training = [];
+# Test 20%
+test = [];
+# Validation 20%
+validation = [];
+
+for i in 1:N
+    r = rand()
+    if r <= 0.6
+        append!(training, i)
+    elseif r <= 0.8
+        append!(test, i)
+    else
+        append!(validation, i)
+    end
+end
+
+training_X = full_X[training, :]
+training_Y = full_Y[training, :]
+test_X = full_X[test, :]
+validation_X = full_X[validation, :]
+
+# Parameters
+L = [5, 5];
+ϕ_sigm(x) = 1.0 ./ (1.0 .+ exp.(-x));
+∂ϕ_sigm(x) = ϕ_sigm(x).*(1 .- ϕ_sigm(x));
+
+ϕ = [ϕ_sigm for i in 1:size(L, 1) + 2];
+∂ϕ = [∂ϕ_sigm for i in 1:size(L, 1) + 2];
+
+## First Eta
+η = -0.2
+Vs, Φs, Ws, ∇s, Ξ = nn(training_X, training_Y, L, ϕ, ∂ϕ; η=η, α=0, s=50);
+
+# Average Error
+plot_ξav(Ξ, save_fig=true, out_file="Eav.pdf", dir="eta_$η")
+
+# Plot Gradients
+plot_∇s(∇s, save_fig=true, out_file="grads.pdf", dir="eta_$η")
+
+# NN-Training Output
+Y_nn = zeros(length(training), 1)
+for i in 1:length(training)
+    Y_nn[i, 1] = propagate(training_X[i, :], Ws, ϕ, 2)[2][end][1]
+end
+# NN-Test Output
+Y_nn_test = zeros(length(test), 1)
+for i in 1:length(test)
+    Y_nn_test[i, 1] = propagate(test_X[i, :], Ws, ϕ, 2)[2][end][1]
+end
+# NN-Validation Output
+Y_nn_valid = zeros(length(validation), 1)
[…]

### 2021-01-17 supervised/exam/daples/src/PlotTools.jl

@@ -1,0 +1,177 @@
+# using Pkg
+# Pkg.add("LaTeXStrings")
+# Pkg.add("Plots")
+
+using LaTeXStrings
+using Plots
+
+include("BackPropagation.jl")
+
+# Standardize file saving
+function save(fig, out_file; dir="")
+    if ~isdir(joinpath(pwd(), "figs"))
+        mkdir("figs");
+    end
+    if ~isdir(joinpath(pwd(), "figs", dir))
+        mkdir(joinpath(pwd(), "figs", dir))
+    end
+    plot_wd = joinpath(pwd(), "figs", dir);
+    savefig(fig, joinpath(plot_wd, out_file))
+end
+
+# Standardize plots and surfaces
+function plotPL(x, y,
+    add = nothing;
+    z = nothing,
+    label = "",
+    color = :black,
+    lw = 2,
+    legend = :right,
+    fontsize = 12,
+    font = "times",
+    xlabel = "",
+    ylabel = "",
+    zlabel = "",
+    st = :surface,
+    cam = (-30, 30)
+)
+    if isnothing(add)
+        if isnothing(z)
+            global fig = plot(x, y,
+                label = label,
+                color = color,
+                lw = lw,
+                legend = legend,
+                xlabel = xlabel,
+                ylabel = ylabel,
+                titlefont = (fontsize, font),
+                xtickfont = (fontsize, font),
+                ytickfont = (fontsize, font),
+                # guidefont = (fontsize, font),
+                legendfontsize = fontsize
+            )
+        else
+            global fig = plot(x, y, z,
+                label = label,
+                lw = lw,
+                legend = legend,
+                xlabel = xlabel,
+                ylabel = ylabel,
+                zlabel = zlabel,
+                titlefont = (fontsize, font),
+                xtickfont = (fontsize, font),
+                ytickfont = (fontsize, font),
+                ztickfont = (fontsize, font),
+                # guidefont = (fontsize, font),
+                legendfontsize = fontsize,
+                st = st
+            )
+        end
+    else
+        if isnothing(z)
+            plot!(add, x, y,
+                label = label,
+                color = color,
+                lw = lw,
+                legend = legend,
+                xlabel = xlabel,
+                ylabel = ylabel,
+                titlefont = (fontsize, font),
+                xtickfont = (fontsize, font),
[…]

### 2021-01-17 supervised/exam/daples/src/Tools.jl

@@ -1,0 +1,30 @@
+using Distributions
+
+# Normalize data with max|x_i| -> [-1,1] hypercube.
+function normalize(data)
+    return data ./ maximum(abs.(data), dims=1)
+end
+
+# Initialize a nxm matrix with [-1,1] uniformly distributed random numbers.
+function init_weights(n, m)
+    return rand(Uniform(-1, 1), (n, m))
+end
+
+function read_data(file)
+    data_file = open(file, "r") do io
+        read(io, String)
+    end
+    lines = split(data_file, "\n")
+    lines = lines[1:end-1]
+    data = split.(lines, ",")
+    header = split(data[1], ",")[1]
+    data = data[2:end]
+    n = size(data)[1]
+    p = size(data[1])[1]
+    data = [parse.(Float64, point) for point in data]
+    aux = reshape(data[1], (1, p))
+    for j in 2:n
+        aux = vcat(aux, reshape(data[j], (1, p)))
+    end
+    return aux, header
+end
